---
title: "HBP_Eswatini_Outputs"
output: html_document
date: "2025-07-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

* Produce a slide deck and series of outputs illustrating the new and improved calibrated model.
* Produce aggregated tables

# Libraries 
```{r}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(data.table))
library(magrittr)
library(rsample)
library(patchwork)
```

## Constants
```{r}
SWZ_CENSUS_YEAR = 2017
SWZ_CENSUS_POP = 1148000 # UN WPP 2019, according to SWZ national census 2017 1093238

current_date <- Sys.Date()
date_string_ymd <- format(current_date, format = "%Y%m%d")
```

# Read in data

```{r}
experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/HBP/Baseline-campaign_20250715-carf_m85_f85___2025_08_01_18_34_54_703179/"

swz.results.hbp <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "swz.results",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV",
                      "Newly.Infected","Diagnosed","OnART0","OnART0_preart","OnART1","EffectiveART","NonSuppressiveART"),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.ARTStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

sim.results.pop.scaling <- swz.results.hbp %>%
  filter(Year == SWZ_CENSUS_YEAR) %>%
  group_by(sim.ix, scenario_name) %>%
  summarize(total.pop = sum(Population), .groups = 'drop_last') %>%
  mutate(pop_scaling_factor = SWZ_CENSUS_POP/total.pop)

swz.results.hbp <- swz.results.hbp %>%
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.ix", "scenario_name")
  )

```


# All ages prevalence vs time

## Load and transform data
```{r}
prev.15.49 <- data.table(Year = c(2006, 2006, 2011,2011, 2016, 2016, 2021, 2021),
                         Gender = c("Female", "Male"),
                         prev = c(31.36998255, 19.54469739, 38.79583333, 24.3101129, 34.67579541, 19.87162343, 32.01485259, 16.34463925)/100,
                         #prev = c(0.38861021, 0.282294676, 0.462308369, 0.274811025, 0.421160235, 0.26133829, 0.384828736, 0.195259228),
                         lb = c(30.02809341, 18.26093783, 37.83139223,23.39183621, 33.35133936,18.60315482,31.85041561, 16.21699044)/100,
                         ub = c(32.73564238, 20.87807258, 39.76691062, 25.2464012, 36.01828845,21.18736119, 32.17962673, 16.4728948)/100)

data <- EMODAnalyzeR::calculate.prevalence(
  swz.results.hbp %>% filter(Age >=15, Age < 50),
         stratify_columns = c("Year", "Gender", "sim.id", "scenario_name"),
         numerator = "Infected",
         denominator = "Population")

prev.data.mean <- data %>%
    dplyr::group_by(Year, Gender, scenario_name) %>%
    dplyr::summarise(Prevalence = mean(Prevalence), .groups = 'keep') %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))
```

## Plot
```{r}
plot.prev <- ggplot() +
    geom_line(data= prev.data.mean %>% filter(Year > 1995),
              aes(x=Year, y=Prevalence, group=scenario_name, color=Gender), linewidth=2, 
               show.legend = FALSE)+
    geom_point(data = prev.15.49,
               mapping = aes(x = Year, y = prev),
                show.legend = FALSE,
               color = 'black', shape = 0,
               size = 2) +
    geom_errorbar(data = prev.15.49,
                  mapping = aes(x = Year, ymin = lb, ymax = ub),
                  show.legend = FALSE,
                  color = 'black', size = .5)+
    facet_wrap(~ Gender, ncol=2) +
    xlab("Year")+
    #xlim(c(date.start, date.end)) +
    ylab("HIV Prevalence (Ages 15-50)") + 
    theme_bw(base_size=16) +
    guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
    scale_x_continuous(breaks = seq(1980,2050,10)) +
    scale_y_continuous(breaks = seq(0,.40,.10), 
                       limits = c(0,.45),
                       labels = scales::percent_format(accuracy = 1)) +
    theme(legend.position="bottom") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    theme(strip.background = element_rect(colour="black", fill="white")) +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    scale_color_manual(values=c("blue", "red"))

plot.prev

ggsave(paste0(c("SWZ_prev_",date_string_ymd,".pdf"), collapse = ""), plot.prev, height = 4, width = 6, units = 'in')

```

# Prevalence vs age over time

```{r}
#age_bins = c(15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65,99)
age_bins = c(15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65,99)
subset_years = c(2007, 2011, 2016, 2021)

# Subset data on years
data <- swz.results.hbp %>% filter(Year %in% subset_years)

# Age bins
age_labels = c()
for (i in 1:(length(age_bins) - 1)){
  age_labels <- append(age_labels, paste0("[",age_bins[i],":",age_bins[i + 1],")"))
}

# Label each age by its bin
data <- data %>% mutate(
  AgeBin = cut(Age, breaks = age_bins, right = FALSE)
  ) %>%
  filter(!is.na(AgeBin))
data$AgeBin_index = factor(data$AgeBin,labels = 1:length(age_labels))

# Calculate prevalence, grouping by age bin
data.prev <- data %>% EMODAnalyzeR::calculate.prevalence(
  stratify_columns = c("Year", "AgeBin_index", "AgeBin", "Gender", "scenario_name", "sim.id"),
  numerator = "Infected",
  denominator = "Population")

# Calculate mean prevalence across all sim runs
ageprev.data.mean <- data.prev %>%
  dplyr::group_by(Year, AgeBin_index, AgeBin, Gender, scenario_name) %>%
  dplyr::summarize(mean.Prevalence = mean(Prevalence),
            sd.Prevalence = sd(Prevalence),
            .groups = 'keep') %>%
  ungroup() %>%
  dplyr::mutate(upper = mean.Prevalence + 2*sd.Prevalence,
                lower = case_when(mean.Prevalence - 2 * sd.Prevalence > 0 ~ mean.Prevalence - 2 * sd.Prevalence,
                         mean.Prevalence - 2 * sd.Prevalence <= 0 ~ 0)
                )

# Transform data
ageprev.data.mean <- ageprev.data.mean %>% mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))
ageprev.data.mean <- ageprev.data.mean[order(ageprev.data.mean$scenario_name), ]
ageprev.data.mean$scenario_name <- as.factor(ageprev.data.mean$scenario_name)
```

## Plot

```{r, fig.width = 10}
Prev.age.plot <- ageprev.data.mean %>% #filter(scenario_name %in% c("carf90", "test", "old")) %>% 
  mutate(scenario_name = as.factor(scenario_name)) %>% 
  ggplot() +
  geom_point(data = obs.prev.sheet.base,
             mapping = aes(x = AgeBin_index, y = Prevalence), 
             size = 3, color = 'black', shape = 0,
             show.legend = FALSE) +
  geom_errorbar(data = obs.prev.sheet.base,
             mapping = aes(x = AgeBin_index, ymin = lb, ymax = ub),
             size = 1, color = 'black',
             show.legend = FALSE) +
  # plot means
  # geom_point(
  #   mapping = aes(x = AgeBin_index, y = mean.Prevalence, color = scenario_name),
  #   size=2,
  #    show.legend = TRUE
  # ) +
  geom_line(
    mapping = aes(x = AgeBin_index, y = mean.Prevalence, group = scenario_name, color = Gender),
    size=1,
    show.legend = FALSE
  ) +
  # geom_errorbar(
  #   mapping = aes(x=AgeBin_index, ymin=lower, ymax=upper, color=Gender),
  #   width=.15, size=1,
  #  show.legend = FALSE) +
  facet_grid(cols = vars(Gender), rows = vars(Year)) +
  #xlab("Age") +
  #ylab("Prevalence") +
  theme_bw(base_size=24) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_discrete(
    breaks = 1:length(age_labels),
    labels = age_labels
    #labels = rep("",length(age_labels))
    ) +
  scale_color_manual(values=c("blue", "red")) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),) + 
  ylab("Prevalence by Age") + 
  #theme(legend.position="bottom") + 
  theme(legend.position="bottom",
        axis.title.x=element_blank(),
        #axis.title.y=element_blank(),
        #strip.text.x = element_blank(),
        #strip.text.y = element_blank()
        ) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

Prev.age.plot

ggsave(paste0(c("SWZ_prev_age_",date_string_ymd,".pdf"), collapse = ""), Prev.age.plot, height = 6, width = 12, units = 'in')
```

# All ages ART coverage over time

## Plot
```{r}
sim.onart <- swz.results.hbp %>%
  filter(Age > 15) %>%
  dplyr::group_by(Year, Gender, sim.ix) %>% 
  dplyr::summarize(On_ART = sum(On_ART * pop_scaling_factor),
                   Infected = sum(Infected * pop_scaling_factor), 
                   .groups = 'drop_last') %>% 
  ungroup()  %>% 
  mutate(ARTcov = case_when(Infected == 0 ~ 0,
                            Infected > 0 ~ On_ART/Infected)) %>%
  group_by(Year, Gender) %>% 
  summarize(On_ART = mean(On_ART),
            Infected = mean(Infected), 
            ARTcov = mean(ARTcov), .groups = 'drop_last') %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

ART.cov.plot <- sim.onart %>% filter(Year >= 2000, Year <=2025)  %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y =  ARTcov* 100, color = Gender)) + 
  facet_grid(cols = vars(Gender)) +
  scale_color_manual(values=c("blue", "red")) + 
  xlab("Year") +
  ylab("ART Coverage (%)") +
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  theme(legend.position="bottom")  + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

ART.cov.plot

ggsave(paste0(c("SWZ_art_coverage_",date_string_ymd,".pdf"), collapse = ""), ART.cov.plot, height = 4, width = 6, units = 'in')
```


```{r}
sim.onart %>% filter(Year == 2025)
```


# ART coverage vs age over time

## Load data
```{r}
art.coverage.shims <- read.csv(file = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/Data/SWZ_ART_SHIMS_2024-07-05.csv")

art.coverage.shims$AgeMin = sapply(strsplit(art.coverage.shims$agecat, "-"), `[`, 1)
art.coverage.shims$AgeMin = as.numeric(art.coverage.shims$AgeMin)
art.coverage.shims$AgeMax = sapply(strsplit(art.coverage.shims$agecat, "-"), `[`, 2)
art.coverage.shims$AgeMax = as.numeric(art.coverage.shims$AgeMax)
art.coverage.shims[is.na(art.coverage.shims$AgeMin),]$AgeMin <- 80
art.coverage.shims[is.na(art.coverage.shims$AgeMax),]$AgeMax <- 100

art.coverage.shims <- art.coverage.shims %>% 
  select(gender, agecat, AgeMin, AgeMax) %>%
  group_by(gender, agecat, AgeMin, AgeMax) %>% 
  slice(1) %>%
  ungroup() %>% 
  mutate(year = 2004, 
         pct_on_art = 0) %>% 
  select(year, gender, agecat, AgeMin, AgeMax, pct_on_art) %>% 
  rbind(art.coverage.shims %>% select(year, gender, agecat, AgeMin, AgeMax, pct_on_art))

art.coverage.shims <- art.coverage.shims %>% select(Year = year, Gender= gender, agecat, AgeMin, AgeMax, pct_on_art)
```

## Transform simulation data
```{r}
age_bins = c(15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65)

# Subset data on years
data <- swz.results.hbp %>% filter(Year >= 2004)

# Age bins
age_labels = c()
for (i in 1:(length(age_bins) - 1)){
  age_labels <- append(age_labels, paste0("[",age_bins[i],":",age_bins[i + 1],")"))
}

# Label each age by its bin
data <- data %>% mutate(
  AgeBin = cut(Age, breaks = age_bins, right = FALSE)
  ) %>%
  filter(!is.na(AgeBin))
data$AgeBin_index = factor(data$AgeBin,labels = 1:10)#length(age_labels))

# Label SHIMS ART coverage data age by bins
art.coverage.shims <- art.coverage.shims %>% 
  mutate(AgeBin = cut(AgeMin, breaks = age_bins, right = FALSE)
         ) %>% 
  filter(!is.na(AgeBin))
art.coverage.shims$AgeBin_index = factor(art.coverage.shims$AgeBin,labels = 1:length(age_labels))

# Calculate prevalence, grouping by age bin
data.prev <- data %>% EMODAnalyzeR::calculate.prevalence(
  stratify_columns = c("Year", "AgeBin_index", "AgeBin", "Gender", "scenario_name", "sim.id"),
  numerator = "On_ART",
  denominator = "Infected")

# Calculate mean ART coverage
art.cov.age.mean <- data.prev %>%
  dplyr::group_by(Year, AgeBin_index, AgeBin, Gender, scenario_name) %>%
  dplyr::summarize(mean.Prevalence = mean(Prevalence),
            sd.Prevalence = sd(Prevalence),
            .groups = 'keep') %>%
  ungroup() %>%
  dplyr::mutate(upper = mean.Prevalence + 2*sd.Prevalence,
                lower = case_when(mean.Prevalence - 2 * sd.Prevalence > 0 ~ mean.Prevalence - 2 * sd.Prevalence,
                         mean.Prevalence - 2 * sd.Prevalence <= 0 ~ 0)
                )

art.cov.age.mean <- art.cov.age.mean %>% mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))
```

## Plot

```{r, fig.width=10}
art.cov.age.plot <- art.cov.age.mean %>% 
  filter(Year == floor(Year), Year < 2025, as.numeric(AgeBin_index) < 8) %>% 
  ggplot() +
  # plot means
  geom_point(
    mapping = aes(x = Year, y = mean.Prevalence*100, color = Gender), 
    size=3,
     show.legend = FALSE
  ) +
  geom_line(
    mapping = aes(x = Year, y = mean.Prevalence*100, color = Gender),
    size=2,
     show.legend = FALSE
  ) +
  # plot data
  geom_point(data = art.coverage.shims %>% filter(as.numeric(AgeBin_index) < 8),
             mapping = aes(x = Year, y = pct_on_art), size = 4) + 
  facet_grid(cols = vars(Gender), rows = vars(AgeBin)) +
  xlab("Year") +
  ylab("ART Coverage (%)")  +
  scale_color_manual(values=c("blue", "red")) +
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
  
art.cov.age.plot

ggsave(paste0(c("SWZ_art_coverage_age_",date_string_ymd,".pdf"), collapse = ""), art.cov.age.plot, height = 6, width = 12, units = 'in')

```

```{r}

```


# All ages VLS coverage vs time

## Load data
```{r}
# VLS coverage by gender and year scraped from PHIA website
VLS.table <- data.table(
  Year = c(2017, 2017, 2021, 2021),
  Gender = c("Male", "Female", "Male", "Female"),
  VLS = c(57.6, 81.2, 96.7, 95.9)/100
)
```

## Plot
```{r}
plot.vls <- swz.results.hbp %>% 
  filter(Year >= 2004, Age >= 15) %>% 
  dplyr::group_by(Year, Gender, scenario_name, IP_Key.ARTStatus, sim.ix) %>% 
  dplyr::summarize(On_ART = sum(On_ART * pop_scaling_factor), 
                   .groups = "keep") %>% 
  ungroup() %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female")) %>%
  group_by(Year, Gender, scenario_name, IP_Key.ARTStatus) %>% 
  summarize(On_ART = mean(On_ART), .groups = 'drop_last') %>% 
  pivot_wider(id_cols = c(Year, Gender, scenario_name), 
              names_from = IP_Key.ARTStatus,
              values_from = On_ART) %>% 
  mutate(Total = NeverOnART + OffART + OnARTPreVLS+ OnEffectiveART + OnNonSuppressiveART) %>% 
  mutate(VLS = OnEffectiveART/Total) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = VLS, color = Gender), 
            show.legend = FALSE)  +
  scale_color_manual(values=c("blue", "red")) + 
  geom_point(data = VLS.table, mapping = aes(x = Year, y  = VLS), color = 'black') +
  facet_wrap(facets = vars(Gender), ncol = 2) + 
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  theme(legend.position="bottom")

plot.vls

ggsave(paste0(c("SWZ_VLS_coverage_",date_string_ymd,".pdf"), collapse = ""), plot.vls, height = 4, width = 6, units = 'in')

```


# VLS coverage vs age over time

## Load data
```{r}
# From SHIMS, extracted by Kasturi
VLS.data <- read.csv(file = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/Data/SWZ_VLS_coverage.csv")
VLS.data <- VLS.data %>% 
  pivot_longer(cols = c(X2017, X2021), values_to = "VLS", names_to = "Year", names_prefix = "X") %>%
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))
VLS.data$Year = as.numeric(VLS.data$Year)

```


## Transform data
```{r}
VLS.cov.by.age <- merge(
  swz.results.hbp %>% #filter(scenario_name == 'test') %>% 
    filter(Year >= 2004, Age >= 15, Age <= 65, IP_Key.ARTStatus == "OnEffectiveART") %>% 
    dplyr::group_by(Year, Age, Gender, scenario_name, sim.ix) %>% 
    dplyr::summarize(OnEffectiveART = sum(On_ART * pop_scaling_factor), 
                     .groups = "drop_last") %>% 
    group_by(Year, Age, Gender, scenario_name) %>% 
    summarize(OnEffectiveART = mean(OnEffectiveART), .groups = 'drop_last'),
  swz.results.hbp %>% #filter(scenario_name == 'test') %>% 
    filter(Year >= 2004, Age >= 15, Age <= 65, IP_Key.ARTStatus == "OnNonSuppressiveART") %>% 
    dplyr::group_by(Year, Age, Gender, scenario_name, sim.ix) %>% 
    dplyr::summarize(OnNonSuppressiveART = sum(On_ART * pop_scaling_factor), 
                     .groups = "drop_last") %>% 
    group_by(Year, Age, Gender, scenario_name) %>% 
    summarize(OnNonSuppressiveART = mean(OnNonSuppressiveART), .groups = 'drop_last'),
  by = c("Year", "Age", "Gender", "scenario_name")
) %>%
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female")) %>%
  mutate(Total = OnEffectiveART + OnNonSuppressiveART) %>% 
  mutate(VLS = OnEffectiveART/Total)

```

## Plot

```{r, fig.width=10}
plot.vls.age <- VLS.cov.by.age %>% filter(Age <= 50) %>% 
  mutate(Age_factor = factor(Age)) %>%
  ggplot() + 
  geom_point(mapping = aes(x = Year, y = VLS, color = Gender), 
             show.legend = FALSE) + 
  geom_point(data = VLS.data %>% filter(Age >= 15, Age <=50) %>% 
               mutate(Age_factor = factor(Age)), 
             mapping = aes(x = Year, y = VLS), color = 'black') + 
  scale_y_continuous(limits = c(.5,1))  +
  scale_color_manual(values=c("blue", "red")) + 
  facet_grid(cols = vars(Gender), 
             rows = vars(Age_factor), scales = "free_y"
             ) + 
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  theme(legend.position="bottom")

plot.vls.age

ggsave(paste0(c("SWZ_VLS_coverage_age_",date_string_ymd,".pdf"), collapse = ""), plot.vls.age, height = 8, width = 12, units = 'in')
```

# All ages incidence over time
## Load data

```{r}
 # 2011 SHIMS
# <https://www-ncbi-nlm-nih-gov.ezproxy.med.nyu.edu/pmc/articles/PMC5291824/>
# 2016
# <https://phia.icap.columbia.edu/wp-content/uploads/2019/05/SHIMS2_Final-Report_05.03.2019_forWEB.pdf>
# 2021
# <https://phia.icap.columbia.edu/wp-content/uploads/2023/12/241123_SHIMS_ENG_RR3_Final-1.pdf>
# Ages 15-49
incidence.data <- data.table(Year = c(2011, 2011, 2016, 2016, 2021, 2021),
                                     Gender = c("Male", "Female"),
                                     inc = c(1.7,3.1,.99, 1.99, .2, 1.45),
                                     lb = c(1.3, 2.6, .032, 1.09, 0, 0.69 ),
                                     ub = c(2.1,3.7, 1.66, 2.88, .48, 2.2))
```

## Transform simulation results
```{r}
data <- swz.results.hbp %>% filter(Age >= 15, Age < 50)

# Calculate incidence
data$Year_Integer <- floor((data$Year-0.5))
# Aggregate number of new infections each year, broken down by Year_Integer and Gender
trajectories_IR.1a <- aggregate(Newly.Infected ~ Year_Integer+Gender + sim.id+scenario_name, data=data,FUN=sum)
#Make the denominator as HIV-negative individuals
trajectories_IR.2 <- aggregate(Population - Infected ~ Year+Gender + sim.id+scenario_name, data=data, FUN=sum)
trajectories_IR.2$Year_Integer <- floor(trajectories_IR.2$Year-0.5)
#remove second instance of duplicate rows
trajectories_IR.2 <- trajectories_IR.2[!duplicated(trajectories_IR.2[c("Year_Integer","Gender", "sim.id","scenario_name")]),]
trajectories_IR.2 <- trajectories_IR.2[-match("Year",names(trajectories_IR.2))]
trajectories_IRoverall <- merge(trajectories_IR.1a, trajectories_IR.2, by=c("Year_Integer","Gender","sim.id","scenario_name"))
trajectories_IRoverall$incidence <- trajectories_IRoverall$Newly.Infected / (trajectories_IRoverall$Population)
data <- trajectories_IRoverall %>% dplyr::rename(Year = Year_Integer)

# Calculate mean incidence across all sim runs
inc.data.mean <- data %>%
  dplyr::group_by(Year, Gender, scenario_name) %>%
  dplyr::summarize(mean.Incidence = mean(incidence),
                  sd.Incidence = sd(incidence),
            .groups = 'keep') %>%
  ungroup() %>%
  dplyr::mutate(upper = mean.Incidence + 2*sd.Incidence,
                lower = case_when(mean.Incidence - 2 * sd.Incidence > 0 ~ mean.Incidence - 2 * sd.Incidence,
                         mean.Incidence - 2 * sd.Incidence <= 0 ~ 0)
                )

# Transform data
inc.data.mean <- inc.data.mean %>% mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))
```

## Plot

```{r, fig.width=10}
plot.inc <- inc.data.mean %>%
  ggplot() +
  # plot means
  geom_point(
    mapping = aes(x = Year, y = mean.Incidence*100, color = Gender),
    size=2,
     show.legend = FALSE
  ) +
  geom_errorbar(
    mapping = aes(x=Year, ymin=lower*100, ymax=upper*100, color=Gender),
    width=.15, size=1,
   show.legend = FALSE) +
  geom_point(data = incidence.data, 
             mapping = aes(x = Year, y = inc), color = 'black') + 
  geom_errorbar(data = incidence.data, 
    mapping = aes(x = Year, ymin = lb, ymax = ub), color = 'black') + 
  facet_grid(cols = vars(Gender), rows = vars(scenario_name)) +
  #scale_color_manual(values=c("blue", "red")) +
  xlab("Age") +
  ylab("Incidence (%)") +
  scale_color_manual(values=c("blue", "red")) +
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_continuous(breaks = c(2005, 2010, 2015, 2020, 2025),
                     limits = c(2005, 2025)) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text.y = element_blank()) 

plot.inc

ggsave(paste0(c("SWZ_inc_",date_string_ymd,".pdf"), collapse = ""), plot.inc, height = 4, width = 6, units = 'in')

```

# Mortality over time

## Transform data

```{r}
mort.all <- swz.results.hbp %>% group_by(Year, Gender, sim.ix) %>% 
  summarize(Died = sum(Died * pop_scaling_factor),
            Population = sum(Population * pop_scaling_factor)) %>% 
  group_by(Year, Gender) %>% 
  summarize(Died = mean(Died),
            Population = mean(Population)) %>% 
  ungroup() %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female")) %>% 
  mutate(mort.rate = case_when(Population == 0 ~ 0, Population > 0 ~ Died/Population)) 

hiv.mort <- swz.results.hbp %>% group_by(Year, Gender, sim.ix) %>% 
  summarize(Died = sum(Died_from_HIV * pop_scaling_factor),
            Population = sum(Population * pop_scaling_factor)) %>% 
  group_by(Year, Gender) %>% 
  summarize(Died = mean(Died),
            Population = mean(Population)) %>% 
  ungroup() %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female")) %>% 
  mutate(mort.rate = case_when(Population == 0 ~ 0, Population > 0 ~ Died/Population))

mort.all$row <- "All"

hiv.mort$row <- "HIV"

mort.dat <- rbind(mort.all, hiv.mort)


p <- ggplot() +  
  geom_line(mort.dat, mapping = aes(x = Year, y = mort.rate*100, color = Gender), 
            size = 2, show.legend = FALSE) + 
  facet_grid(cols = vars(Gender), rows = vars(row)) + 
  xlab("Year") +
  ylab("Mortality Rate (%)") +
  #scale_x_continuous(breaks = c(2000, 2050, 5),) +
  scale_color_manual(values=c("blue", "red")) + 
  theme_bw(base_size=16)+
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

p

ggsave(paste0(c("SWZ_mort_",date_string_ymd,".pdf"), collapse = ""), p, height = 4, width = 6, units = 'in')

```


## Plot

# Incidence vs age over time

## Incidence calculation

```{r}
age_bins = c(15, 25, 35, 50)
subset_years = c(2016, 2016.5, 2021, 2021.5)

# Subset data on years
data <- swz.results.hbp %>% filter(Year %in% subset_years)

# Calculate incidence
data$Year_Integer <- floor((data$Year-0.5))
# Aggregate number of new infections each year, broken down by Year_Integer and Gender
trajectories_IR.1a <- aggregate(Newly.Infected ~ Year_Integer+Gender+Age + sim.id+scenario_name, data=data,FUN=sum)
#Make the denominator as HIV-negative individuals
trajectories_IR.2 <- aggregate(Population - Infected ~ Year+Gender+Age + sim.id+scenario_name, data=data, FUN=sum)
trajectories_IR.2$Year_Integer <- floor(trajectories_IR.2$Year-0.5)
#remove second instance of duplicate rows
trajectories_IR.2 <- trajectories_IR.2[!duplicated(trajectories_IR.2[c("Year_Integer","Gender","Age", "sim.id","scenario_name")]),]
trajectories_IR.2 <- trajectories_IR.2[-match("Year",names(trajectories_IR.2))]
trajectories_IRoverall <- merge(trajectories_IR.1a, trajectories_IR.2, by=c("Year_Integer","Gender","Age", "sim.id","scenario_name"))
trajectories_IRoverall$incidence <- trajectories_IRoverall$Newly.Infected / (trajectories_IRoverall$Population)
data <- trajectories_IRoverall %>% dplyr::rename(Year = Year_Integer)

# Age bins
age_labels = c()
for (i in 1:(length(age_bins) - 1)){
  age_labels <- append(age_labels, paste0("[",age_bins[i],":",age_bins[i + 1],")"))
}

# Label each age by its bin
data <- data %>% mutate(
  AgeBin = cut(Age, breaks = age_bins, right = FALSE)
  ) %>%
  filter(!is.na(AgeBin))
data$AgeBin_index = factor(data$AgeBin,labels = 1:length(age_labels))

# Calculate mean incidence across all sim runs
inc.age.data.mean <- data %>%
  dplyr::group_by(Year, AgeBin_index, AgeBin, Gender, scenario_name) %>%
  dplyr::summarize(mean.Incidence = mean(incidence),
                  sd.Incidence = sd(incidence),
            .groups = 'keep') %>%
  ungroup() %>%
  dplyr::mutate(
    upper = mean.Incidence + 2*sd.Incidence,
    lower = case_when(
      mean.Incidence - 2 * sd.Incidence > 0 ~ mean.Incidence - 2 * sd.Incidence,
      mean.Incidence - 2 * sd.Incidence <= 0 ~ 0)
    )  %>% mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))
```


## Plot

```{r}
plot.inc.age <- inc.age.data.mean %>% filter(Year %in% c(2016,2021)) %>% 
  ggplot() +
  # plot means
  geom_point(
    mapping = aes(x = AgeBin_index, y = mean.Incidence*100, color = Gender),
    size=2,
     show.legend = FALSE
  ) +
  geom_errorbar(
    mapping = aes(x=AgeBin_index, ymin=lower*100, ymax=upper*100, color=Gender),
    width=.15, size=1,
   show.legend = FALSE) +
  # shims data 
  geom_point(
    data = inc.data, #%>% #filter(Year == 2016), 
    mapping = aes(x = AgeBin_index, y = Incidence), 
    size = 3, shape = 0, color = 'black', show.legend = FALSE
  ) + 
  geom_errorbar(
    data = inc.data,# %>% #filter(Year == 2016),
    mapping = aes(x = AgeBin_index, ymin = lb, ymax = ub),
    color = 'black', show.legend = FALSE
  ) + 
  facet_grid(cols = vars(Gender), rows = vars(Year)) +
  xlab("Age") +
  ylab("Incidence (%)") +
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_discrete(
    breaks = 1:length(age_labels),
    labels = age_labels
    #@labels = rep("", length(age_labels))
    ) +
  ylim(0,4.5) + 
  scale_color_manual(values=c("blue", "red"))
  
plot.inc.age

ggsave(paste0(c("SWZ_inc_age_",date_string_ymd,".pdf"), collapse = ""), plot.inc.age, height = 4, width = 6, units = 'in')

```

# Aggregate for Kasturi

Provide a table stratified by year, gender, age (single years), ART status

```{r}
sim.results.agg <- swz.results.hbp %>% 
  mutate(Year = floor(Year)) %>% 
  group_by(Year, Gender, Age, sim.ix) %>% 
  summarize(Population = sum(Population * pop_scaling_factor),
            Infected = sum(Infected * pop_scaling_factor),
            On_ART = sum(On_ART * pop_scaling_factor),
            Died = sum(Died * pop_scaling_factor),
            Died_from_HIV = sum(Died_from_HIV * pop_scaling_factor),
            Newly.Infected = sum(Newly.Infected * pop_scaling_factor),
            Diagnosed = sum(Diagnosed * pop_scaling_factor)) %>% 
  group_by(Year, Gender, Age) %>% 
  summarize(Population = mean(Population),
            Infected = mean(Infected),
            On_ART = mean(On_ART),
            Died = mean(Died),
            Died_from_HIV = mean(Died_from_HIV),
            Newly.Infected = mean(Newly.Infected),
            Diagnosed = mean(Diagnosed))

sim.results.agg %>% write_csv( file = paste0(c("SWZ_simulation_results3_aggregated_for_Kasturi_",date_string_ymd,".pdf"), collapse = ""))

```
