---
title: "Eswatini HBP Testing"
output: html_document
date: "2025-07-17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The purpose of this notebook is to test the new features of our Eswatini Health Benefits Package simulations

# Libraries 
```{r}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(data.table))
library(magrittr)
library(rsample)
library(patchwork)
```

## Constants
```{r}
SWZ_CENSUS_YEAR = 2017
SWZ_CENSUS_POP = 1148000 # UN WPP 2019, according to SWZ national census 2017 1093238
```

# Read in data

```{r}
# Test results - original distribution of VLS, no time delay or maintenance
# experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/HBP/Baseline-campaign_20250715-test___2025_07_17_11_16_26_189988/"
experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/HBP/Baseline-campaign_20250715-test___2025_07_17_15_07_49_376423"

test.results <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "test",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV",
                      "Newly.Infected","Diagnosed","OnART0","OnART0_preart","OnART1","EffectiveART","NonSuppressiveART"),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.ARTStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

# Old results, for comparison on incidence rates
experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/HBP/Baseline-campaign_20240707-test_old___2025_07_25_17_04_29_032043/"

old.results <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "old",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV",
                      "Newly.Infected","Diagnosed","OnART0","OnART0_preart","OnART1","EffectiveART","NonSuppressiveART"),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.ARTStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

# Crank VLS up to 100%
experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/HBP/Baseline-campaign_20250715-test_100VLS___2025_07_25_17_02_38_481593/"

vls100.results <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "vls100",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV",
                      "Newly.Infected","Diagnosed","OnART0","OnART0_preart","OnART1","EffectiveART","NonSuppressiveART"),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.ARTStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

# Crank VLS up to 100%, decrease CARF to 50%
#experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/HBP/Baseline-campaign_20250715-test_carf_50___2025_07_25_10_02_53_803015/"

# Crank VLS up to 100%, decrease CARF to 85%
experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/HBP/Baseline-campaign_20250715-test_carf_85___2025_07_25_14_50_04_010564/"

carf85.results <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "carf85",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV",
                      "Newly.Infected","Diagnosed","OnART0","OnART0_preart","OnART1","EffectiveART","NonSuppressiveART"),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.ARTStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

# Crank VLS down to 100%, decrease CARF to 90%
experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/HBP/Baseline-campaign_20250715-test_carf_90___2025_07_25_14_52_00_515269/"

carf90.results <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "carf90",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV",
                      "Newly.Infected","Diagnosed","OnART0","OnART0_preart","OnART1","EffectiveART","NonSuppressiveART"),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.ARTStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

# Crank VLS down to 100%, decrease CARF to 95%
experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/HBP/Baseline-campaign_20250715-test_carf_95___2025_07_25_14_53_26_965754/"

carf95.results <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "carf95",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV",
                      "Newly.Infected","Diagnosed","OnART0","OnART0_preart","OnART1","EffectiveART","NonSuppressiveART"),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.ARTStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/HBP/Baseline-campaign_20250715-carf_m90_f100_VLStest___2025_08_01_17_14_48_341941/"

vls.test.results <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "carf95",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV",
                      "Newly.Infected","Diagnosed","OnART0","OnART0_preart","OnART1","EffectiveART","NonSuppressiveART"),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.ARTStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

sim.results.hbp <- rbind(test.results, vls.test.results, carf.m90.f100)
# Advance VLS ramp up by 4 years, so it happens faster
#experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/HBP/Baseline-campaign_20250715-test_VLSadvance__2025_07_17_17_42_07_716958"

sim.results.hbp <- rbind(
  test.results,
  old.results,
  vls100.results,
  carf85.results,
  carf90.results,
  carf95.results
)

sim.results.pop.scaling <- sim.results.hbp %>%
  filter(Year == SWZ_CENSUS_YEAR) %>%
  group_by(sim.ix, scenario_name) %>%
  summarize(total.pop = sum(Population), .groups = 'drop_last') %>%
  mutate(pop_scaling_factor = SWZ_CENSUS_POP/total.pop)

sim.results.hbp <- sim.results.hbp %>%
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.ix", "scenario_name")
  )
```

### Optimize CARF

```{r}
#experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/HBP/Baseline-campaign_20250715-carf_m100_f100___2025_07_31_12_08_30_679971/"
experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/HBP/Baseline-campaign_20250715-carf_m100_f100___2025_08_01_18_48_57_420873/"

carf.m100.f100 <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "carf.m100.f100",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV",
                      "Newly.Infected","Diagnosed","OnART0","OnART0_preart","OnART1","EffectiveART","NonSuppressiveART"),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.ARTStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

#experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/HBP/Baseline-campaign_20250715-carf_m100_f95___2025_07_31_12_07_15_617410/"
experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/HBP/Baseline-campaign_20250715-carf_m100_f95___2025_08_01_18_47_34_863660/"

carf.m100.f95 <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "carf.m100.f95",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV",
                      "Newly.Infected","Diagnosed","OnART0","OnART0_preart","OnART1","EffectiveART","NonSuppressiveART"),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.ARTStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

#experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/HBP/Baseline-campaign_20250715-carf_m100_f90___2025_07_31_12_06_01_095036/"
experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/HBP/Baseline-campaign_20250715-carf_m100_f90___2025_08_01_18_45_49_412024/"

carf.m100.f90 <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "carf.m100.f90",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV",
                      "Newly.Infected","Diagnosed","OnART0","OnART0_preart","OnART1","EffectiveART","NonSuppressiveART"),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.ARTStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

#experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/HBP/Baseline-campaign_20250715-carf_m95_f100___2025_07_31_12_04_46_034578/"
experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/HBP/Baseline-campaign_20250715-carf_m95_f100___2025_08_01_18_44_30_843303/"

carf.m95.f100 <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "carf.m95.f100",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV",
                      "Newly.Infected","Diagnosed","OnART0","OnART0_preart","OnART1","EffectiveART","NonSuppressiveART"),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.ARTStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

#experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/HBP/Baseline-campaign_20250715-carf_m95_f95___2025_07_31_12_03_28_142137/"
experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/HBP/Baseline-campaign_20250715-carf_m95_f95___2025_08_01_18_42_46_170137/"

carf.m95.f95 <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "carf.m95.f95",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV",
                      "Newly.Infected","Diagnosed","OnART0","OnART0_preart","OnART1","EffectiveART","NonSuppressiveART"),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.ARTStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/HBP/Baseline-campaign_20250715-carf_m95_f90___2025_08_01_18_41_27_601817/"

carf.m95.f90 <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "carf.m95.f90",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV",
                      "Newly.Infected","Diagnosed","OnART0","OnART0_preart","OnART1","EffectiveART","NonSuppressiveART"),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.ARTStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/HBP/Baseline-campaign_20250715-carf_m90_f100___2025_08_01_18_39_41_945374/"

carf.m90.f100 <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "carf.m90.f100",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV",
                      "Newly.Infected","Diagnosed","OnART0","OnART0_preart","OnART1","EffectiveART","NonSuppressiveART"),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.ARTStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

#experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/HBP/Baseline-campaign_20250715-carf_m90_f95___2025_07_31_11_59_24_631841/"
experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/HBP/Baseline-campaign_20250715-carf_m90_f95___2025_08_01_18_38_20_939369"

carf.m90.f95 <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "carf.m90.f95",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV",
                      "Newly.Infected","Diagnosed","OnART0","OnART0_preart","OnART1","EffectiveART","NonSuppressiveART"),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.ARTStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

# experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/HBP/Baseline-campaign_20250715-carf_m90_f90___2025_07_31_11_57_38_617568/"
experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/HBP/Baseline-campaign_20250715-carf_m90_f90___2025_08_01_18_36_42_861991"
carf.m90.f90 <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "carf.m90.f90",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV",
                      "Newly.Infected","Diagnosed","OnART0","OnART0_preart","OnART1","EffectiveART","NonSuppressiveART"),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.ARTStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/HBP/Baseline-campaign_20250715-carf_m85_f85___2025_08_01_18_34_54_703179"

carf.m85.f85 <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "carf.m85.f85",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV",
                      "Newly.Infected","Diagnosed","OnART0","OnART0_preart","OnART1","EffectiveART","NonSuppressiveART"),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.ARTStatus"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

sim.results.hbp <- rbind(
  test.results,
  carf.m100.f100,
  carf.m100.f95,
  carf.m100.f90,
  carf.m95.f100,
  carf.m95.f95,
  carf.m95.f90,
  carf.m90.f100,
  carf.m90.f95,
  carf.m90.f90,
  carf.m85.f85
)

sim.results.pop.scaling <- sim.results.hbp %>%
  filter(Year == SWZ_CENSUS_YEAR) %>%
  group_by(sim.ix, scenario_name) %>%
  summarize(total.pop = sum(Population), .groups = 'drop_last') %>%
  mutate(pop_scaling_factor = SWZ_CENSUS_POP/total.pop)

sim.results.hbp <- sim.results.hbp %>%
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.ix", "scenario_name")
  )

```


# Plots

## Events over time by age

```{r, fig.height=10}
#test.results %>% 
sim.results.hbp %>% filter(scenario_name == 'vls100') %>% 
  filter(Year >= 1990, Age <=65) %>% 
  group_by(Year, Age, Gender, scenario_name, sim.ix) %>% 
  summarize(
    OnART0 = sum(OnART0 * pop_scaling_factor),
    OnART0_preart= sum(OnART0_preart* pop_scaling_factor),
    OnART1= sum(OnART1* pop_scaling_factor),
    EffectiveART= sum(EffectiveART* pop_scaling_factor),
    NonSuppressiveART= sum(NonSuppressiveART* pop_scaling_factor), .groups = 'drop_last') %>% 
  group_by(Year, Age, Gender, scenario_name) %>% 
  summarize(
    OnART0 = mean(OnART0),
    OnART0_preart= mean(OnART0_preart),
    OnART1= mean(OnART1),
    EffectiveART= mean(EffectiveART),
    NonSuppressiveART= mean(NonSuppressiveART), .groups = 'drop_last') %>% 
  pivot_longer(
    cols = c(OnART0, OnART0_preart, OnART1, EffectiveART, NonSuppressiveART),
    names_to = "metric",
    values_to = "value"
  ) %>% 
  mutate(Age_factor = factor(Age)) %>% 
  ggplot() + 
  geom_point(mapping = aes(x = Year, y = value, color = metric)) + 
  facet_grid(cols = vars(Gender), rows = vars(Age_factor))
```

### Compare that to the denominator in each category
```{r, fig.height=10}
test.results %>% 
  filter(Year >= 2004, Age <=65) %>% 
  group_by(Year, Age, Gender, scenario_name, sim.ix) %>% 
  summarize(
    Population = sum(Population * pop_scaling_factor),
    Infected= sum(Infected* pop_scaling_factor),
    On_ART = sum(On_ART * pop_scaling_factor)) %>% 
  group_by(Year, Age, Gender, scenario_name) %>% 
  summarize(
    Population = mean(Population),
    Infected= mean(Infected), 
    On_ART = mean(On_ART), 
    .groups = 'drop_last') %>% 
  pivot_longer(
    cols = c( On_ART),
    names_to = "metric",
    values_to = "value"
  ) %>% 
  mutate(Age_factor = factor(Age)) %>% 
  ggplot() + 
  geom_point(mapping = aes(x = Year, y = value, color = metric)) + 
  facet_grid(cols = vars(Gender), rows = vars(Age_factor), scales= "free_y")
```


## ART coverage
```{r}
sim.onart <- sim.results.hbp %>% filter(scenario_name == 'test') %>% 
  dplyr::group_by(Year, Gender, sim.ix) %>% 
  dplyr::summarize(On_ART = sum(On_ART * pop_scaling_factor),
                   Infected = sum(Infected * pop_scaling_factor), 
                   .groups = 'drop_last') %>% 
  ungroup()  %>% 
  mutate(ARTcov = case_when(Infected == 0 ~ 0,
                            Infected > 0 ~ On_ART/Infected)) %>%
  group_by(Year, Gender) %>% 
  summarize(On_ART = mean(On_ART),
            Infected = mean(Infected), 
            ARTcov = mean(ARTcov), .groups = 'drop_last') %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

sim.onart %>% filter(Year >= 2000, Year <=2025)  %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y =  ARTcov* 100, color = Gender)) + 
  facet_grid(cols = vars(Gender)) +
  scale_color_manual(values=c("blue", "red")) + 
  xlab("Year") +
  ylab("ART Coverage (%)") +
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  theme(legend.position="bottom") 
```


## Plot ART coverage by age

### Import data
```{r}
art.coverage.shims <- read.csv(file = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/Data/SWZ_ART_SHIMS_2024-07-05.csv")

art.coverage.shims$AgeMin = sapply(strsplit(art.coverage.shims$agecat, "-"), `[`, 1)
art.coverage.shims$AgeMin = as.numeric(art.coverage.shims$AgeMin)
art.coverage.shims$AgeMax = sapply(strsplit(art.coverage.shims$agecat, "-"), `[`, 2)
art.coverage.shims$AgeMax = as.numeric(art.coverage.shims$AgeMax)
art.coverage.shims[is.na(art.coverage.shims$AgeMin),]$AgeMin <- 80
art.coverage.shims[is.na(art.coverage.shims$AgeMax),]$AgeMax <- 100

art.coverage.shims <- art.coverage.shims %>% 
  select(gender, agecat, AgeMin, AgeMax) %>%
  group_by(gender, agecat, AgeMin, AgeMax) %>% 
  slice(1) %>%
  ungroup() %>% 
  mutate(year = 2004, 
         pct_on_art = 0) %>% 
  select(year, gender, agecat, AgeMin, AgeMax, pct_on_art) %>% 
  rbind(art.coverage.shims %>% select(year, gender, agecat, AgeMin, AgeMax, pct_on_art))

art.coverage.shims <- art.coverage.shims %>% select(Year = year, Gender= gender, agecat, AgeMin, AgeMax, pct_on_art)
```

### Set up plot
```{r}
age_bins = c(15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65)

# Subset data on years
data <- test.results %>% filter(Year >= 2004)

# Age bins
age_labels = c()
for (i in 1:(length(age_bins) - 1)){
  age_labels <- append(age_labels, paste0("[",age_bins[i],":",age_bins[i + 1],")"))
}

# Label each age by its bin
data <- data %>% mutate(
  AgeBin = cut(Age, breaks = age_bins, right = FALSE)
  ) %>%
  filter(!is.na(AgeBin))
data$AgeBin_index = factor(data$AgeBin,labels = 1:8)#length(age_labels))

# Label SHIMS ART coverage data age by bins
art.coverage.shims <- art.coverage.shims %>% 
  mutate(AgeBin = cut(AgeMin, breaks = age_bins, right = FALSE)
         ) %>% 
  filter(!is.na(AgeBin))
art.coverage.shims$AgeBin_index = factor(art.coverage.shims$AgeBin,labels = 1:length(age_labels))

# Calculate prevalence, grouping by age bin
data.prev <- data %>% EMODAnalyzeR::calculate.prevalence(
  stratify_columns = c("Year", "AgeBin_index", "AgeBin", "Gender", "scenario_name", "sim.id"),
  numerator = "On_ART",
  denominator = "Infected")

# Calculate mean ART coverage
data.mean <- data.prev %>%
  dplyr::group_by(Year, AgeBin_index, AgeBin, Gender, scenario_name) %>%
  dplyr::summarize(mean.Prevalence = mean(Prevalence),
            sd.Prevalence = sd(Prevalence),
            .groups = 'keep') %>%
  ungroup() %>%
  dplyr::mutate(upper = mean.Prevalence + 2*sd.Prevalence,
                lower = case_when(mean.Prevalence - 2 * sd.Prevalence > 0 ~ mean.Prevalence - 2 * sd.Prevalence,
                         mean.Prevalence - 2 * sd.Prevalence <= 0 ~ 0)
                )

# Transform data
data.mean <- data.mean %>% mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))
#data.mean
```

### Plot
```{r, fig.height= 10}
p <- data.mean %>% filter(Year == floor(Year), Year < 2025, as.numeric(AgeBin_index) < 8) %>% 
  ggplot() +
  # plot means
  geom_point(
    mapping = aes(x = Year, y = mean.Prevalence*100, color = Gender), 
    size=3,
     show.legend = FALSE
  ) +
  geom_line(
    mapping = aes(x = Year, y = mean.Prevalence*100, color = Gender),
    size=2,
     show.legend = FALSE
  ) +
  # plot data
  geom_point(data = art.coverage.shims %>% filter(as.numeric(AgeBin_index) < 8),
             mapping = aes(x = Year, y = pct_on_art), size = 4) + 
  facet_grid(cols = vars(Gender), rows = vars(AgeBin)) +
  xlab("Year") +
  ylab("ART Coverage (%)") +
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_manual(values=c("blue", "red"))
  
p
```

## VLS Coverage

```{r}
# VLS coverage by gender and year scraped from PHIA website
VLS.table <- data.table(
  Year = c(2017, 2017, 2021, 2021),
  Gender = c("Male", "Female", "Male", "Female"),
  VLS = c(57.6, 81.2, 96.7, 95.9)/100
)

sim.results.hbp %>% 
  filter(Year >= 2004, Age >= 15) %>% 
  dplyr::group_by(Year, Gender, scenario_name, IP_Key.ARTStatus, sim.ix) %>% 
  dplyr::summarize(On_ART = sum(On_ART * pop_scaling_factor), 
                   .groups = "keep") %>% 
  ungroup() %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female")) %>%
  group_by(Year, Gender, scenario_name, IP_Key.ARTStatus) %>% 
  summarize(On_ART = mean(On_ART), .groups = 'drop_last') %>% 
  pivot_wider(id_cols = c(Year, Gender, scenario_name), 
              names_from = IP_Key.ARTStatus,
              values_from = On_ART) %>% 
  mutate(Total = NeverOnART + OffART + OnARTPreVLS+ OnEffectiveART + OnNonSuppressiveART) %>% 
  mutate(VLS = OnEffectiveART/Total) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = VLS, color = scenario_name)) + 
  geom_point(data = VLS.table, mapping = aes(x = Year, y  = VLS), color = 'black') +
  facet_wrap(facets = vars(Gender), ncol = 2)
```

## VLS Coverage by Age

```{r, fig.height=10}
# From SHIMS, extracted by Kasturi
VLS.data <- read.csv(file = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/Data/SWZ_VLS_coverage.csv")
VLS.data <- VLS.data %>% 
  pivot_longer(cols = c(X2017, X2021), values_to = "VLS", names_to = "Year", names_prefix = "X") %>%
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))
VLS.data$Year = as.numeric(VLS.data$Year)


VLS.cov.by.age <- merge(
  sim.results.hbp %>% #filter(scenario_name == 'test') %>% 
    filter(Year >= 2004, Age >= 15, Age <= 65, IP_Key.ARTStatus == "OnEffectiveART") %>% 
    dplyr::group_by(Year, Age, Gender, scenario_name, sim.ix) %>% 
    dplyr::summarize(OnEffectiveART = sum(On_ART * pop_scaling_factor), 
                     .groups = "drop_last") %>% 
    group_by(Year, Age, Gender, scenario_name) %>% 
    summarize(OnEffectiveART = mean(OnEffectiveART), .groups = 'drop_last'),
  sim.results.hbp %>% #filter(scenario_name == 'test') %>% 
    filter(Year >= 2004, Age >= 15, Age <= 65, IP_Key.ARTStatus == "OnNonSuppressiveART") %>% 
    dplyr::group_by(Year, Age, Gender, scenario_name, sim.ix) %>% 
    dplyr::summarize(OnNonSuppressiveART = sum(On_ART * pop_scaling_factor), 
                     .groups = "drop_last") %>% 
    group_by(Year, Age, Gender, scenario_name) %>% 
    summarize(OnNonSuppressiveART = mean(OnNonSuppressiveART), .groups = 'drop_last'),
  by = c("Year", "Age", "Gender", "scenario_name")
) %>%
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female")) %>%
  mutate(Total = OnEffectiveART + OnNonSuppressiveART) %>% 
  mutate(VLS = OnEffectiveART/Total)


VLS.cov.by.age %>% 
  mutate(Age_factor = factor(Age)) %>%
  ggplot() + 
  geom_point(mapping = aes(x = Year, y = VLS, color = scenario_name)) + 
  geom_point(data = VLS.data %>% filter(Age >= 15, Age <=65, Age != 55, Age != 60) %>% 
               mutate(Age_factor = factor(Age)), 
             mapping = aes(x = Year, y = VLS), color = 'black') + 
  scale_y_continuous(limits = c(.5,1)) + 
  facet_grid(cols = vars(Gender), 
             rows = vars(Age_factor)
             )
```

```{r, fig.height=10}
sim.results.hbp %>% filter(scenario_name == 'test') %>% 
  filter(Year >= 2004, Age >= 15, Age <= 65) %>% 
  dplyr::group_by(Year, Age, Gender, scenario_name, IP_Key.ARTStatus, sim.ix) %>% 
  dplyr::summarize(On_ART = sum(On_ART * pop_scaling_factor), 
                   .groups = "keep") %>% 
  ungroup() %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female")) %>%
  group_by(Year, Age, Gender, scenario_name, IP_Key.ARTStatus) %>% 
  summarize(On_ART = mean(On_ART), .groups = 'drop_last') %>% 
  pivot_wider(id_cols = c(Year, Age, Gender, scenario_name), 
              names_from = IP_Key.ARTStatus,
              values_from = On_ART) %>% 
  mutate(Total = NeverOnART + OffART + OnARTPreVLS+ OnEffectiveART + OnNonSuppressiveART) %>% 
  mutate(VLS = OnEffectiveART/Total) %>% #arrange(Age, Gender, Year) %>% View()
  mutate(Age_factor = factor(Age)) %>%
  ggplot() + 
  geom_point(mapping = aes(x = Year, y = VLS, color = Gender)) + 
  geom_point(data = VLS.data %>% filter(Age >= 15, Age <=65, Age != 55, Age != 60) %>% 
               mutate(Age_factor = factor(Age)), 
             mapping = aes(x = Year, y = VLS), color = 'black') + 
  scale_y_continuous(limits = c(.5,1)) + 
  facet_grid(cols = vars(Gender), 
             rows = vars(Age_factor)
             )
```


```{r}
p1 <- sim.results.hbp %>% 
  filter(Year >= 2004, Age >= 15, Age <= 30) %>%  #65) %>% 
  dplyr::group_by(Year, Age, Gender, scenario_name, IP_Key.ARTStatus, sim.ix) %>% 
  dplyr::summarize(On_ART = sum(On_ART * pop_scaling_factor), 
                   .groups = "keep") %>% 
  ungroup() %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female")) %>%
  group_by(Year, Age, Gender, scenario_name, IP_Key.ARTStatus) %>% 
  summarize(On_ART = mean(On_ART), .groups = 'drop_last') %>% 
  pivot_wider(id_cols = c(Year, Age, Gender, scenario_name), 
              names_from = IP_Key.ARTStatus,
              values_from = On_ART) %>% 
  mutate(Total = NeverOnART + OffART + OnARTPreVLS+ OnEffectiveART + OnNonSuppressiveART) %>% 
  mutate(VLS = OnEffectiveART/Total) %>% 
  mutate(Age_factor = factor(Age)) %>%
  ggplot() + 
  geom_point(mapping = aes(x = Year, y = OnEffectiveART, color = scenario_name)) + 
  #geom_point(mapping = aes(x = Year, y = OnNonSuppressiveART, color = scenario_name)) +
  #scale_y_continuous(limits = c(.5,1)) + 
  facet_grid(cols = vars(Gender), 
             rows = vars(Age_factor),
             scales = "free_y"
             )


p2 <- sim.results.hbp %>% 
  filter(Year >= 2004, Age >= 15, Age <= 30) %>%  #65) %>% 
  dplyr::group_by(Year, Age, Gender, scenario_name, IP_Key.ARTStatus, sim.ix) %>% 
  dplyr::summarize(On_ART = sum(On_ART * pop_scaling_factor), 
                   .groups = "keep") %>% 
  ungroup() %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female")) %>%
  group_by(Year, Age, Gender, scenario_name, IP_Key.ARTStatus) %>% 
  summarize(On_ART = mean(On_ART), .groups = 'drop_last') %>% 
  pivot_wider(id_cols = c(Year, Age, Gender, scenario_name), 
              names_from = IP_Key.ARTStatus,
              values_from = On_ART) %>% 
  mutate(Total = NeverOnART + OffART + OnARTPreVLS+ OnEffectiveART + OnNonSuppressiveART) %>% 
  mutate(VLS = OnEffectiveART/Total) %>% 
  mutate(Age_factor = factor(Age)) %>%
  ggplot() + 
  #geom_point(mapping = aes(x = Year, y = OnEffectiveART, color = scenario_name)) + 
  geom_point(mapping = aes(x = Year, y = OnNonSuppressiveART, color = scenario_name)) +
  #scale_y_continuous(limits = c(.5,1)) + 
  facet_grid(cols = vars(Gender), 
             rows = vars(Age_factor),
             scales = "free_y"
             )

p1 + p2
```

## Prevalence by age

```{r}
sim.results.hbp %>% 
  filter(Year >= 2004, Age >= 15, Age <= 30) %>%  #65) %>% 
  dplyr::group_by(Year, Age, Gender, scenario_name, sim.ix) %>% 
  dplyr::summarize(Infected = sum(Infected * pop_scaling_factor), 
                   .groups = "keep") %>% 
  ungroup() %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female")) %>%
  group_by(Year, Age, Gender, scenario_name) %>% 
  summarize(Infected = mean(Infected), .groups = 'drop_last') %>% 
  mutate(Age_factor = factor(Age)) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Infected, color = scenario_name)) + 
  facet_grid(rows = vars(Age_factor),
             cols = vars(Gender),
             scales = "free_y")
```
### Bin prevalence by age
```{r}
#age_bins = c(15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65,99)
age_bins = c(15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65,99)
subset_years = c(2007, 2011, 2016, 2021)

# Subset data on years
data <- sim.results.hbp %>% filter(Year %in% subset_years)

# Age bins
age_labels = c()
for (i in 1:(length(age_bins) - 1)){
  age_labels <- append(age_labels, paste0("[",age_bins[i],":",age_bins[i + 1],")"))
}

# Label each age by its bin
data <- data %>% mutate(
  AgeBin = cut(Age, breaks = age_bins, right = FALSE)
  ) %>%
  filter(!is.na(AgeBin))
data$AgeBin_index = factor(data$AgeBin,labels = 1:length(age_labels))

# Calculate prevalence, grouping by age bin
data.prev <- data %>% EMODAnalyzeR::calculate.prevalence(
  stratify_columns = c("Year", "AgeBin_index", "AgeBin", "Gender", "scenario_name", "sim.id"),
  numerator = "Infected",
  denominator = "Population")

# Calculate mean prevalence across all sim runs
ageprev.data.mean <- data.prev %>%
  dplyr::group_by(Year, AgeBin_index, AgeBin, Gender, scenario_name) %>%
  dplyr::summarize(mean.Prevalence = mean(Prevalence),
            sd.Prevalence = sd(Prevalence),
            .groups = 'keep') %>%
  ungroup() %>%
  dplyr::mutate(upper = mean.Prevalence + 2*sd.Prevalence,
                lower = case_when(mean.Prevalence - 2 * sd.Prevalence > 0 ~ mean.Prevalence - 2 * sd.Prevalence,
                         mean.Prevalence - 2 * sd.Prevalence <= 0 ~ 0)
                )

# Transform data
ageprev.data.mean <- ageprev.data.mean %>% mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))
ageprev.data.mean <- ageprev.data.mean[order(ageprev.data.mean$scenario_name), ]
ageprev.data.mean$scenario_name <- as.factor(ageprev.data.mean$scenario_name)
```

```{r}
ageprev.data.mean %>% filter(scenario_name %in% c("carf.m100.f90", "carf.m85.f85")) %>% 
  filter(AgeBin_index %in% c(2,3,4,5), 
         Year %in% c(2016, 2021)) %>% 
  arrange(scenario_name, Gender, Year)
```


### Plot

```{r, fig.width= 12}
p.ageprev <- ageprev.data.mean %>% filter(scenario_name %in% c("carf.m100.f90", "carf.m85.f85")) %>% 
  mutate(scenario_name = as.factor(scenario_name)) %>% 
  ggplot() +
  geom_point(data = obs.prev.sheet.base,
             mapping = aes(x = AgeBin_index, y = Prevalence), 
             size = 3, color = 'black', shape = 0,
             show.legend = FALSE) +
  geom_errorbar(data = obs.prev.sheet.base,
             mapping = aes(x = AgeBin_index, ymin = lb, ymax = ub),
             size = 1, color = 'black',
             show.legend = FALSE) +
  # plot means
  # geom_point(
  #   mapping = aes(x = AgeBin_index, y = mean.Prevalence, color = scenario_name),
  #   size=2,
  #    show.legend = TRUE
  # ) +
  geom_line(
    mapping = aes(x = AgeBin_index, y = mean.Prevalence, color = scenario_name, group = scenario_name),
    size=1,
    show.legend = TRUE
  ) +
  # geom_errorbar(
  #   mapping = aes(x=AgeBin_index, ymin=lower, ymax=upper, color=Gender),
  #   width=.15, size=1,
  #  show.legend = FALSE) +
  facet_grid(cols = vars(Gender), rows = vars(Year)) +
  #xlab("Age") +
  #ylab("Prevalence") +
  theme_bw(base_size=24) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_discrete(
    breaks = 1:length(age_labels),
    labels = age_labels
    #labels = rep("",length(age_labels))
    ) +
  #scale_color_manual(values=c("blue", "red"))
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
  #theme(legend.position="bottom") + 
  theme(legend.position="bottom",
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        #strip.text.x = element_blank(),
        #strip.text.y = element_blank()
        ) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

p.ageprev
```


```{r}
ageprev.data.mean %>% filter(Year >2010) %>%
  merge(
    obs.prev.sheet.base %>% select(Year,Gender, AgeBin_index, Prevalence),
    by = c("Year", "AgeBin_index", "Gender")
  )  %>% 
  mutate(distance = (mean.Prevalence - Prevalence)**2/(sd.Prevalence)/(sd.Prevalence)) %>% 
  group_by(scenario_name) %>% 
  summarize(distance = sum(distance))


ageprev.data.mean %>% filter(Year >2010) %>%
  merge(
    obs.prev.sheet.base %>% select(Year,Gender, AgeBin_index, Prevalence),
    by = c("Year", "AgeBin_index", "Gender")
  )  %>% 
  mutate(distance = (mean.Prevalence - Prevalence)**2/(sd.Prevalence)/(sd.Prevalence)) %>% 
  group_by(scenario_name, Gender) %>% 
  summarize(distance = sum(distance))

```

```{r}
ageprev.data.mean %>% 
  merge(
    obs.prev.sheet.base %>% filter(Year > 2010) %>% select(Year,Gender, AgeBin_index, Prevalence),
    by = c("Year", "AgeBin_index", "Gender")
  )  %>% 
  mutate(distance = (mean.Prevalence - Prevalence)**2/(sd.Prevalence)/(sd.Prevalence)) %>% 
  group_by(scenario_name) %>% 
  summarize(distance = sum(distance))


ageprev.data.mean %>% 
  merge(
    obs.prev.sheet.base  %>% filter(Year > 2010) %>% select(Year,Gender, AgeBin_index, Prevalence),
    by = c("Year", "AgeBin_index", "Gender")
  )  %>% 
  mutate(distance = (mean.Prevalence - Prevalence)**2/(sd.Prevalence)/(sd.Prevalence)) %>% 
  group_by(scenario_name, Gender) %>% 
  summarize(distance = sum(distance))
```


## Incidence

The real question is, do we improve upon incidence from before?

```{r}
 # 2011 SHIMS
# <https://www-ncbi-nlm-nih-gov.ezproxy.med.nyu.edu/pmc/articles/PMC5291824/>
# 2016
# <https://phia.icap.columbia.edu/wp-content/uploads/2019/05/SHIMS2_Final-Report_05.03.2019_forWEB.pdf>
# 2021
# <https://phia.icap.columbia.edu/wp-content/uploads/2023/12/241123_SHIMS_ENG_RR3_Final-1.pdf>
# Ages 15-49
incidence.data <- data.table(Year = c(2011, 2011, 2016, 2016, 2021, 2021),
                                     Gender = c("Male", "Female"),
                                     inc = c(1.7,3.1,.99, 1.99, .2, 1.45),
                                     lb = c(1.3, 2.6, .032, 1.09, 0, 0.69 ),
                                     ub = c(2.1,3.7, 1.66, 2.88, .48, 2.2))
```

```{r, fig.width=10}
data <- sim.results.hbp %>% filter(Age >= 15, Age < 50)

# Calculate incidence
data$Year_Integer <- floor((data$Year-0.5))
# Aggregate number of new infections each year, broken down by Year_Integer and Gender
trajectories_IR.1a <- aggregate(Newly.Infected ~ Year_Integer+Gender + sim.id+scenario_name, data=data,FUN=sum)
#Make the denominator as HIV-negative individuals
trajectories_IR.2 <- aggregate(Population - Infected ~ Year+Gender + sim.id+scenario_name, data=data, FUN=sum)
trajectories_IR.2$Year_Integer <- floor(trajectories_IR.2$Year-0.5)
#remove second instance of duplicate rows
trajectories_IR.2 <- trajectories_IR.2[!duplicated(trajectories_IR.2[c("Year_Integer","Gender", "sim.id","scenario_name")]),]
trajectories_IR.2 <- trajectories_IR.2[-match("Year",names(trajectories_IR.2))]
trajectories_IRoverall <- merge(trajectories_IR.1a, trajectories_IR.2, by=c("Year_Integer","Gender","sim.id","scenario_name"))
trajectories_IRoverall$incidence <- trajectories_IRoverall$Newly.Infected / (trajectories_IRoverall$Population)
data <- trajectories_IRoverall %>% dplyr::rename(Year = Year_Integer)

# Calculate mean incidence across all sim runs
inc.data.mean <- data %>%
  dplyr::group_by(Year, Gender, scenario_name) %>%
  dplyr::summarize(mean.Incidence = mean(incidence),
                  sd.Incidence = sd(incidence),
            .groups = 'keep') %>%
  ungroup() %>%
  dplyr::mutate(upper = mean.Incidence + 2*sd.Incidence,
                lower = case_when(mean.Incidence - 2 * sd.Incidence > 0 ~ mean.Incidence - 2 * sd.Incidence,
                         mean.Incidence - 2 * sd.Incidence <= 0 ~ 0)
                )

# Transform data
inc.data.mean <- inc.data.mean %>% mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

```

### Plot 
```{r, fig.height=12}
p.inc <- inc.data.mean %>%
  ggplot() +
  # plot means
  geom_point(
    mapping = aes(x = Year, y = mean.Incidence*100, color = Gender),
    size=2,
     show.legend = FALSE
  ) +
  geom_errorbar(
    mapping = aes(x=Year, ymin=lower*100, ymax=upper*100, color=Gender),
    width=.15, size=1,
   show.legend = FALSE) +
  geom_point(data = incidence.data, 
             mapping = aes(x = Year, y = inc), color = 'black') + 
  geom_errorbar(data = incidence.data, 
    mapping = aes(x = Year, ymin = lb, ymax = ub), color = 'black') + 
  facet_grid(cols = vars(Gender), rows = vars(scenario_name)) +
  #scale_color_manual(values=c("blue", "red")) +
  xlab("Age") +
  ylab("Incidence (%)") +
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_continuous(breaks = c(2005, 2010, 2015, 2020, 2025),
                     limits = c(2005, 2025)) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) 
  
p.inc
```

```{r}
inc.data.mean %>% filter(Year %in% c(2011, 2016, 2021)) %>% 
  merge(incidence.data, by = c("Year", "Gender")) %>% 
  mutate(distance = (mean.Incidence*100 - inc)**2/(sd.Incidence*100)/(sd.Incidence*100)) %>% 
  group_by(scenario_name) %>% 
  summarize(distance = sum(distance))
```
```{r}
inc.data.mean %>% filter(Year %in% c(2011, 2016, 2021)) %>% 
  merge(incidence.data, by = c("Year", "Gender")) %>% 
  mutate(distance = (mean.Incidence*100 - inc)**2/(sd.Incidence*100)/(sd.Incidence*100)) %>% 
  group_by(scenario_name, Gender) %>% 
  summarize(distance = sum(distance))
```

### Combining metrics for comparison

```{r}

merge(
  inc.data.mean %>% filter(Year %in% c(2011, 2016, 2021)) %>% 
    merge(incidence.data, by = c("Year", "Gender")) %>% 
    mutate(distance = (mean.Incidence*100 - inc)**2/(sd.Incidence*100)/(sd.Incidence*100)) %>% 
    group_by(scenario_name) %>% 
    summarize(distance = sum(distance)),
  ageprev.data.mean %>% filter(Year >2010) %>%
    merge(
      obs.prev.sheet.base %>% select(Year,Gender, AgeBin_index, Prevalence),
      by = c("Year", "AgeBin_index", "Gender")
    )  %>% 
    mutate(distance = (mean.Prevalence - Prevalence)**2/(sd.Prevalence)/(sd.Prevalence)) %>% 
    group_by(scenario_name) %>% 
    summarize(distance = sum(distance)),
  by = c("scenario_name")
) %>% 
  mutate(distance = distance.x + distance.y) %>% 
  arrange(distance) %>% 
  head(11)

```


### By Age

```{r, fig.width=10}
# age_bins = c(15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65,99)
# subset_years = c(2007, 2007.5, 2011, 2011.5, 2016, 2016.5, 2021, 2021.5)
# 
# # Subset data on years
# data <- sim.results.hbp %>% filter(Year %in% subset_years)
# 
# # Age bins
# age_labels = c()
# for (i in 1:(length(age_bins) - 1)){
#   age_labels <- append(age_labels, paste0("[",age_bins[i],":",age_bins[i + 1],")"))
# }
# # Label each age by its bin
# data <- data %>% mutate(
#   AgeBin = cut(Age, breaks = age_bins, right = FALSE)
#   ) %>%
#   filter(!is.na(AgeBin))
# data$AgeBin_index = factor(data$AgeBin,labels = 1:11)#length(age_labels))
# 
# # Calculate incidence
# data$Year_Integer <- floor((data$Year-0.5))
# # Aggregate number of new infections each year, broken down by Year_Integer and Gender
# trajectories_IR.1a <- aggregate(Newly.Infected ~ Year_Integer+Gender+AgeBin_index + AgeBin + sim.id+scenario_name, data=data,FUN=sum)
# #Make the denominator as HIV-negative individuals
# trajectories_IR.2 <- aggregate(Population - Infected ~ Year+Gender+AgeBin_index + AgeBin + sim.id+scenario_name, data=data, FUN=sum)
# trajectories_IR.2$Year_Integer <- floor(trajectories_IR.2$Year-0.5)
# #remove second instance of duplicate rows
# trajectories_IR.2 <- trajectories_IR.2[!duplicated(trajectories_IR.2[c("Year_Integer","Gender","AgeBin_index", "AgeBin", "sim.id","scenario_name")]),]
# trajectories_IR.2 <- trajectories_IR.2[-match("Year",names(trajectories_IR.2))]
# trajectories_IRoverall <- merge(trajectories_IR.1a, trajectories_IR.2, by=c("Year_Integer","Gender","AgeBin_index", "AgeBin", "sim.id","scenario_name"))
# trajectories_IRoverall$incidence <- trajectories_IRoverall$Newly.Infected / (trajectories_IRoverall$Population)
# data <- trajectories_IRoverall %>% dplyr::rename(Year = Year_Integer)
# 
# # Calculate mean prevalence across all sim runs
# data.mean <- data %>%
#   dplyr::group_by(Year, AgeBin_index, AgeBin, Gender, scenario_name) %>%
#   dplyr::summarize(mean.Incidence = mean(incidence),
#                   sd.Incidence = sd(incidence),
#             .groups = 'keep') %>%
#   ungroup() %>%
#   dplyr::mutate(upper = mean.Incidence + 2*sd.Incidence,
#                 lower = case_when(mean.Incidence - 2 * sd.Incidence > 0 ~ mean.Incidence - 2 * sd.Incidence,
#                          mean.Incidence - 2 * sd.Incidence <= 0 ~ 0)
#                 )
# 
# # Transform data
# inc.age.data.mean <- data.mean %>% mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))


```

### Plot
```{r}
p <- inc.age.data.mean %>% filter(Year %in% c(2007, 2011, 2016, 2021)) %>% 
  ggplot() +
  # plot means
  geom_point(
    mapping = aes(x = AgeBin_index, y = mean.Incidence, color = scenario_name),
    size=2,
     show.legend = TRUE
  ) +
  geom_line(
    mapping = aes(x = AgeBin_index, y = mean.Incidence, color = scenario_name, group = scenario_name),
    size=.25,
     show.legend = FALSE
  ) +
  # geom_errorbar(
  #   mapping = aes(x=AgeBin_index, ymin=lower, ymax=upper, color=scenario_name),
  #   width=.15, size=1,
  #  show.legend = FALSE) +
  facet_grid(cols = vars(Gender), rows = vars(Year)) +
  xlab("Age") +
  ylab("Incidence (%)") +
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_discrete(
    breaks = 1:length(age_labels),
    #labels = age_labels
    labels = rep("", length(age_labels))
    ) +
  scale_y_continuous(#breaks = seq(0,.4,.1),
                       labels = scales::percent_format(accuracy = 1)) +
  theme(legend.position="bottom") +
  # theme(axis.title.x=element_blank(),
  #       axis.text.y = element_blank(),
  #       axis.title.y=element_blank(),
  #       strip.text.x = element_blank(),
  #       strip.text.y = element_blank()) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
  
p
```

# Incidence by age

### Incidence comparison with SHIMS report

```{r}
# SHIMS annual report on incidence, 2016 and 2021
inc.data <- data.table(
  Year = c(rep(2016, 6), rep(2021, 6)),
  Gender = c("Male","Male","Male", "Female", "Female", "Female"),
  AgeBin = c("[15,25)", "[25:35)","[35:50)", "[15,25)", "[25:35)","[35:50)"),
  AgeBin_index = c(1,2,3,1,2,3),
  Incidence = c(.79, 1.5, .68, 1.87, 1.84, 2.4, 
                .17, .38, 0.77, 1.63, 1.90, .42),
  lb = c(.07, 0, 0 , .76, .17, .45,
         0,0,0, 0.43, 0.45, 0),
  ub = c( 1.5, 3.06, 1.85, 2.98, 3.48, 4.33,
          .5, 1.13, 1.54, 2.81, 3.33, 1.24)
)


```

### Incidence by age calc
```{r}
age_bins = c(15, 25, 35, 50)
subset_years = c(2016, 2016.5, 2021, 2021.5)

# Subset data on years
data <- sim.results.hbp %>% filter(Year %in% subset_years)

# Calculate incidence
data$Year_Integer <- floor((data$Year-0.5))
# Aggregate number of new infections each year, broken down by Year_Integer and Gender
trajectories_IR.1a <- aggregate(Newly.Infected ~ Year_Integer+Gender+Age + sim.id+scenario_name, data=data,FUN=sum)
#Make the denominator as HIV-negative individuals
trajectories_IR.2 <- aggregate(Population - Infected ~ Year+Gender+Age + sim.id+scenario_name, data=data, FUN=sum)
trajectories_IR.2$Year_Integer <- floor(trajectories_IR.2$Year-0.5)
#remove second instance of duplicate rows
trajectories_IR.2 <- trajectories_IR.2[!duplicated(trajectories_IR.2[c("Year_Integer","Gender","Age", "sim.id","scenario_name")]),]
trajectories_IR.2 <- trajectories_IR.2[-match("Year",names(trajectories_IR.2))]
trajectories_IRoverall <- merge(trajectories_IR.1a, trajectories_IR.2, by=c("Year_Integer","Gender","Age", "sim.id","scenario_name"))
trajectories_IRoverall$incidence <- trajectories_IRoverall$Newly.Infected / (trajectories_IRoverall$Population)
data <- trajectories_IRoverall %>% dplyr::rename(Year = Year_Integer)

# Age bins
age_labels = c()
for (i in 1:(length(age_bins) - 1)){
  age_labels <- append(age_labels, paste0("[",age_bins[i],":",age_bins[i + 1],")"))
}

# Label each age by its bin
data <- data %>% mutate(
  AgeBin = cut(Age, breaks = age_bins, right = FALSE)
  ) %>%
  filter(!is.na(AgeBin))
data$AgeBin_index = factor(data$AgeBin,labels = 1:length(age_labels))

# Calculate mean incidence across all sim runs
inc.age.data.mean <- data %>%
  dplyr::group_by(Year, AgeBin_index, AgeBin, Gender, scenario_name) %>%
  dplyr::summarize(mean.Incidence = mean(incidence),
                  sd.Incidence = sd(incidence),
            .groups = 'keep') %>%
  ungroup() %>%
  dplyr::mutate(
    upper = mean.Incidence + 2*sd.Incidence,
    lower = case_when(
      mean.Incidence - 2 * sd.Incidence > 0 ~ mean.Incidence - 2 * sd.Incidence,
      mean.Incidence - 2 * sd.Incidence <= 0 ~ 0)
    )  %>% mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))
```

### Plot
```{r, fig.width=10}
p.inc.age <- inc.age.data.mean %>% filter(Year == 2016) %>%  filter(scenario_name %in% c("test", "carf.m85.f85")) %>% 
  ggplot() +
  # plot means
  geom_point(
    mapping = aes(x = AgeBin_index, y = mean.Incidence*100, color = Gender),
    size=2,
     show.legend = TRUE
  ) +
  geom_errorbar(
    mapping = aes(x=AgeBin_index, ymin=lower*100, ymax=upper*100, color=Gender),
    width=.15, size=1,
   show.legend = FALSE) +
  # shims data 
  geom_point(
    data = inc.data %>% filter(Year == 2016), 
    mapping = aes(x = AgeBin_index, y = Incidence), 
    size = 3, shape = 0, color = 'black'
  ) + 
  geom_errorbar(
    data = inc.data %>% filter(Year == 2016),
    mapping = aes(x = AgeBin_index, ymin = lb, ymax = ub),
    color = 'black'
  ) + 
  facet_grid(cols = vars(Gender), rows = vars(scenario_name)) +
  xlab("Age") +
  ylab("Incidence (%)") +
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_discrete(
    breaks = 1:length(age_labels),
    labels = age_labels
    #@labels = rep("", length(age_labels))
    ) +
  ylim(0,4.5) + 
  scale_color_manual(values=c("blue", "red"))
  
p.inc.age
```

## New HIV Infections

```{r}
sim.results.hbp %>%
  filter(Year >= 2004, Age <= 65) %>% 
  group_by(Year, Gender, scenario_name, sim.ix) %>%
  summarize()
  
```


# Mortality

Mortality rate, number of deaths per number infected:

```{r}
sim.results.hbp %>% 
  filter(Year >= 2004, Age <= 65) %>% 
  group_by(scenario_name, sim.ix) %>% 
  summari
```



