---
title: "Modeling Duet"
output: html_document
date: "2025-10-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Introduction

* Produce a slide deck and series of outputs illustrating the new and improved calibrated model.
* Produce aggregated tables

# Libraries 
```{r}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(data.table))
library(magrittr)
library(rsample)
library(patchwork)
```


## Constants
```{r}
SWZ_CENSUS_YEAR = 2017
SWZ_CENSUS_POP = 1148000 # UN WPP 2019, according to SWZ national census 2017 1093238

current_date <- Sys.Date()
date_string_ymd <- format(current_date, format = "%Y%m%d")
```


# Preliminary checks

The purpose here will be to make sure that certain events are firing as intended, that the interventions are going out as designed

## Read in data

```{r}
experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet-baseline___2025_10_29_17_20_05_919018/"

results.baseline.2 <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "baseline.2",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet-baseline___2025_10_31_16_27_37_257804/"

results.baseline <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "baseline",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

baseline.comp <- rbind(
  results.baseline,
  results.baseline.2
  # ,
  # results.cut.perm,
  # results.cut.2025,
  # results.cut.la,
  # results.cut.perm.max
)

sim.results.pop.scaling <- baseline.comp %>%
  filter(Year == SWZ_CENSUS_YEAR) %>%
  group_by(sim.ix, scenario_name) %>%
  summarize(total.pop = sum(Population), .groups = 'drop_last') %>%
  mutate(pop_scaling_factor = SWZ_CENSUS_POP/total.pop)

baseline.comp <- baseline.comp %>%
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.ix", "scenario_name")
  )

```


```{r}
dat <- baseline.comp %>% 
  filter(Age > 15) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    On_ART = sum(On_ART * pop_scaling_factor),
    Infected = sum(Infected * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    On_ART = mean(On_ART),
    Infected = mean(Infected)
  ) %>% 
  ungroup() %>% 
  mutate(ARTCov = On_ART/Infected)


```

```{r}
dat <- baseline.comp %>% 
  mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Newly.Infected = sum(Newly.Infected * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Newly.Infected = mean(Newly.Infected)
  )

dat %>% 
  filter(Year >=2025) %>% 
  group_by(scenario_name) %>% 
  summarize(Newly.Infected = sum(Newly.Infected)) %>% 
  mutate(
    Newly.Infected.baseline = rep(
  dat %>% 
    filter(Year >=2025) %>% 
    group_by(scenario_name) %>% 
    summarize(Newly.Infected.baseline = sum(Newly.Infected)) %>% 
    filter(scenario_name == 'baseline') %>% .$Newly.Infected.baseline,
  2)
  ) %>% 
  mutate(
    diff = Newly.Infected - Newly.Infected.baseline
  ) %>% 
  mutate(
    pct = diff/Newly.Infected.baseline
  )

dat
```


```{r}
experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet-baseline___2025_10_29_12_15_02_503307/"

results.baseline <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "baseline",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)


experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet-baseline___2025_10_24_18_07_58_215192/"

results.baseline.current <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "baseline.current",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)


 experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet-cut_perm___2025_10_24_16_48_14_037578/"

results.cut.perm <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "cut.perm",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet-cut_2025___2025_10_24_16_48_16_372521/"

results.cut.2025 <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "cut.2025",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender",  "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet-cut_2025_la___2025_10_24_16_48_18_683696/"

results.cut.la <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "cut.la",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet-cut_perm_max___2025_10_24_16_48_20_987872/"

results.cut.perm.max <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "cut.perm.max",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

duet.results <- rbind(
  results.baseline,
  results.baseline.current
  # ,
  # results.cut.perm,
  # results.cut.2025,
  # results.cut.la,
  # results.cut.perm.max
)

sim.results.pop.scaling <- duet.results %>%
  filter(Year == SWZ_CENSUS_YEAR) %>%
  group_by(sim.ix, scenario_name) %>%
  summarize(total.pop = sum(Population), .groups = 'drop_last') %>%
  mutate(pop_scaling_factor = SWZ_CENSUS_POP/total.pop)

duet.results <- duet.results %>%
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.ix", "scenario_name")
  )

```

## Checks

### Check on ART dropout

```{r}
dat <- duet.results %>% 
  filter(Year > 2020) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    PEPFAR_ARTDropout_Yes = sum(PEPFAR_ARTDropout_Yes * pop_scaling_factor),
    PEPFAR_ARTDropout_No = sum(PEPFAR_ARTDropout_No * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    PEPFAR_ARTDropout_Yes = mean(PEPFAR_ARTDropout_Yes), 
    PEPFAR_ARTDropout_No = mean(PEPFAR_ARTDropout_No)
  ) 

dat %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = PEPFAR_ARTDropout_No , color = scenario_name))


dat %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = PEPFAR_ARTDropout_Yes , color = scenario_name))

dat %>% filter(Year == 2025.5)
```


### Check on ART initiation rates

```{r}
dat <- duet.results %>% 
  filter(Year > 2020) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    OnART1_initiate = sum(OnART1_initiate * pop_scaling_factor),
    OnART1_initiate_FAILURE = sum(OnART1_initiate_FAILURE * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    OnART1_initiate = mean(OnART1_initiate), 
    OnART1_initiate_FAILURE = mean(OnART1_initiate_FAILURE)
  ) %>% 
  mutate(rate = OnART1_initiate/(OnART1_initiate_FAILURE + OnART1_initiate))

dat %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = OnART1_initiate_FAILURE , color = scenario_name))


dat %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = rate , color = scenario_name))


```


### Check on ART Coverage

```{r}
dat <- duet.results %>% 
  filter(Age > 15) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    On_ART = sum(On_ART * pop_scaling_factor),
    Infected = sum(Infected * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    On_ART = mean(On_ART),
    Infected = mean(Infected)
  ) %>% 
  ungroup() %>% 
  mutate(ARTCov = On_ART/Infected)

dat %>% 
  filter(Year >= 2020) %>% 
  filter(scenario_name != "cut.perm.max") %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = ARTCov, color = scenario_name),
            linewidth = 1, show.legend = TRUE) +
  #scale_color_manual(values = c( "black", "#C41000", "#E69F00", "#0072B2")) +
  scale_x_continuous("Year", breaks = c(2020, 2025, 2030)) +
  #scale_y_continuous("ART Coverage") +
  scale_y_continuous("") +
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(),
        #axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        axis.title.y = element_blank(),
        #plot.title = element_text(hjust = 0.5),
        text = element_text(family = "sans"),
        axis.text = element_text(size = 14),
        axis.title= element_text(size = 16))
```


### PrEP Distribution

Both oral and LA

```{r}
dat <- duet.results %>% 
  filter(Year > 2020) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Initiate_PrEP = sum(Initiate_PrEP * pop_scaling_factor),
    Initiate_LAPrEP = sum(Initiate_LAPrEP * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Initiate_PrEP = mean(Initiate_PrEP), 
    Initiate_LAPrEP = mean(Initiate_LAPrEP)
  ) 

dat %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Initiate_PrEP , color = scenario_name))
```

```{r}
dat %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Initiate_LAPrEP , color = scenario_name))
```

### PrEP coverage

```{r}
dat <- duet.results %>% 
  filter(Year > 2020) %>% 
  group_by(sim.ix, scenario_name, Year, IP_Key.OnPrEP) %>% 
  summarize(
    Population = sum(Population * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year,IP_Key.OnPrEP) %>% 
  summarize(
    Population = mean(Population)
  ) 

dat %>% 
  pivot_wider(id_cols = c(scenario_name, Year),
              values_from = Population,
              names_from = IP_Key.OnPrEP) %>% 
  mutate(PrEP_cov = `TRUE`/(`FALSE` + `TRUE`)) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = PrEP_cov, color = scenario_name)) 

```


### VMMC Distribution

```{r}
dat <- duet.results %>% 
  filter(Year > 2020) %>% 
  #mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Program_VMMC = sum(Program_VMMC * pop_scaling_factor),
    Program_VMMC_Uptake = sum(Program_VMMC_Uptake * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Program_VMMC = mean(Program_VMMC),
    Program_VMMC_Uptake = mean(Program_VMMC_Uptake)
  ) %>% 
  mutate(
    rate = case_when(Program_VMMC_Uptake == 0 ~ 0,
                     Program_VMMC_Uptake > 0 ~ Program_VMMC/Program_VMMC_Uptake)
  )

dat %>%
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Program_VMMC, color = scenario_name))


dat %>%
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = rate, color = scenario_name))

```

# Produce results

## PLHIV

```{r}
dat <- duet.results %>% 
  #mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Infected = sum(Infected * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Infected = mean(Infected)
  )

dat %>% 
  filter(Year > 2020) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Infected, color = scenario_name))
```


## New HIV Infections

```{r}
dat <- duet.results %>% 
  mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Newly.Infected = sum(Newly.Infected * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Newly.Infected = mean(Newly.Infected)
  )


dat %>% 
  filter(Year > 2020) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Newly.Infected, color = scenario_name))
```

```{r}
dat %>% 
  filter(Year >=2025) %>% 
  group_by(scenario_name) %>% 
  summarize(Newly.Infected = sum(Newly.Infected)) %>% 
  mutate(
    Newly.Infected.baseline = rep(
  dat %>% 
    filter(Year >=2025) %>% 
    group_by(scenario_name) %>% 
    summarize(Newly.Infected.baseline = sum(Newly.Infected)) %>% 
    filter(scenario_name == 'baseline') %>% .$Newly.Infected.baseline,
  5)
  ) %>% 
  mutate(
    diff = Newly.Infected - Newly.Infected.baseline
  ) %>% 
  mutate(
    pct = diff/Newly.Infected.baseline
  )

```


## HIV-related deaths

```{r}
dat <- duet.results %>% 
  mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Died_from_HIV = sum(Died_from_HIV * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Died_from_HIV = mean(Died_from_HIV)
  )


dat %>% 
  filter(Year > 2020) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Died_from_HIV, color = scenario_name))
```


```{r}
dat %>% 
  filter(Year >=2025) %>% 
  group_by(scenario_name) %>% 
  summarize(Died_from_HIV = sum(Died_from_HIV)) %>% 
  mutate(
    Died_from_HIV.baseline = rep(
  dat %>% 
    filter(Year >=2025) %>% 
    group_by(scenario_name) %>% 
    summarize(Died_from_HIV.baseline = sum(Died_from_HIV)) %>% 
    filter(scenario_name == 'baseline') %>% .$Died_from_HIV.baseline,
  5)
  ) %>% 
  mutate(
    diff = Died_from_HIV - Died_from_HIV.baseline
  ) %>% 
  mutate(
    pct = diff/Died_from_HIV.baseline
  )
```


## ART initiations

```{r}
dat <- duet.results %>% 
  mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    OnART1_initiate = sum(OnART1_initiate * pop_scaling_factor),
    OnART1_initiate_FAILURE = sum(OnART1_initiate_FAILURE * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    OnART1_initiate = mean(OnART1_initiate),
    OnART1_initiate_FAILURE = mean(OnART1_initiate_FAILURE)
  )


dat %>% 
  filter(Year > 2020) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = OnART1_initiate, color = scenario_name))


dat %>% 
  filter(Year > 2020) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = OnART1_initiate_FAILURE, color = scenario_name))
```


```{r}
dat %>% 
  filter(Year >=2025) %>% 
  group_by(scenario_name) %>% 
  summarize(OnART1_initiate = sum(OnART1_initiate)) %>% 
  mutate(
    OnART1_initiate.baseline = rep(
  dat %>% 
    filter(Year >=2025) %>% 
    group_by(scenario_name) %>% 
    summarize(OnART1_initiate.baseline = sum(OnART1_initiate)) %>% 
    filter(scenario_name == 'baseline') %>% .$OnART1_initiate.baseline,
  5)
  ) %>% 
  mutate(
    diff = OnART1_initiate - OnART1_initiate.baseline
  ) %>% 
  mutate(
    pct = diff/OnART1_initiate.baseline
  )
```

What is the excess in ART initiations beyond baseline?
```{r}
dat %>% 
  filter(Year >= 2025) %>% 
  arrange(Year)
```





## PrEP initiations

```{r}
dat <- duet.results %>% 
  mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Initiate_PrEP = sum(Initiate_PrEP * pop_scaling_factor),
    Initiate_LAPrEP = sum(Initiate_LAPrEP * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Initiate_PrEP = mean(Initiate_PrEP),
    Initiate_LAPrEP = mean(Initiate_LAPrEP)
  )

dat %>% 
  filter(Year > 2020) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Initiate_PrEP, color = scenario_name))
```


```{r}
dat %>% 
  filter(Year > 2020) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Initiate_LAPrEP, color = scenario_name))
```

## VMMC distributed

```{r}
dat <- duet.results %>% 
  mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Program_VMMC = sum(Program_VMMC * pop_scaling_factor),
    Program_VMMC_Uptake = sum(Program_VMMC_Uptake * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Program_VMMC = mean(Program_VMMC),
    Program_VMMC_Uptake = mean(Program_VMMC_Uptake)
  )

dat %>% 
  filter(Year > 2020) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Program_VMMC, color = scenario_name))


```

```{r}
dat %>% 
  filter(Year > 2020) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Program_VMMC_Uptake, color = scenario_name))

```


```{r}
dat %>% 
  filter(Year >= 2020) %>% 
  mutate(ratio = Program_VMMC/Program_VMMC_Uptake) %>% View
```

```{r}
results.cut.2025 %>% 
  filter(Year >= 2025) %>% 
  group_by(
  scenario_name, sim.ix, Year) %>% 
  summarize(Died_from_HIV = sum(Died_from_HIV),
            Newly.Infected = sum(Newly.Infected)) %>%
  group_by(scenario_name, Year) %>% 
  summarize(Died_from_HIV = mean(Died_from_HIV),
            Newly.Infected = mean(Newly.Infected))

```

```{r}
results.cut.la %>% 
  filter(Year >= 2025) %>% 
  group_by(
  scenario_name, sim.ix, Year) %>% 
  summarize(Died_from_HIV = sum(Died_from_HIV),
            Newly.Infected = sum(Newly.Infected)) %>%
  group_by(scenario_name, Year) %>% 
  summarize(Died_from_HIV = mean(Died_from_HIV),
            Newly.Infected = mean(Newly.Infected))
```



## Prevalence by age

```{r}
lowerinc.results %>% 
  filter(Year >= 2004, Age >= 15, Age <= 30) %>%  #65) %>% 
  dplyr::group_by(Year, Age, Gender, scenario_name, sim.ix) %>% 
  dplyr::summarize(Infected = sum(Infected * pop_scaling_factor), 
                   .groups = "keep") %>% 
  ungroup() %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female")) %>%
  group_by(Year, Age, Gender, scenario_name) %>% 
  summarize(Infected = mean(Infected), .groups = 'drop_last') %>% 
  mutate(Age_factor = factor(Age)) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Infected, color = scenario_name)) + 
  facet_grid(rows = vars(Age_factor),
             cols = vars(Gender),
             scales = "free_y")
```
### Bin prevalence by age
```{r}
#age_bins = c(15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65,99)
age_bins = c(15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65,99)
subset_years = c(2007, 2011, 2016, 2021)

# Subset data on years
data <- lowerinc.results %>% filter(Year %in% subset_years)

# Age bins
age_labels = c()
for (i in 1:(length(age_bins) - 1)){
  age_labels <- append(age_labels, paste0("[",age_bins[i],":",age_bins[i + 1],")"))
}

# Label each age by its bin
data <- data %>% mutate(
  AgeBin = cut(Age, breaks = age_bins, right = FALSE)
  ) %>%
  filter(!is.na(AgeBin))
data$AgeBin_index = factor(data$AgeBin,labels = 1:length(age_labels))

# Calculate prevalence, grouping by age bin
data.prev <- data %>% EMODAnalyzeR::calculate.prevalence(
  stratify_columns = c("Year", "AgeBin_index", "AgeBin", "Gender", "scenario_name", "sim.id"),
  numerator = "Infected",
  denominator = "Population")

# Calculate mean prevalence across all sim runs
ageprev.data.mean <- data.prev %>%
  dplyr::group_by(Year, AgeBin_index, AgeBin, Gender, scenario_name) %>%
  dplyr::summarize(mean.Prevalence = mean(Prevalence),
            sd.Prevalence = sd(Prevalence),
            .groups = 'keep') %>%
  ungroup() %>%
  dplyr::mutate(upper = mean.Prevalence + 2*sd.Prevalence,
                lower = case_when(mean.Prevalence - 2 * sd.Prevalence > 0 ~ mean.Prevalence - 2 * sd.Prevalence,
                         mean.Prevalence - 2 * sd.Prevalence <= 0 ~ 0)
                )

# Transform data
ageprev.data.mean <- ageprev.data.mean %>% mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))
ageprev.data.mean <- ageprev.data.mean[order(ageprev.data.mean$scenario_name), ]
ageprev.data.mean$scenario_name <- as.factor(ageprev.data.mean$scenario_name)
```

```{r}
ageprev.data.mean %>% 
  filter(AgeBin_index %in% c(2,3,4,5), 
         Year %in% c(2016, 2021)) %>% 
  arrange(scenario_name, Gender, Year)
```


### Plot

```{r}
ingest.file.base = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/Data/calibration_ingest_form-Swaziland_ART_vars--UPDATED--2023-07.xlsm"

obs.prev.sheet.base <- EMODAnalyzeR::read.ingest.sheet(ingest.file.base, "Obs-Prevalence")
obs.prev.sheet.base <- obs.prev.sheet.base %>% filter(!is.na(AgeBin))

# Reformat the prevalence data:
obs.prev.sheet.base <- obs.prev.sheet.base %>% 
  mutate(AgeBin_index = factor(obs.prev.sheet.base$AgeBin,labels = 1:length(age_labels)))
```


```{r, fig.width= 12}
p.ageprev <- ageprev.data.mean %>% #filter(scenario_name %in% c("carf.m100.f90", "carf.m85.f85")) %>% 
  mutate(scenario_name = as.factor(scenario_name)) %>% 
  ggplot() +
  geom_point(data = obs.prev.sheet.base,
             mapping = aes(x = AgeBin_index, y = Prevalence), 
             size = 3, color = 'black', shape = 0,
             show.legend = FALSE) +
  geom_errorbar(data = obs.prev.sheet.base,
             mapping = aes(x = AgeBin_index, ymin = lb, ymax = ub),
             size = 1, color = 'black',
             show.legend = FALSE) +
  # plot means
  # geom_point(
  #   mapping = aes(x = AgeBin_index, y = mean.Prevalence, color = scenario_name),
  #   size=2,
  #    show.legend = TRUE
  # ) +
  geom_line(
    mapping = aes(x = AgeBin_index, y = mean.Prevalence, color = scenario_name, group = scenario_name),
    size=1,
    show.legend = TRUE
  ) +
  # geom_errorbar(
  #   mapping = aes(x=AgeBin_index, ymin=lower, ymax=upper, color=Gender),
  #   width=.15, size=1,
  #  show.legend = FALSE) +
  facet_grid(cols = vars(Gender), rows = vars(Year)) +
  #xlab("Age") +
  #ylab("Prevalence") +
  theme_bw(base_size=24) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_discrete(
    breaks = 1:length(age_labels),
    labels = age_labels
    #labels = rep("",length(age_labels))
    ) +
  #scale_color_manual(values=c("blue", "red"))
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
  #theme(legend.position="bottom") + 
  theme(legend.position="bottom",
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        #strip.text.x = element_blank(),
        #strip.text.y = element_blank()
        ) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

p.ageprev
```

# Incidence comparison with SHIMS report

```{r}
# SHIMS annual report on incidence, 2016 and 2021
inc.data <- data.table(
  Year = c(rep(2016, 6), rep(2021, 6)),
  Gender = c("Male","Male","Male", "Female", "Female", "Female"),
  AgeBin = c("[15,25)", "[25:35)","[35:50)", "[15,25)", "[25:35)","[35:50)"),
  AgeBin_index = c(1,2,3,1,2,3),
  Incidence = c(.79, 1.5, .68, 1.87, 1.84, 2.4, 
                .17, .38, 0.77, 1.63, 1.90, .42),
  lb = c(.07, 0, 0 , .76, .17, .45,
         0,0,0, 0.43, 0.45, 0),
  ub = c( 1.5, 3.06, 1.85, 2.98, 3.48, 4.33,
          .5, 1.13, 1.54, 2.81, 3.33, 1.24)
)


```

### Incidence by age calc
```{r}
age_bins = c(15, 25, 35, 50)
subset_years = c(2016, 2016.5, 2021, 2021.5)

# Subset data on years
data <- lowinc.results %>% filter(Year %in% subset_years)

# Calculate incidence
data$Year_Integer <- floor((data$Year-0.5))
# Aggregate number of new infections each year, broken down by Year_Integer and Gender
trajectories_IR.1a <- aggregate(Newly.Infected ~ Year_Integer+Gender+Age + sim.id+scenario_name, data=data,FUN=sum)
#Make the denominator as HIV-negative individuals
trajectories_IR.2 <- aggregate(Population - Infected ~ Year+Gender+Age + sim.id+scenario_name, data=data, FUN=sum)
trajectories_IR.2$Year_Integer <- floor(trajectories_IR.2$Year-0.5)
#remove second instance of duplicate rows
trajectories_IR.2 <- trajectories_IR.2[!duplicated(trajectories_IR.2[c("Year_Integer","Gender","Age", "sim.id","scenario_name")]),]
trajectories_IR.2 <- trajectories_IR.2[-match("Year",names(trajectories_IR.2))]
trajectories_IRoverall <- merge(trajectories_IR.1a, trajectories_IR.2, by=c("Year_Integer","Gender","Age", "sim.id","scenario_name"))
trajectories_IRoverall$incidence <- trajectories_IRoverall$Newly.Infected / (trajectories_IRoverall$Population)
data <- trajectories_IRoverall %>% dplyr::rename(Year = Year_Integer)

# Age bins
age_labels = c()
for (i in 1:(length(age_bins) - 1)){
  age_labels <- append(age_labels, paste0("[",age_bins[i],":",age_bins[i + 1],")"))
}

# Label each age by its bin
data <- data %>% mutate(
  AgeBin = cut(Age, breaks = age_bins, right = FALSE)
  ) %>%
  filter(!is.na(AgeBin))
data$AgeBin_index = factor(data$AgeBin,labels = 1:length(age_labels))

# Calculate mean incidence across all sim runs
inc.age.data.mean <- data %>%
  dplyr::group_by(Year, AgeBin_index, AgeBin, Gender, scenario_name) %>%
  dplyr::summarize(mean.Incidence = mean(incidence),
                  sd.Incidence = sd(incidence),
            .groups = 'keep') %>%
  ungroup() %>%
  dplyr::mutate(
    upper = mean.Incidence + 2*sd.Incidence,
    lower = case_when(
      mean.Incidence - 2 * sd.Incidence > 0 ~ mean.Incidence - 2 * sd.Incidence,
      mean.Incidence - 2 * sd.Incidence <= 0 ~ 0)
    )  %>% mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))
```

### Plot
```{r, fig.width=10}
p.inc.age <- inc.age.data.mean %>% filter(Year == 2016) %>% 
  filter(scenario_name == 'lowinc.baseline') %>% 
  ggplot() +
  # plot means
  geom_point(
    mapping = aes(x = AgeBin_index, y = mean.Incidence*100, color = Gender),
    size=2,
     show.legend = TRUE
  ) +
  geom_errorbar(
    mapping = aes(x=AgeBin_index, ymin=lower*100, ymax=upper*100, color=Gender),
    width=.15, size=1,
   show.legend = FALSE) +
  # shims data 
  geom_point(
    data = inc.data %>% filter(Year == 2016), 
    mapping = aes(x = AgeBin_index, y = Incidence), 
    size = 3, shape = 0, color = 'black'
  ) + 
  geom_errorbar(
    data = inc.data %>% filter(Year == 2016),
    mapping = aes(x = AgeBin_index, ymin = lb, ymax = ub),
    color = 'black'
  ) + 
  facet_grid(cols = vars(Gender), rows = vars(scenario_name)) +
  xlab("Age") +
  ylab("Incidence (%)") +
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_discrete(
    breaks = 1:length(age_labels),
    labels = age_labels
    #@labels = rep("", length(age_labels))
    ) +
  ylim(0,4.5) + 
  scale_color_manual(values=c("blue", "red"))
  
p.inc.age
```



Incience in 2021
```{r}
lowerinc.results %>% 
  mutate(Year = floor(Year - .5)) %>% 
  filter(Age > 15) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(Newly.Infected = sum(Newly.Infected * pop_scaling_factor),
            Population = sum(Population * pop_scaling_factor/2),
            Infected = sum(Infected * pop_scaling_factor/2)) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(Newly.Infected = mean(Newly.Infected), 
            Population = mean(Population), 
            Infected = mean(Infected))  %>% 
  ungroup() %>% 
  mutate(Susc = Population - Infected) %>% 
  mutate(rate = Newly.Infected/Susc)
```


```{r}
data <- lowinc.results %>% filter(Age >= 15a, Age < 50)

# Calculate incidence
data$Year_Integer <- floor((data$Year-0.5))
# Aggregate number of new infections each year, broken down by Year_Integer and Gender
trajectories_IR.1a <- aggregate(Newly.Infected ~ Year_Integer+Gender + sim.id+scenario_name, data=data,FUN=sum)
#Make the denominator as HIV-negative individuals
trajectories_IR.2 <- aggregate(Population - Infected ~ Year+Gender + sim.id+scenario_name, data=data, FUN=sum)
trajectories_IR.2$Year_Integer <- floor(trajectories_IR.2$Year-0.5)
#remove second instance of duplicate rows
trajectories_IR.2 <- trajectories_IR.2[!duplicated(trajectories_IR.2[c("Year_Integer","Gender", "sim.id","scenario_name")]),]
trajectories_IR.2 <- trajectories_IR.2[-match("Year",names(trajectories_IR.2))]
trajectories_IRoverall <- merge(trajectories_IR.1a, trajectories_IR.2, by=c("Year_Integer","Gender","sim.id","scenario_name"))
trajectories_IRoverall$incidence <- trajectories_IRoverall$Newly.Infected / (trajectories_IRoverall$Population)
data <- trajectories_IRoverall %>% dplyr::rename(Year = Year_Integer)

# Calculate mean incidence across all sim runs
inc.data.mean <- data %>%
  dplyr::group_by(Year, Gender, scenario_name) %>%
  dplyr::summarize(mean.Incidence = mean(incidence),
                  sd.Incidence = sd(incidence),
            .groups = 'keep') %>%
  ungroup() %>%
  dplyr::mutate(upper = mean.Incidence + 2*sd.Incidence,
                lower = case_when(mean.Incidence - 2 * sd.Incidence > 0 ~ mean.Incidence - 2 * sd.Incidence,
                         mean.Incidence - 2 * sd.Incidence <= 0 ~ 0)
                )

# Transform data
inc.data.mean <- inc.data.mean %>% mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))
```



```{r, fig.height=6}
p.inc <- inc.data.mean %>%
  ggplot() +
  # plot means
  geom_point(
    mapping = aes(x = Year, y = mean.Incidence*100, color = Gender),
    size=2,
     show.legend = FALSE
  ) +
  geom_errorbar(
    mapping = aes(x=Year, ymin=lower*100, ymax=upper*100, color=Gender),
    width=.15, size=1,
   show.legend = FALSE) +
  geom_point(data = incidence.data, 
             mapping = aes(x = Year, y = inc), color = 'black') + 
  geom_errorbar(data = incidence.data, 
    mapping = aes(x = Year, ymin = lb, ymax = ub), color = 'black') + 
  facet_grid(cols = vars(Gender), rows = vars(scenario_name)) +
  #scale_color_manual(values=c("blue", "red")) +
  xlab("Age") +
  ylab("Incidence (%)") +
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_continuous(breaks = c(2005, 2010, 2015, 2020, 2025),
                     limits = c(2005, 2025)) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) 
  
p.inc
```

