---
title: "Duet_analysis"
output: html_document
date: "2025-10-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries 
```{r}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(data.table))
library(magrittr)
library(rsample)
library(patchwork)
```


## Constants
```{r}
SWZ_CENSUS_YEAR = 2017
SWZ_CENSUS_POP = 1148000 # UN WPP 2019, according to SWZ national census 2017 1093238

current_date <- Sys.Date()
date_string_ymd <- format(current_date, format = "%Y%m%d")
```


# Read in data

```{r}
experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet-baseline___2025_10_29_17_20_05_919018/"

results.baseline.2 <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "baseline.2",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet-baseline___2025_10_31_16_27_37_257804/"

results.baseline <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "baseline",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)


experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet-cut_perm___2025_10_31_16_29_27_340721/"

results.cut.perm <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "cut.perm",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)


experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet-cut_2025___2025_10_31_16_30_47_764181/"

results.cut.2025 <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "cut.2025",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)


experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet-cut_2025_la___2025_10_31_16_32_08_943774/"

results.cut.la <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "cut.la",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet-cut_perm_max___2025_10_31_16_33_30_132823/"

results.cut.perm.max <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "cut.perm.max",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

duet.results <- rbind(
  results.baseline,
  results.cut.perm,
  results.cut.2025,
  results.cut.la,
  results.cut.perm.max
)

sim.results.pop.scaling <- duet.results %>%
  filter(Year == SWZ_CENSUS_YEAR) %>%
  group_by(sim.ix, scenario_name) %>%
  summarize(total.pop = sum(Population), .groups = 'drop_last') %>%
  mutate(pop_scaling_factor = SWZ_CENSUS_POP/total.pop)

duet.results <- duet.results %>%
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.ix", "scenario_name")
  )

```



# Tables

## PLHIV

```{r}
dat <- duet.results %>% 
  filter(Age >= 15) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Infected = sum(Infected * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Infected = mean(Infected)
  )



dat %>% filter(Year == 2031) %>% 
  mutate(
    Infected.baseline = dat %>% filter(Year == 2031, scenario_name == 'baseline') %>% .$Infected
    ) %>% 
  mutate(diff = Infected - Infected.baseline) %>% 
  mutate(pct = diff/Infected.baseline)
```


## New Acquisitions
```{r}
dat <- duet.results %>% 
  mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Newly.Infected = sum(Newly.Infected * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Newly.Infected = mean(Newly.Infected)
  )

dat %>% 
  filter(Year >=2025) %>% 
  group_by(scenario_name) %>% 
  summarize(Newly.Infected = sum(Newly.Infected)) %>% 
  mutate(
    Newly.Infected.baseline = rep(
  dat %>% 
    filter(Year >=2025) %>% 
    group_by(scenario_name) %>% 
    summarize(Newly.Infected.baseline = sum(Newly.Infected)) %>% 
    filter(scenario_name == 'baseline') %>% .$Newly.Infected.baseline,
  5)
  ) %>% 
  mutate(
    diff = Newly.Infected - Newly.Infected.baseline
  ) %>% 
  mutate(
    pct = diff/Newly.Infected.baseline
  )
```

## HIV deaths

```{r}
dat <- duet.results %>% 
  mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Died_from_HIV = sum(Died_from_HIV * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Died_from_HIV = mean(Died_from_HIV)
  )

dat %>% 
  filter(Year >=2025) %>% 
  group_by(scenario_name) %>% 
  summarize(Died_from_HIV = sum(Died_from_HIV)) %>% 
  mutate(
    Died_from_HIV.baseline = rep(
  dat %>% 
    filter(Year >=2025) %>% 
    group_by(scenario_name) %>% 
    summarize(Died_from_HIV.baseline = sum(Died_from_HIV)) %>% 
    filter(scenario_name == 'baseline') %>% .$Died_from_HIV.baseline,
  5)
  ) %>% 
  mutate(
    diff = Died_from_HIV - Died_from_HIV.baseline
  ) %>% 
  mutate(
    pct = diff/Died_from_HIV.baseline
  )
```

## ART Coverage

```{r}
dat <- duet.results %>% 
  filter(Age > 15) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    On_ART = sum(On_ART * pop_scaling_factor),
    Infected = sum(Infected * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    On_ART = mean(On_ART),
    Infected = mean(Infected)
  ) %>% 
  ungroup() %>% 
  mutate(ARTCov = On_ART/Infected)

dat %>% filter(Year == 2026)

dat %>% filter(Year == 2031)
```


# Plots

## PLHIV Populations

```{r}
dat <- duet.results %>% 
  #mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Infected = sum(Infected * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Infected = mean(Infected)
  )

dat %>% 
  filter(Year > 2024) %>% 
  filter(scenario_name != "cut.perm.max") %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Infected, color = scenario_name),
            linewidth = 1,
            show.legend = FALSE) +
  scale_color_manual(values = c( "black", "#C41000", "#E69F00", "#0072B2")) +
  scale_x_continuous("Year", breaks = c(2025, 2027, 2029, 2031)) +
  scale_y_continuous("PLHIV (thousands)", limits = c(220000,260000), labels = c("220,000","230,000","240,000","250,000","260,000"), breaks = c(220000, 230000, 240000, 250000, 260000)) +
  #scale_y_continuous("") +
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(),
        #axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        axis.title.y = element_blank(),
        #plot.title = element_text(hjust = 0.5),
        text = element_text(family = "sans"),
        axis.text = element_text(size = 14),
        axis.title= element_text(size = 16)
        #axis.text.y = element_text(angle = 45, hjust = .5, vjust = 1)
        )

ggsave("Duet_figures/PLHIV_time_series.pdf", height = 4, width = 5, units = "in")
```

## HIV Acquisitions

```{r}
dat <- duet.results %>% 
  mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Newly.Infected = sum(Newly.Infected * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Newly.Infected = mean(Newly.Infected)
  )


dat %>% 
  filter(Year >= 2020) %>% 
  filter(scenario_name != "cut.perm.max") %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Newly.Infected, color = scenario_name),
            linewidth = 1, show.legend = FALSE) +
  scale_color_manual(values = c( "black", "#C41000", "#E69F00", "#0072B2")) +
  scale_x_continuous("Year", breaks = c(2020, 2025, 2030)) +
  #scale_y_continuous("HIV Acquisitions") +
  scale_y_continuous("") +
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(),
        #axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        axis.title.y = element_blank(),
        #plot.title = element_text(hjust = 0.5),
        text = element_text(family = "sans"),
        axis.text = element_text(size = 14),
        axis.title= element_text(size = 16))

ggsave("Duet_figures/HIVAcquisitions_time_series.pdf", height = 4, width = 5, units = "in")
```


## HIV-related Deaths

```{r}
dat <- duet.results %>% 
  mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Died_from_HIV = sum(Died_from_HIV * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Died_from_HIV = mean(Died_from_HIV)
  )


dat %>% 
  filter(Year >= 2020) %>% 
  filter(scenario_name != "cut.perm.max") %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Died_from_HIV, color = scenario_name),
            linewidth = 1, show.legend = FALSE) +
  scale_color_manual(values = c( "black", "#C41000", "#E69F00", "#0072B2")) +
  scale_x_continuous("Year", breaks = c(2020, 2025, 2030)) +
  #scale_y_continuous("HIV Deaths") +
  scale_y_continuous("") +
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(),
        #axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        axis.title.y = element_blank(),
        #plot.title = element_text(hjust = 0.5),
        text = element_text(family = "sans"),
        axis.text = element_text(size = 14),
        axis.title= element_text(size = 16))

ggsave("Duet_figures/HIVDeaths_time_series.pdf", height = 4, width = 5, units = "in")

```


## ART Coverage

```{r}
# What percentage of people are on ART in the baseline, at the start of 2026?
dat <- duet.results %>% 
  filter(Age > 15) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    On_ART = sum(On_ART * pop_scaling_factor),
    Infected = sum(Infected * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    On_ART = mean(On_ART),
    Infected = mean(Infected)
  ) %>% 
  ungroup() %>% 
  mutate(ARTCov = On_ART/Infected)

dat %>% 
  filter(Year >= 2020) %>% 
  filter(scenario_name != "cut.perm.max") %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = ARTCov, color = scenario_name),
            linewidth = 1, show.legend = FALSE) +
  scale_color_manual(values = c( "black", "#C41000", "#E69F00", "#0072B2")) +
  scale_x_continuous("Year", breaks = c(2020, 2025, 2030)) +
  #scale_y_continuous("ART Coverage") +
  scale_y_continuous("", breaks = seq(.8,.9,.02)) +
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(),
        #axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        axis.title.y = element_blank(),
        #plot.title = element_text(hjust = 0.5),
        text = element_text(family = "sans"),
        axis.text = element_text(size = 14),
        axis.title= element_text(size = 16))

ggsave("Duet_figures/ARTCoverage_time_series.pdf", height = 4, width = 5, units = "in")

```
## PrEP Coverage

```{r}
dat <- duet.results %>% 
  mutate(Year = floor(Year - .5)) %>% 
  filter(Age > 15) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Initiate_PrEP = sum(Initiate_PrEP * pop_scaling_factor),
    Initiate_LAPrEP = sum(Initiate_LAPrEP * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Initiate_PrEP = mean(Initiate_PrEP),
    Initiate_LAPrEP = mean(Initiate_LAPrEP)
  )

dat %>% 
  filter(Year >= 2020) %>% 
  filter(scenario_name != "cut.perm.max") %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Initiate_PrEP, color = scenario_name),
            linewidth = 1) +
  scale_color_manual(values = c( "black", "#C41000", "#E69F00", "#0072B2")) +
  scale_x_continuous("Year", breaks = c(2020, 2025, 2030)) +
  scale_y_continuous("PrEP Initiations") +
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(),
        #axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        #plot.title = element_text(hjust = 0.5),
        text = element_text(family = "sans"),
        axis.text = element_text(size = 14),
        axis.title= element_text(size = 16))

```

```{r}
dat %>% 
  filter(Year >= 2020) %>% 
  filter(scenario_name != "cut.perm.max") %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Initiate_LAPrEP, color = scenario_name),
            linewidth = 1) +
  scale_color_manual(values = c( "black", "#C41000", "#E69F00", "#0072B2")) +
  scale_x_continuous("Year", breaks = c(2020, 2025, 2030)) +
  scale_y_continuous("PrEP Initiations") +
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(),
        #axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        #plot.title = element_text(hjust = 0.5),
        text = element_text(family = "sans"),
        axis.text = element_text(size = 14),
        axis.title= element_text(size = 16))
```

# Tuned up ARTCoverage

## Read in Data

```{r}
experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet-baseline_lowinc___2025_11_04_11_44_57_828297/"

lowinc.baseline <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "lowinc.baseline",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet-cut_perm_lowinc___2025_11_04_11_46_45_602773/"

lowinc.cut.perm <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "lowinc.cut.perm",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)


experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet-cut_2025_lowinc___2025_11_04_11_48_08_739054/"

lowinc.cut.2025 <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "lowinc.cut.2025",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)


experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet-cut_2025_la_lowinc___2025_11_04_11_49_29_894966/"

lowinc.cut.la <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "lowinc.cut.la",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet-cut_perm_max_lowinc___2025_11_04_11_50_50_594236/"

lowinc.cut.perm.max <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "lowinc.cut.perm.max",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

lowinc.results <- rbind(
  lowinc.baseline,
  lowinc.cut.perm,
  lowinc.cut.2025,
  lowinc.cut.la,
  lowinc.cut.perm.max
)

sim.results.pop.scaling <- lowinc.results %>%
  filter(Year == SWZ_CENSUS_YEAR) %>%
  group_by(sim.ix, scenario_name) %>%
  summarize(total.pop = sum(Population), .groups = 'drop_last') %>%
  mutate(pop_scaling_factor = SWZ_CENSUS_POP/total.pop)

lowinc.results <- lowinc.results %>%
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.ix", "scenario_name")
  )

```


## Tables

### PLHIV

```{r}
dat <- lowinc.results %>% 
  filter(Age >= 15) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Infected = sum(Infected * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Infected = mean(Infected)
  )



dat %>% filter(Year == 2031) %>% 
  mutate(
    Infected.baseline = dat %>% filter(Year == 2031, scenario_name == 'lowinc.baseline') %>% .$Infected
    ) %>% 
  mutate(diff = Infected - Infected.baseline) %>% 
  mutate(pct = diff/Infected.baseline)
```


### New Acquisitions
```{r}
dat <- lowinc.results %>% 
  mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Newly.Infected = sum(Newly.Infected * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Newly.Infected = mean(Newly.Infected)
  )

dat %>% 
  filter(Year >=2025) %>% 
  group_by(scenario_name) %>% 
  summarize(Newly.Infected = sum(Newly.Infected)) %>% 
  mutate(
    Newly.Infected.baseline = rep(
  dat %>% 
    filter(Year >=2025) %>% 
    group_by(scenario_name) %>% 
    summarize(Newly.Infected.baseline = sum(Newly.Infected)) %>% 
    filter(scenario_name == 'lowinc.baseline') %>% .$Newly.Infected.baseline,
  5)
  ) %>% 
  mutate(
    diff = Newly.Infected - Newly.Infected.baseline
  ) %>% 
  mutate(
    pct = diff/Newly.Infected.baseline
  )
```

#### Incidence in 2021
```{r}
lowinc.results %>% 
  mutate(Year = floor(Year - .5)) %>% 
  filter(Age > 15) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(Newly.Infected = sum(Newly.Infected * pop_scaling_factor),
            Population = sum(Population * pop_scaling_factor/2),
            Infected = sum(Infected * pop_scaling_factor/2)) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(Newly.Infected = mean(Newly.Infected), 
            Population = mean(Population), 
            Infected = mean(Infected))  %>% 
  ungroup() %>% 
  mutate(Susc = Population - Infected) %>% 
  mutate(rate = Newly.Infected/Susc)
```

### HIV deaths

```{r}
dat <- lowinc.results %>% 
  mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Died_from_HIV = sum(Died_from_HIV * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Died_from_HIV = mean(Died_from_HIV)
  )

dat %>% 
  filter(Year >=2025) %>% 
  group_by(scenario_name) %>% 
  summarize(Died_from_HIV = sum(Died_from_HIV)) %>% 
  mutate(
    Died_from_HIV.baseline = rep(
  dat %>% 
    filter(Year >=2025) %>% 
    group_by(scenario_name) %>% 
    summarize(Died_from_HIV.baseline = sum(Died_from_HIV)) %>% 
    filter(scenario_name == 'lowinc.baseline') %>% .$Died_from_HIV.baseline,
  5)
  ) %>% 
  mutate(
    diff = Died_from_HIV - Died_from_HIV.baseline
  ) %>% 
  mutate(
    pct = diff/Died_from_HIV.baseline
  )
```

### ART Coverage

```{r}
dat <- lowinc.results %>% 
  filter(Age > 15) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    On_ART = sum(On_ART * pop_scaling_factor),
    Infected = sum(Infected * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    On_ART = mean(On_ART),
    Infected = mean(Infected)
  ) %>% 
  ungroup() %>% 
  mutate(ARTCov = On_ART/Infected)

dat %>% filter(Year == 2026)

dat %>% filter(Year == 2031)
```

## Plots


### PLHIV Populations

```{r}
dat <- lowinc.results %>% 
  #mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Infected = sum(Infected * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Infected = mean(Infected)
  )

dat %>% 
  filter(Year > 2024) %>% 
  filter(scenario_name != "lowinc.cut.perm.max") %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Infected, color = scenario_name),
            linewidth = 1,
            show.legend = FALSE) +
  scale_color_manual(values = c( "black", "#C41000", "#E69F00", "#0072B2")) +
  scale_x_continuous("Year", breaks = c(2025, 2027, 2029, 2031)) +
  #scale_y_continuous("PLHIV (thousands)", limits = c(220000,260000), labels = c("220,000","230,000","240,000","250,000","260,000"), breaks = c(220000, 230000, 240000, 250000, 260000)) +
  #scale_y_continuous("") +
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(),
        #axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        axis.title.y = element_blank(),
        #plot.title = element_text(hjust = 0.5),
        text = element_text(family = "sans"),
        axis.text = element_text(size = 14),
        axis.title= element_text(size = 16)
        #axis.text.y = element_text(angle = 45, hjust = .5, vjust = 1)
        )

ggsave("Duet_figures/PLHIV_time_series_lowinc.pdf", height = 4, width = 5, units = "in")
```

### HIV Acquisitions

```{r}
dat <- lowinc.results %>% 
  mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Newly.Infected = sum(Newly.Infected * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Newly.Infected = mean(Newly.Infected)
  )


dat %>% 
  filter(Year >= 2020) %>% 
  filter(scenario_name != "lowinc.cut.perm.max") %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Newly.Infected, color = scenario_name),
            linewidth = 1, show.legend = FALSE) +
  scale_color_manual(values = c( "black", "#C41000", "#E69F00", "#0072B2")) +
  scale_x_continuous("Year", breaks = c(2020, 2025, 2030)) +
  #scale_y_continuous("HIV Acquisitions") +
  scale_y_continuous("") +
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(),
        #axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        axis.title.y = element_blank(),
        #plot.title = element_text(hjust = 0.5),
        text = element_text(family = "sans"),
        axis.text = element_text(size = 14),
        axis.title= element_text(size = 16))

ggsave("Duet_figures/HIVAcquisitions_time_seriess_lowinc.pdf", height = 4, width = 5, units = "in")
```


### HIV-related Deaths

```{r}
dat <- lowinc.results %>% 
  mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Died_from_HIV = sum(Died_from_HIV * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Died_from_HIV = mean(Died_from_HIV)
  )


dat %>% 
  filter(Year >= 2020) %>% 
  filter(scenario_name != "lowinc.cut.perm.max") %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Died_from_HIV, color = scenario_name),
            linewidth = 1, show.legend = FALSE) +
  scale_color_manual(values = c( "black", "#C41000", "#E69F00", "#0072B2")) +
  scale_x_continuous("Year", breaks = c(2020, 2025, 2030)) +
  #scale_y_continuous("HIV Deaths") +
  scale_y_continuous("") +
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(),
        #axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        axis.title.y = element_blank(),
        #plot.title = element_text(hjust = 0.5),
        text = element_text(family = "sans"),
        axis.text = element_text(size = 14),
        axis.title= element_text(size = 16))

ggsave("Duet_figures/HIVDeaths_time_seriess_lowinc.pdf", height = 4, width = 5, units = "in")

```


### ART Coverage

```{r}
# What percentage of people are on ART in the baseline, at the start of 2026?
dat <- lowinc.results %>% 
  filter(Age > 15) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    On_ART = sum(On_ART * pop_scaling_factor),
    Infected = sum(Infected * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    On_ART = mean(On_ART),
    Infected = mean(Infected)
  ) %>% 
  ungroup() %>% 
  mutate(ARTCov = On_ART/Infected)

dat %>% 
  filter(Year >= 2020) %>% 
  filter(scenario_name != "lowinc.cut.perm.max") %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = ARTCov, color = scenario_name),
            linewidth = 1, show.legend = FALSE) +
  scale_color_manual(values = c( "black", "#C41000", "#E69F00", "#0072B2")) +
  scale_x_continuous("Year", breaks = c(2020, 2025, 2030)) +
  #scale_y_continuous("ART Coverage") +
  #scale_y_continuous("", breaks = seq(.8,.9,.02)) +
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(),
        #axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        axis.title.y = element_blank(),
        #plot.title = element_text(hjust = 0.5),
        text = element_text(family = "sans"),
        axis.text = element_text(size = 14),
        axis.title= element_text(size = 16))

ggsave("Duet_figures/ARTCoverage_time_seriess_lowinc.pdf", height = 4, width = 5, units = "in")

```

### PrEP Coverage

```{r}
dat <- duet.results %>% 
  mutate(Year = floor(Year - .5)) %>% 
  filter(Age > 15) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Initiate_PrEP = sum(Initiate_PrEP * pop_scaling_factor),
    Initiate_LAPrEP = sum(Initiate_LAPrEP * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Initiate_PrEP = mean(Initiate_PrEP),
    Initiate_LAPrEP = mean(Initiate_LAPrEP)
  )

dat %>% 
  filter(Year >= 2020) %>% 
  filter(scenario_name != "cut.perm.max") %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Initiate_PrEP, color = scenario_name),
            linewidth = 1) +
  scale_color_manual(values = c( "black", "#C41000", "#E69F00", "#0072B2")) +
  scale_x_continuous("Year", breaks = c(2020, 2025, 2030)) +
  scale_y_continuous("PrEP Initiations") +
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(),
        #axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        #plot.title = element_text(hjust = 0.5),
        text = element_text(family = "sans"),
        axis.text = element_text(size = 14),
        axis.title= element_text(size = 16))

```

```{r}
dat %>% 
  filter(Year >= 2020) %>% 
  filter(scenario_name != "cut.perm.max") %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Initiate_LAPrEP, color = scenario_name),
            linewidth = 1) +
  scale_color_manual(values = c( "black", "#C41000", "#E69F00", "#0072B2")) +
  scale_x_continuous("Year", breaks = c(2020, 2025, 2030)) +
  scale_y_continuous("PrEP Initiations") +
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(),
        #axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        #plot.title = element_text(hjust = 0.5),
        text = element_text(family = "sans"),
        axis.text = element_text(size = 14),
        axis.title= element_text(size = 16))
```



# Lower Incidence in Men

## Read in Data

```{r}
experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet-baseline_lowerinc_2___2025_11_07_17_27_19_883503/"

lowerinc.baseline <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "lowerinc.baseline",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet-cut_perm_lowerinc_2___2025_11_07_17_29_10_265629/"

lowerinc.cut.perm <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "lowerinc.cut.perm",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)


experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet-cut_2025_lowerinc_2___2025_11_07_17_30_36_860158/"

lowerinc.cut.2025 <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "lowerinc.cut.2025",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)


experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet-cut_2025_la_lowerinc_2___2025_11_07_17_32_01_056011/"

lowerinc.cut.la <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "lowerinc.cut.la",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

lowerinc.results <- rbind(
  lowerinc.baseline,
  lowerinc.cut.perm,
  lowerinc.cut.2025,
  lowerinc.cut.la
)

sim.results.pop.scaling <- lowerinc.results %>%
  filter(Year == SWZ_CENSUS_YEAR) %>%
  group_by(sim.ix, scenario_name) %>%
  summarize(total.pop = sum(Population), .groups = 'drop_last') %>%
  mutate(pop_scaling_factor = SWZ_CENSUS_POP/total.pop)

lowerinc.results <- lowerinc.results %>%
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.ix", "scenario_name")
  )

```


## Tables

### PLHIV

```{r}
dat <- lowerinc.results %>% 
  filter(Age >= 15) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Infected = sum(Infected * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Infected = mean(Infected)
  )


dat %>% filter(Year == 2031) %>% 
  mutate(
    Infected.baseline = dat %>% filter(Year == 2031, scenario_name == 'lowerinc.baseline') %>% .$Infected
    ) %>% 
  mutate(diff = Infected - Infected.baseline) %>% 
  mutate(pct = diff/Infected.baseline)
```


### New Acquisitions
```{r}
dat <- lowerinc.results %>% 
  filter(Age >= 15) %>% 
  mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Newly.Infected = sum(Newly.Infected * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Newly.Infected = mean(Newly.Infected)
  )

dat %>% 
  filter(Year >=2025) %>% 
  group_by(scenario_name) %>% 
  summarize(Newly.Infected = sum(Newly.Infected)) %>% 
  mutate(
    Newly.Infected.baseline = rep(
  dat %>% 
    filter(Year >=2025) %>% 
    group_by(scenario_name) %>% 
    summarize(Newly.Infected.baseline = sum(Newly.Infected)) %>% 
    filter(scenario_name == 'lowerinc.baseline') %>% .$Newly.Infected.baseline,
  4)
  ) %>% 
  mutate(
    diff = Newly.Infected - Newly.Infected.baseline
  ) %>% 
  mutate(
    pct = diff/Newly.Infected.baseline
  )
```

#### Incidence in 2021
```{r}
lowerinc.results %>% 
  mutate(Year = floor(Year - .5)) %>% 
  filter(Age > 15) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(Newly.Infected = sum(Newly.Infected * pop_scaling_factor),
            Population = sum(Population * pop_scaling_factor/2),
            Infected = sum(Infected * pop_scaling_factor/2)) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(Newly.Infected = mean(Newly.Infected), 
            Population = mean(Population), 
            Infected = mean(Infected))  %>% 
  ungroup() %>% 
  mutate(Susc = Population - Infected) %>% 
  mutate(rate = Newly.Infected/Susc)
```


### HIV deaths

```{r}
dat <- lowerinc.results %>% 
  filter(Age >= 15) %>% 
  mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Died_from_HIV = sum(Died_from_HIV * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Died_from_HIV = mean(Died_from_HIV)
  )

dat %>% 
  filter(Year >=2025) %>% 
  group_by(scenario_name) %>% 
  summarize(Died_from_HIV = sum(Died_from_HIV)) %>% 
  mutate(
    Died_from_HIV.baseline = rep(
  dat %>% 
    filter(Year >=2025) %>% 
    group_by(scenario_name) %>% 
    summarize(Died_from_HIV.baseline = sum(Died_from_HIV)) %>% 
    filter(scenario_name == 'lowerinc.baseline') %>% .$Died_from_HIV.baseline,
  4)
  ) %>% 
  mutate(
    diff = Died_from_HIV - Died_from_HIV.baseline
  ) %>% 
  mutate(
    pct = diff/Died_from_HIV.baseline
  )
```

### ART Coverage

```{r}
dat <- lowerinc.results %>% 
  filter(Age > 15) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    On_ART = sum(On_ART * pop_scaling_factor),
    Infected = sum(Infected * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    On_ART = mean(On_ART),
    Infected = mean(Infected)
  ) %>% 
  ungroup() %>% 
  mutate(ARTCov = On_ART/Infected)

dat %>% filter(Year == 2026)

dat %>% filter(Year == 2031)
```

## Plots


### PLHIV Populations

```{r}
dat <- lowerinc.results %>% 
  #mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Infected = sum(Infected * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Infected = mean(Infected)
  )

dat %>% 
  filter(Year > 2024) %>% 
  filter(scenario_name != "lowinc.cut.perm.max") %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Infected, color = scenario_name),
            linewidth = 1,
            show.legend = FALSE) +
  scale_color_manual(values = c( "black", "#C41000", "#E69F00", "#0072B2")) +
  scale_x_continuous("Year", breaks = c(2025, 2027, 2029, 2031)) +
  #scale_y_continuous("PLHIV (thousands)", limits = c(220000,260000), labels = c("220,000","230,000","240,000","250,000","260,000"), breaks = c(220000, 230000, 240000, 250000, 260000)) +
  #scale_y_continuous("") +
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(),
        #axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        axis.title.y = element_blank(),
        #plot.title = element_text(hjust = 0.5),
        text = element_text(family = "sans"),
        axis.text = element_text(size = 14),
        axis.title= element_text(size = 16)
        #axis.text.y = element_text(angle = 45, hjust = .5, vjust = 1)
        )

ggsave("Duet_figures/PLHIV_time_series_lowinc.pdf", height = 4, width = 5, units = "in")
```

### HIV Acquisitions

```{r}
dat <- lowerinc.results %>% 
  mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Newly.Infected = sum(Newly.Infected * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Newly.Infected = mean(Newly.Infected)
  )


dat %>% 
  filter(Year >= 2020) %>% 
  filter(scenario_name != "lowinc.cut.perm.max") %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Newly.Infected, color = scenario_name),
            linewidth = 1, show.legend = FALSE) +
  scale_color_manual(values = c( "black", "#C41000", "#E69F00", "#0072B2")) +
  scale_x_continuous("Year", breaks = c(2020, 2025, 2030)) +
  #scale_y_continuous("HIV Acquisitions") +
  scale_y_continuous("") +
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(),
        #axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        axis.title.y = element_blank(),
        #plot.title = element_text(hjust = 0.5),
        text = element_text(family = "sans"),
        axis.text = element_text(size = 14),
        axis.title= element_text(size = 16))

#ggsave("Duet_figures/HIVAcquisitions_time_seriess_lowinc.pdf", height = 4, width = 5, units = "in")
```


### HIV-related Deaths

```{r}
dat <- lowerinc.results %>% 
  mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Died_from_HIV = sum(Died_from_HIV * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Died_from_HIV = mean(Died_from_HIV)
  )


dat %>% 
  filter(Year >= 2020) %>% 
  filter(scenario_name != "lowinc.cut.perm.max") %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Died_from_HIV, color = scenario_name),
            linewidth = 1, show.legend = FALSE) +
  scale_color_manual(values = c( "black", "#C41000", "#E69F00", "#0072B2")) +
  scale_x_continuous("Year", breaks = c(2020, 2025, 2030)) +
  #scale_y_continuous("HIV Deaths") +
  scale_y_continuous("") +
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(),
        #axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        axis.title.y = element_blank(),
        #plot.title = element_text(hjust = 0.5),
        text = element_text(family = "sans"),
        axis.text = element_text(size = 14),
        axis.title= element_text(size = 16))

#ggsave("Duet_figures/HIVDeaths_time_seriess_lowinc.pdf", height = 4, width = 5, units = "in")

```


### ART Coverage

```{r}
# What percentage of people are on ART in the baseline, at the start of 2026?
dat <- lowerinc.results %>% 
  filter(Age > 15) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    On_ART = sum(On_ART * pop_scaling_factor),
    Infected = sum(Infected * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    On_ART = mean(On_ART),
    Infected = mean(Infected)
  ) %>% 
  ungroup() %>% 
  mutate(ARTCov = On_ART/Infected)

dat %>% 
  filter(Year >= 2020) %>% 
  filter(scenario_name != "lowinc.cut.perm.max") %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = ARTCov, color = scenario_name),
            linewidth = 1, show.legend = FALSE) +
  scale_color_manual(values = c( "black", "#C41000", "#E69F00", "#0072B2")) +
  scale_x_continuous("Year", breaks = c(2020, 2025, 2030)) +
  #scale_y_continuous("ART Coverage") +
  #scale_y_continuous("", breaks = seq(.8,.9,.02)) +
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(),
        #axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        axis.title.y = element_blank(),
        #plot.title = element_text(hjust = 0.5),
        text = element_text(family = "sans"),
        axis.text = element_text(size = 14),
        axis.title= element_text(size = 16))

#ggsave("Duet_figures/ARTCoverage_time_seriess_lowinc.pdf", height = 4, width = 5, units = "in")

```

### PrEP Coverage

```{r}
dat <- lowerinc.results %>% 
  mutate(Year = floor(Year - .5)) %>% 
  filter(Age > 15) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Initiate_PrEP = sum(Initiate_PrEP * pop_scaling_factor),
    Initiate_LAPrEP = sum(Initiate_LAPrEP * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Initiate_PrEP = mean(Initiate_PrEP),
    Initiate_LAPrEP = mean(Initiate_LAPrEP)
  )

dat %>% 
  filter(Year >= 2020) %>% 
  filter(scenario_name != "lower.cut.perm.max") %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Initiate_PrEP, color = scenario_name),
            linewidth = 1) +
  scale_color_manual(values = c( "black", "#C41000", "#E69F00", "#0072B2")) +
  scale_x_continuous("Year", breaks = c(2020, 2025, 2030)) +
  scale_y_continuous("PrEP Initiations") +
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(),
        #axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        #plot.title = element_text(hjust = 0.5),
        text = element_text(family = "sans"),
        axis.text = element_text(size = 14),
        axis.title= element_text(size = 16))

```

```{r}
dat %>% 
  filter(Year >= 2020) %>% 
  filter(scenario_name != "lowinc.cut.perm.max") %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Initiate_LAPrEP, color = scenario_name),
            linewidth = 1) +
  scale_color_manual(values = c( "black", "#C41000", "#E69F00", "#0072B2")) +
  scale_x_continuous("Year", breaks = c(2020, 2025, 2030)) +
  scale_y_continuous("PrEP Initiations") +
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(),
        #axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        #plot.title = element_text(hjust = 0.5),
        text = element_text(family = "sans"),
        axis.text = element_text(size = 14),
        axis.title= element_text(size = 16))
```
