---
title: "Modeling Duet"
output: html_document
date: "2025-10-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Introduction

* Produce a slide deck and series of outputs illustrating the new and improved calibrated model.
* Produce aggregated tables

# Libraries 
```{r}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(data.table))
library(magrittr)
library(rsample)
library(patchwork)
```


## Constants
```{r}
SWZ_CENSUS_YEAR = 2017
SWZ_CENSUS_POP = 1148000 # UN WPP 2019, according to SWZ national census 2017 1093238

current_date <- Sys.Date()
date_string_ymd <- format(current_date, format = "%Y%m%d")
```


# Preliminary checks

The purpose here will be to make sure that certain events are firing as intended, that the interventions are going out as designed

## Read in data

```{r}
experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet-baseline___2025_10_24_16_47_43_353533/"

results.baseline <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "baseline",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)


experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet-cut_perm___2025_10_24_16_48_14_037578/"

results.cut.perm <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "cut.perm",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet-cut_2025___2025_10_24_16_48_16_372521/"

results.cut.2025 <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "cut.2025",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender",  "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet-cut_2025_la___2025_10_24_16_48_18_683696/"

results.cut.la <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "cut.la",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet-cut_perm_max___2025_10_24_16_48_20_987872/"

results.cut.perm.max <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "cut.perm.max",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

duet.results <- rbind(
  results.baseline,
  results.cut.perm,
  results.cut.2025,
  results.cut.la,
  results.cut.perm.max
)

sim.results.pop.scaling <- duet.results %>%
  filter(Year == SWZ_CENSUS_YEAR) %>%
  group_by(sim.ix, scenario_name) %>%
  summarize(total.pop = sum(Population), .groups = 'drop_last') %>%
  mutate(pop_scaling_factor = SWZ_CENSUS_POP/total.pop)

duet.results <- duet.results %>%
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.ix", "scenario_name")
  )

```

## Checks

### Check on ART dropout

```{r}
dat <- duet.results %>% 
  filter(Year > 2020) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    PEPFAR_ARTDropout_Yes = sum(PEPFAR_ARTDropout_Yes * pop_scaling_factor),
    PEPFAR_ARTDropout_No = sum(PEPFAR_ARTDropout_No * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    PEPFAR_ARTDropout_Yes = mean(PEPFAR_ARTDropout_Yes), 
    PEPFAR_ARTDropout_No = mean(PEPFAR_ARTDropout_No)
  ) 

dat %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = PEPFAR_ARTDropout_No , color = scenario_name))


dat %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = PEPFAR_ARTDropout_Yes , color = scenario_name))

dat %>% filter(Year == 2025.5)
```


### Check on ART initiation rates

```{r}
dat <- duet.results %>% 
  filter(Year > 2020) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    OnART1_initiate = sum(OnART1_initiate * pop_scaling_factor),
    OnART1_initiate_FAILURE = sum(OnART1_initiate_FAILURE * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    OnART1_initiate = mean(OnART1_initiate), 
    OnART1_initiate_FAILURE = mean(OnART1_initiate_FAILURE)
  ) %>% 
  mutate(rate = OnART1_initiate/(OnART1_initiate_FAILURE + OnART1_initiate))

dat %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = OnART1_initiate_FAILURE , color = scenario_name))


dat %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = rate , color = scenario_name))


```

### PrEP Distribution

Both oral and LA

```{r}
dat <- duet.results %>% 
  filter(Year > 2020) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Initiate_PrEP = sum(Initiate_PrEP * pop_scaling_factor),
    Initiate_LAPrEP = sum(Initiate_LAPrEP * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Initiate_PrEP = mean(Initiate_PrEP), 
    Initiate_LAPrEP = mean(Initiate_LAPrEP)
  ) 

dat %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Initiate_PrEP , color = scenario_name))
```

```{r}
dat %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Initiate_LAPrEP , color = scenario_name))
```

### PrEP coverage

```{r}
dat <- duet.results %>% 
  filter(Year > 2020) %>% 
  group_by(sim.ix, scenario_name, Year, IP_Key.OnPrEP) %>% 
  summarize(
    Population = sum(Population * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year,IP_Key.OnPrEP) %>% 
  summarize(
    Population = mean(Population)
  ) 

dat %>% 
  pivot_wider(id_cols = c(scenario_name, Year),
              values_from = Population,
              names_from = IP_Key.OnPrEP) %>% 
  mutate(PrEP_cov = `TRUE`/(`FALSE` + `TRUE`)) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = PrEP_cov, color = scenario_name)) 

```


### VMMC Distribution

```{r}
dat <- duet.results %>% 
  filter(Year > 2020) %>% 
  #mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Program_VMMC = sum(Program_VMMC * pop_scaling_factor),
    Program_VMMC_Uptake = sum(Program_VMMC_Uptake * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Program_VMMC = mean(Program_VMMC),
    Program_VMMC_Uptake = mean(Program_VMMC_Uptake)
  ) %>% 
  mutate(
    rate = case_when(Program_VMMC_Uptake == 0 ~ 0,
                     Program_VMMC_Uptake > 0 ~ Program_VMMC/Program_VMMC_Uptake)
  )

dat %>%
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Program_VMMC, color = scenario_name))


dat %>%
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = rate, color = scenario_name))

```

# Produce results

## PLHIV

```{r}
dat <- duet.results %>% 
  #mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Infected = sum(Infected * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Infected = mean(Infected)
  )

dat %>% 
  filter(Year > 2020) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Infected, color = scenario_name))
```


## New HIV Infections

```{r}
dat <- duet.results %>% 
  mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Newly.Infected = sum(Newly.Infected * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Newly.Infected = mean(Newly.Infected)
  )


dat %>% 
  filter(Year > 2020) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Newly.Infected, color = scenario_name))
```

```{r}
dat %>% 
  filter(Year >=2025) %>% 
  group_by(scenario_name) %>% 
  summarize(Newly.Infected = sum(Newly.Infected)) %>% 
  mutate(
    Newly.Infected.baseline = rep(
  dat %>% 
    filter(Year >=2025) %>% 
    group_by(scenario_name) %>% 
    summarize(Newly.Infected.baseline = sum(Newly.Infected)) %>% 
    filter(scenario_name == 'baseline') %>% .$Newly.Infected.baseline,
  5)
  ) %>% 
  mutate(
    diff = Newly.Infected - Newly.Infected.baseline
  ) %>% 
  mutate(
    pct = diff/Newly.Infected.baseline
  )

```


## HIV-related deaths

```{r}
dat <- duet.results %>% 
  mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Died_from_HIV = sum(Died_from_HIV * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Died_from_HIV = mean(Died_from_HIV)
  )


dat %>% 
  filter(Year > 2020) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Died_from_HIV, color = scenario_name))
```


```{r}
dat %>% 
  filter(Year >=2025) %>% 
  group_by(scenario_name) %>% 
  summarize(Died_from_HIV = sum(Died_from_HIV)) %>% 
  mutate(
    Died_from_HIV.baseline = rep(
  dat %>% 
    filter(Year >=2025) %>% 
    group_by(scenario_name) %>% 
    summarize(Died_from_HIV.baseline = sum(Died_from_HIV)) %>% 
    filter(scenario_name == 'baseline') %>% .$Died_from_HIV.baseline,
  5)
  ) %>% 
  mutate(
    diff = Died_from_HIV - Died_from_HIV.baseline
  ) %>% 
  mutate(
    pct = diff/Died_from_HIV.baseline
  )
```


## ART initiations

```{r}
dat <- duet.results %>% 
  mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    OnART1_initiate = sum(OnART1_initiate * pop_scaling_factor),
    OnART1_initiate_FAILURE = sum(OnART1_initiate_FAILURE * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    OnART1_initiate = mean(OnART1_initiate),
    OnART1_initiate_FAILURE = mean(OnART1_initiate_FAILURE)
  )


dat %>% 
  filter(Year > 2020) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = OnART1_initiate, color = scenario_name))


dat %>% 
  filter(Year > 2020) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = OnART1_initiate_FAILURE, color = scenario_name))
```


```{r}
dat %>% 
  filter(Year >=2025) %>% 
  group_by(scenario_name) %>% 
  summarize(OnART1_initiate = sum(OnART1_initiate)) %>% 
  mutate(
    OnART1_initiate.baseline = rep(
  dat %>% 
    filter(Year >=2025) %>% 
    group_by(scenario_name) %>% 
    summarize(OnART1_initiate.baseline = sum(OnART1_initiate)) %>% 
    filter(scenario_name == 'baseline') %>% .$OnART1_initiate.baseline,
  5)
  ) %>% 
  mutate(
    diff = OnART1_initiate - OnART1_initiate.baseline
  ) %>% 
  mutate(
    pct = diff/OnART1_initiate.baseline
  )
```

What is the excess in ART initiations beyond baseline?
```{r}
dat %>% 
  filter(Year >= 2025) %>% 
  arrange(Year)
```





## PrEP initiations

```{r}
dat <- duet.results %>% 
  mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Initiate_PrEP = sum(Initiate_PrEP * pop_scaling_factor),
    Initiate_LAPrEP = sum(Initiate_LAPrEP * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Initiate_PrEP = mean(Initiate_PrEP),
    Initiate_LAPrEP = mean(Initiate_LAPrEP)
  )

dat %>% 
  filter(Year > 2020) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Initiate_PrEP, color = scenario_name))
```


```{r}
dat %>% 
  filter(Year > 2020) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Initiate_LAPrEP, color = scenario_name))
```

## VMMC distributed

```{r}
dat <- duet.results %>% 
  mutate(Year = floor(Year - .5)) %>% 
  group_by(sim.ix, scenario_name, Year) %>% 
  summarize(
    Program_VMMC = sum(Program_VMMC * pop_scaling_factor),
    Program_VMMC_Uptake = sum(Program_VMMC_Uptake * pop_scaling_factor)
  ) %>% 
  group_by(scenario_name, Year) %>% 
  summarize(
    Program_VMMC = mean(Program_VMMC),
    Program_VMMC_Uptake = mean(Program_VMMC_Uptake)
  )

dat %>% 
  filter(Year > 2020) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Program_VMMC, color = scenario_name))


dat %>% 
  filter(Year > 2020) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Program_VMMC_Uptake, color = scenario_name))
```

```{r}
dat %>% 
  filter(Year >= 2020)
```

```{r}
results.cut.2025 %>% 
  filter(Year >= 2025) %>% 
  group_by(
  scenario_name, sim.ix, Year) %>% 
  summarize(Died_from_HIV = sum(Died_from_HIV),
            Newly.Infected = sum(Newly.Infected)) %>%
  group_by(scenario_name, Year) %>% 
  summarize(Died_from_HIV = mean(Died_from_HIV),
            Newly.Infected = mean(Newly.Infected))

```

```{r}
results.cut.la %>% 
  filter(Year >= 2025) %>% 
  group_by(
  scenario_name, sim.ix, Year) %>% 
  summarize(Died_from_HIV = sum(Died_from_HIV),
            Newly.Infected = sum(Newly.Infected)) %>%
  group_by(scenario_name, Year) %>% 
  summarize(Died_from_HIV = mean(Died_from_HIV),
            Newly.Infected = mean(Newly.Infected))
```

