---
title: "Duet_manuscript_figures"
output: html_document

---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries 
```{r}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(data.table))
library(magrittr)
library(rsample)
library(patchwork)
```


## Constants
```{r}
SWZ_CENSUS_YEAR = 2017
SWZ_CENSUS_POP = 1148000 # UN WPP 2019, according to SWZ national census 2017 1093238

current_date <- Sys.Date()
date_string_ymd <- format(current_date, format = "%Y%m%d")
```

## Functions
```{r}
bt_mean <- function(splits, colname){
  x <- as.data.frame(analysis(splits))
  mean(x[[colname]])
}

calculate.CI.by.metric = function(data, scenario.name, metric, n = 500){
  bt_resamples <- bootstraps(data %>% filter(scenario_name == scenario.name), times = n)
  
  bt_resamples$mean.metric <- map_dbl(bt_resamples$splits, bt_mean, metric)
  metric_95 <- quantile(bt_resamples$mean.metric, probs = c(0.025, 0.975))
  
  return(
      data.frame(
      scenario_name = scenario.name, 
      metric = metric,
      metric.mean = mean(bt_resamples$mean.metric),
      metric.lb = metric_95[[1]], 
      metric.ub = metric_95[[2]]
    )
  )
}
```

# Read in data

I am going to use the inputs that I had for year long PrEP use, but at PrEP watch levels of initiations

That is version 7, longprep, of the model

```{r}
experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet_longPrEP-baseline_v7___2025_12_04_10_23_36_545931/"

results.baseline <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "baseline",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)


experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet_longPrEP-cut_perm_v7___2025_12_04_10_24_33_055849/"

results.cut.perm <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "cut.perm",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)


experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet_longPrEP-cut_2025_v7___2025_12_04_10_25_02_882835/"

results.cut.2025 <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "cut.2025",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)


experiment.path = "/gpfs/scratch/citrod01/experiments/eSwatini/Duet/Baseline-campaign_20250715_duet_longPrEP-cut_2025_la_v7___2025_12_04_10_25_32_903633/"

results.cut.la <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name =  "cut.la",
  summarize_columns = c("Population","Infected", "On_ART",
                      "Died", "Died_from_HIV", "Newly.Infected","Diagnosed",
                      "Initiate_PrEP","Initiate_LAPrEP","Program_VMMC", "Program_VMMC_Uptake",
                      "PEPFAR_ARTDropout_Yes","PEPFAR_ARTDropout_No","OnART1_initiate","OnART1_initiate_FAILURE"
                      ),
  stratify_columns = c("Year", "Age", "Gender", "IP_Key.OnPrEP"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

duet.results.highprep.v7 <- rbind(
  results.baseline,
  results.cut.perm,
  results.cut.2025,
  results.cut.la
)

sim.results.pop.scaling <- duet.results.highprep.v7 %>%
  filter(Year == SWZ_CENSUS_YEAR) %>%
  group_by(sim.ix, scenario_name) %>%
  summarize(total.pop = sum(Population), .groups = 'drop_last') %>%
  mutate(pop_scaling_factor = SWZ_CENSUS_POP/total.pop)

duet.results.highprep.v7 <- duet.results.highprep.v7 %>%
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.ix", "scenario_name")
  )

```

# Generate Tables

Year (single years from 2000-2031)
Age ([0-15), [15-20),[20-25), [25-30), [30-35), [35-40), [40-45), [45-50), [50-55), [55-60), [60-99))
Total population
People living with HIV
People living with HIV on ART
New HIV acquisitions
HIV-related deaths
Number of Oral PrEP initiations
Number of LA PrEP initiations

## Annual Data

```{r}
# Age bins
age_bins = c(0, 15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 99)
age_labels = c()
for (i in 1:(length(age_bins) - 1)){
  age_labels <- append(age_labels, paste0("[",age_bins[i],":",age_bins[i + 1],")"))
}

# Label each age by its bin
data <- duet.results.highprep.v7 %>% mutate(
  AgeBin = cut(Age, breaks = age_bins, right = FALSE)
  ) %>%
  filter(!is.na(AgeBin))
data$AgeBin_index = factor(data$AgeBin,labels = 1:length(age_labels))

data.staging <- data %>% 
  mutate(Year = floor(Year )) %>% 
  group_by(Year, AgeBin, scenario_name, sim.ix) %>% 
  summarize(
    Population = sum(Population * pop_scaling_factor/2), 
    Infected = sum(Infected * pop_scaling_factor/2), 
    On_ART = sum(On_ART * pop_scaling_factor/2), 
    Newly.Infected = sum(Newly.Infected * pop_scaling_factor),
    Died_from_HIV = sum(Died_from_HIV * pop_scaling_factor),
    Initiate_PrEP = sum(Initiate_PrEP * pop_scaling_factor), 
    Initiate_LAPrEP = sum(Initiate_LAPrEP * pop_scaling_factor),
    .groups = "drop_last"
  )  %>% ungroup()

data.staging <- rbind(
  data.staging, 
  data %>% 
    mutate(Year = floor(Year)) %>% 
    filter(Age >= 15) %>% 
    mutate(AgeBin = "[15,99)") %>% 
    group_by(Year, AgeBin, scenario_name, sim.ix) %>% 
    summarize(
      Population = sum(Population * pop_scaling_factor/2), 
      Infected = sum(Infected * pop_scaling_factor/2), 
      On_ART = sum(On_ART * pop_scaling_factor/2), 
      Newly.Infected = sum(Newly.Infected * pop_scaling_factor),
      Died_from_HIV = sum(Died_from_HIV * pop_scaling_factor),
      Initiate_PrEP = sum(Initiate_PrEP * pop_scaling_factor), 
      Initiate_LAPrEP = sum(Initiate_LAPrEP * pop_scaling_factor),
      .groups = "drop_last"
    ) %>% ungroup()
)

scenario.names = c("baseline", "cut.2025", "cut.la", "cut.perm")
metrics.names = c("Population", "Infected", "On_ART", "Newly.Infected", "Died_from_HIV", "Initiate_PrEP", "Initiate_LAPrEP")
age.bin.list =  c("[0,15)", "[15,20)", "[20,25)", "[25,30)", "[30,35)", "[35,40)", "[40,45)", "[45,50)", "[50,55)", "[55,60)", "[60,99)", "[15,99)")
years.list = c(2020:2030)

metrics.by.year = data.frame()

for (i in scenario.names){
  for (j in years.list) {
    for(k in age.bin.list) {
      for(l in metrics.names){
        print(c(i,j,k,l))
        h <- calculate.CI.by.metric(
          data = data.staging %>% filter(Year == j, AgeBin == k),
          scenario.name = i,
          metric = l)
        
        h$Year = j
        h$Age = k
        
        metrics.by.year = rbind(metrics.by.year, h) 
      }
    }
  }
}
metrics.by.year %>% 
  mutate(Model = "EMOD") %>%   
  select(
    Model,
    Scenario = scenario_name, Year, 
    Age,
    Metric = metric, Mean = metric.mean, Lower.Bound = metric.lb, Upper.Bound = metric.ub) %>% 
  write_csv("Duet_figures/Duet_Metrics_by_Year_2.csv")

```

## Aggregated data
```{r}
data.staging <- data %>% 
  mutate(Year = floor(Year)) %>% 
  filter(Age >= 15) %>% 
  filter(Year %in% c(2025, 2026, 2027, 2028, 2029)) %>% 
  group_by(scenario_name, sim.ix) %>% 
  summarize(
    Newly.Infected = sum(Newly.Infected * pop_scaling_factor),
    Died_from_HIV = sum(Died_from_HIV * pop_scaling_factor),
    Initiate_PrEP = sum(Initiate_PrEP * pop_scaling_factor), 
    Initiate_LAPrEP = sum(Initiate_LAPrEP * pop_scaling_factor),
    .groups = "drop_last"
  ) %>% ungroup()

metrics.aggregated = data.frame()

for (i in metrics.names[c(-1,-2, -3)]){
  for (j in scenario.names) {
    for(l in c("[15,99)")){
      print(c(i,j,l))
      h <- calculate.CI.by.metric(
        data = data.staging,
        scenario.name = j,
        metric = i)

      h$Age = l
      
      metrics.aggregated = rbind(metrics.aggregated, h) 
    }
  }
}

metrics.aggregated

metrics.aggregated %>% 
  select(
    Scenario= scenario_name,
    Age,
    Metric = metric, Mean = metric.mean, Lower.Bound = metric.lb, Upper.Bound = metric.ub) %>% 
  write_csv("Duet_figures/Duet_Metrics_Aggregated_2.csv")

metrics.aggregated <- read_csv("Duet_figures/Duet_Metrics_Aggregated_2.csv")

metrics.aggregated %>% 
  mutate(Model = "EMOD") %>%
  select(
    Model,
    Scenario=  scenario_name,
    Age,
    Metric , Mean , Lower.Bound , Upper.Bound ) %>% 
  write_csv("Duet_figures/Duet_Metrics_Aggregated_2.csv")

```

```{r}
metrics.aggregated
```

## Print out results

### PLHIV
```{r}
metrics.by.year %>% 
  filter(Year == 2029,
         Age == "[15,99)",
         Metric == "Infected") %>% 
  mutate(baseline = metrics.by.year %>% filter(Year == 2029, Age == "[15,99)", Metric == "Infected", scenario_name =="baseline") %>% .$Mean) %>% 
  mutate(diff = Mean - baseline) %>% 
  mutate(pct = diff/baseline)
```



### HIV acquisitions

```{r}
metrics.aggregated %>% 
  filter(Age == "[15,99)",
         Metric == "Newly.Infected") %>% 
  mutate(baseline = metrics.aggregated %>% filter(Age == "[15,99)", Metric == "Newly.Infected", scenario_name =="baseline") %>% .$Mean) %>% 
  mutate(diff = Mean - baseline) %>% 
  mutate(pct = diff/baseline)
```


### HIV deaths

```{r}
metrics.aggregated %>% 
  filter(Age == "[15,99)",
         Metric == "Died_from_HIV") %>% 
  mutate(baseline = metrics.aggregated %>% filter(Age == "[15,99)", Metric == "Died_from_HIV", scenario_name =="baseline") %>% .$Mean) %>% 
  mutate(diff = Mean - baseline) %>% 
  mutate(pct = diff/baseline)
```


### ART Coverage

```{r}
metrics.by.year %>% 
  filter(Year %in% c(2025, 2030),
         Age == "[15,99)",
         Metric %in% c("Infected", "On_ART")) %>% 
  pivot_wider(
    id_cols = c(scenario_name, Year),
    names_from = Metric,
    values_from = Mean
  ) %>% 
  mutate(cov = On_ART/Infected) %>% 
  arrange(Year, scenario_name)
```


# Plots

```{r}
data.metrics.by.year <- read_csv("Duet_figures/Duet_Metrics_by_Year_2.csv")

data.metrics.by.year %>% 
   pivot_wider(id_cols = c(scenario_name, Year, Age),
               names_from = Metric,
               values_from = Mean) %>% 
   filter(Age == "[15,99)")
```

## PLHIV Populations

```{r}
data.metrics.by.year %>% 
  pivot_wider(id_cols = c(scenario_name, Year, Age),
              names_from = Metric,
              values_from = Mean) %>% 
  filter(Age == "[15,99)") %>%
  filter(Year >= 2020) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Infected, color = scenario_name),
            linewidth = 1,
            show.legend = FALSE) +
  scale_color_manual(values = c( "black", "#C41000", "#E69F00", "#0072B2")) +
  scale_x_continuous("Year", breaks =  seq(2020,2030,2)) +
  #scale_y_continuous("PLHIV (thousands)", limits = c(220000,260000), labels = c("220,000","230,000","240,000","250,000","260,000"), breaks = c(220000, 230000, 240000, 250000, 260000)) +
  #scale_y_continuous("") +
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(),
        #axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        axis.title.y = element_blank(),
        #plot.title = element_text(hjust = 0.5),
        text = element_text(family = "sans"),
        axis.text = element_text(size = 14),
        axis.title= element_text(size = 16)
        #axis.text.y = element_text(angle = 45, hjust = .5, vjust = 1)
        )

ggsave("Duet_figures/PLHIV_time_series_longprep_v7.pdf", height = 4, width = 5, units = "in")
```

## HIV Infections

```{r}
data.metrics.by.year %>% 
  pivot_wider(id_cols = c(scenario_name, Year, Age),
              names_from = Metric,
              values_from = Mean) %>% 
  filter(Age == "[15,99)") %>%
  filter(Year >= 2020) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Newly.Infected, color = scenario_name),
            linewidth = 1, show.legend = FALSE) +
  scale_color_manual(values = c( "black", "#C41000", "#E69F00", "#0072B2")) +
  scale_x_continuous("Year", breaks =  seq(2020,2030,2)) +
  #scale_y_continuous("HIV Acquisitions") +
  scale_y_continuous("") +
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(),
        #axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        axis.title.y = element_blank(),
        #plot.title = element_text(hjust = 0.5),
        text = element_text(family = "sans"),
        axis.text = element_text(size = 14),
        axis.title= element_text(size = 16))

ggsave("Duet_figures/HIV_Acquisitions_time_series_longprep_v7.pdf", height = 4, width = 5, units = "in")

```

```{r}
duet.results.highprep.v7 %>%
  mutate(Year = floor(Year)) %>% 
  filter(Age >= 15) %>% 
  mutate(AgeBin = "[15,99)") %>% 
  group_by(Year, AgeBin, scenario_name, sim.ix) %>% 
  summarize(
    Population = sum(Population * pop_scaling_factor), 
    Infected = sum(Infected * pop_scaling_factor), 
    On_ART = sum(On_ART * pop_scaling_factor), 
    Newly.Infected = sum(Newly.Infected * pop_scaling_factor),
    Died_from_HIV = sum(Died_from_HIV * pop_scaling_factor),
    Initiate_PrEP = sum(Initiate_PrEP * pop_scaling_factor), 
    Initiate_LAPrEP = sum(Initiate_LAPrEP * pop_scaling_factor),
    .groups = "drop_last"
  ) %>%
  group_by(Year, AgeBin, scenario_name) %>% 
  summarize(
    Population = mean(Population),
    Infected = mean(Infected), 
    On_ART = mean(On_ART),
    Newly.Infected = mean(Newly.Infected), 
    Died_from_HIV = mean(Died_from_HIV)
  ) %>% 
  filter(Year >= 2024, Year < 2030) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Died_from_HIV, color = scenario_name),
            linewidth = 1, show.legend = FALSE) +
  scale_color_manual(values = c( "black", "#C41000", "#E69F00", "#0072B2")) +
  scale_x_continuous("Year", breaks = c(2024:2031)) +
  #scale_y_continuous("HIV Acquisitions") +
  scale_y_continuous("") +
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(),
        #axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        axis.title.y = element_blank(),
        #plot.title = element_text(hjust = 0.5),
        text = element_text(family = "sans"),
        axis.text = element_text(size = 14),
        axis.title= element_text(size = 16))
```


## HIV Deaths

```{r}
data.metrics.by.year %>% 
  pivot_wider(id_cols = c(scenario_name, Year, Age),
              names_from = Metric,
              values_from = Mean) %>% 
  filter(Age == "[15,99)") %>%
  filter(Year >= 2020) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Died_from_HIV, color = scenario_name),
            linewidth = 1, show.legend = FALSE) +
  scale_color_manual(values = c( "black", "#C41000", "#E69F00", "#0072B2")) +
  scale_x_continuous("Year", breaks =  seq(2020,2030,2)) +
  #scale_y_continuous("HIV Deaths") +
  scale_y_continuous("") +
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(),
        #axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        axis.title.y = element_blank(),
        #plot.title = element_text(hjust = 0.5),
        text = element_text(family = "sans"),
        axis.text = element_text(size = 14),
        axis.title= element_text(size = 16))

ggsave("Duet_figures/HIV_Deaths_time_series_longprep_v7.pdf", height = 4, width = 5, units = "in")

```

## ART coverage

```{r}
data.metrics.by.year %>% 
  pivot_wider(id_cols = c(scenario_name, Year, Age),
              names_from = Metric,
              values_from = Mean) %>% 
  filter(Age == "[15,99)") %>%
  filter(Year >= 2020) %>% 
  mutate(ARTCov = On_ART/Infected) %>% 
  ggplot() + 
    geom_line(mapping = aes(x = Year, y = ARTCov, color = scenario_name),
              linewidth = 1, show.legend = FALSE) +
    scale_color_manual(values = c( "black", "#C41000", "#E69F00", "#0072B2")) +
    scale_x_continuous("Year", breaks =  seq(2020,2030,2)) +
    #scale_y_continuous("HIV Deaths") +
    scale_y_continuous("") +
    theme_minimal() + theme_bw() +
    theme(panel.grid = element_blank(),
          #axis.title.x = element_blank(),
          #axis.text.x = element_blank(),
          axis.title.y = element_blank(),
          #plot.title = element_text(hjust = 0.5),
          text = element_text(family = "sans"),
          axis.text = element_text(size = 14),
          axis.title= element_text(size = 16))

ggsave("Duet_figures/ARTCov_time_series_longprep_v7.pdf", height = 4, width = 5, units = "in")

```

## PrEP initiations

### Oral PrEP

```{r}
data.metrics.by.year %>% 
  pivot_wider(id_cols = c(scenario_name, Year, Age),
              names_from = Metric,
              values_from = Mean) %>% 
  filter(Age == "[15,99)") %>%
  filter(Year >= 2020) %>% 
  mutate(ARTCov = On_ART/Infected) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Initiate_PrEP, color = scenario_name),
            linewidth = 1, show.legend = FALSE) +
  scale_color_manual(values = c( "black", "#C41000", "#E69F00", "#0072B2")) +
  scale_x_continuous("Year", breaks = c(2020, 2025, 2030)) +
  scale_y_continuous("PrEP Initiations") +
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(),
        #axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        #plot.title = element_text(hjust = 0.5),
        text = element_text(family = "sans"),
        axis.text = element_text(size = 14),
        axis.title= element_text(size = 16))

ggsave("Duet_figures/PrEP_oral_time_series_longprep_v7.pdf", height = 4, width = 5, units = "in")
```


### LA PrEP

```{r}
data.metrics.by.year %>% 
  pivot_wider(id_cols = c(scenario_name, Year, Age),
              names_from = Metric,
              values_from = Mean) %>% 
  filter(Age == "[15,99)") %>%
  filter(Year >= 2020) %>% 
  mutate(ARTCov = On_ART/Infected) %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = Initiate_LAPrEP, color = scenario_name),
            linewidth = 1, show.legend = FALSE) +
  scale_color_manual(values = c( "black", "#C41000", "#E69F00", "#0072B2")) +
  scale_x_continuous("Year", breaks = c(2020, 2025, 2030)) +
  scale_y_continuous("PrEP Initiations") +
  theme_minimal() + theme_bw() +
  theme(panel.grid = element_blank(),
        #axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        #plot.title = element_text(hjust = 0.5),
        text = element_text(family = "sans"),
        axis.text = element_text(size = 14),
        axis.title= element_text(size = 16))

ggsave("Duet_figures/PrEP_LA_time_series_longprep_v7.pdf", height = 4, width = 5, units = "in")
```

