---
title: "SWZ_calibration_check"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The purpose of this notebook is to compare the Swaziland model output against the calibration targets

```{r Load Libraries, echo = FALSE}
library(tidyverse)
library(tidyr)
library(data.table)
library(magrittr)
library(ggplot2)
library(devtools)
library(readxl)
library(spatstat)
#devtools::install_github("BershteynLab/EMODAnalyzeR")
```

```{r}
CENSUS_YEAR = 2017
SWZ_CENSUS_POP = 1148000 # UN WPP 2019, according to SWZ national census 2017 1093238
```

## Import data

```{r, echo=FALSE}
sim.results <- EMODAnalyzeR::read.simulation.results(
  results_path = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/test2/Baseline-campaign_20231113-baseline/ReportHIVByAgeAndGender",
  scenario_name = 'baseline',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  stratify_columns = c("Year", "Gender", "Age"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

sim.results.pop.scaling <- sim.results %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.id) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = SWZ_CENSUS_POP/total.pop)

sim.results <- sim.results %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.id")
  )

```

# Prevalence

```{r, echo=FALSE}
ingest.file.base = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/Data/calibration_ingest_form-Swaziland_ART_vars--UPDATED--2023-07.xlsm"

obs.prev.sheet.base <- EMODAnalyzeR::read.ingest.sheet(ingest.file.base, "Obs-Prevalence")
obs.prev.sheet.base <- obs.prev.sheet.base %>% filter(!is.na(AgeBin))

# DHS data for adults 15-50
# 2006
# Female: 31.1 [29.3, 32.9]
# Male: 19.7 [17.9, 21.5]

# PHIA data for adults 15 +
# 2016
# Female: 32.5 [31,34]
# Male: 20.4 [18.9, 21.9]

# Note the differences in age brackets. Depending on whether we look at Adults 15-50 or Adults 15+ we will match one or the ohter dataset but not both.
calib.targets.prev.all <- data.table(Year = c(2006, 2006, 2016, 2016),
                                     Gender = c("Male", "Female", "Male", "Female"),
                                     prev = c(19.7, 31.1, 20.4, 32.5),
                                     lb = c(17.9, 29.3, 18.9, 31),
                                     ub = c(21.5, 32.9, 21.9, 34))

obs.prev.sheet.base %>% head
```

```{r, fig.width=8}
data <- EMODAnalyzeR::calculate.prevalence(
  sim.results %>% filter(Age >=15, Age < 50),
         stratify_columns = c("Year", "Gender", "sim.id", "scenario_name"),
         numerator = "Infected",
         denominator = "Population")

prev.data.mean <- data %>%
    dplyr::group_by(Year, Gender, scenario_name) %>%
    dplyr::summarise(Prevalence = mean(Prevalence), .groups = 'keep') %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

ggplot() +
    geom_line(data= prev.data.mean %>% filter(Year > 2000),
              aes(x=Year, y=Prevalence, group=scenario_name, color=scenario_name), linewidth=.75)+
    geom_point(data = calib.targets.prev.all,
               mapping = aes(x = Year, y = prev/100)) +
    geom_errorbar(data = calib.targets.prev.all,
               mapping = aes(x = Year, ymin = lb/100, ymax = ub/100)) +
    facet_wrap(~ Gender, ncol=2) +
    xlab("Year")+
    #xlim(c(date.start, date.end)) +
    ylab("Prevalence") +
    theme_bw(base_size=16) +
    guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
    scale_x_continuous(breaks = seq(1980,2040,10)) +
    theme(legend.position="bottom") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    theme(strip.background = element_rect(colour="black", fill="white")) +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    #scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0,0.25,0.05), limits=c(0, 0.25)) +
      ylab("HIV Prevalence (%)") + 
    scale_color_manual(values=c("blue")) 

ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/Analysis/prev_all_ages_calib.pdf",
       width = 8, height = 6, units = "in")
```

```{r}
prev.20.49 <- data.table(Year = c(2006, 2006, 2011,2011, 2016, 2016, 2021, 2021),
                         Gender = c("Female", "Male"),
                         prev = c(0.38861021, 0.282294676, 0.462308369, 0.274811025, 0.421160235, 0.26133829, 0.384828736, 0.195259228))

data <- EMODAnalyzeR::calculate.prevalence(
  sim.results %>% filter(Age >=20, Age < 50),
         stratify_columns = c("Year", "Gender", "sim.id", "scenario_name"),
         numerator = "Infected",
         denominator = "Population")

prev.data.mean <- data %>%
    dplyr::group_by(Year, Gender, scenario_name) %>%
    dplyr::summarise(Prevalence = mean(Prevalence), .groups = 'keep') %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

ggplot() +
    geom_line(data= prev.data.mean %>% filter(Year > 2000),
              aes(x=Year, y=Prevalence, group=scenario_name, color=scenario_name), linewidth=.75)+
    geom_point(data = prev.20.49,
               mapping = aes(x = Year, y = prev)) +
    facet_wrap(~ Gender, ncol=2) +
    xlab("Year")+
    #xlim(c(date.start, date.end)) +
    ylab("Prevalence") +
    theme_bw(base_size=16) +
    guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
    scale_x_continuous(breaks = seq(1980,2040,10)) +
    theme(legend.position="bottom") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    theme(strip.background = element_rect(colour="black", fill="white")) +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    #scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0,0.25,0.05), limits=c(0, 0.25)) +
      ylab("HIV Prevalence (%)") + 
    scale_color_manual(values=c("blue")) 


ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/Analysis/prev_adults.pdf",
       width = 8, height = 6, units = "in")
```


# Prevalence by Age

```{r, fig.width=10, fig.height=10}
age_bins = c(15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65,99)
subset_years = c(2007, 2011, 2016, 2021)

# Subset data on years
data <- sim.results %>% filter(Year %in% subset_years)

# Age bins
age_labels = c()
for (i in 1:(length(age_bins) - 1)){
  age_labels <- append(age_labels, paste0("[",age_bins[i],":",age_bins[i + 1],")"))
}

# Label each age by its bin
data <- data %>% mutate(
  AgeBin = cut(Age, breaks = age_bins, right = FALSE)
  ) %>%
  filter(!is.na(AgeBin))
data$AgeBin_index = factor(data$AgeBin,labels = 1:length(age_labels))

# Calculate prevalence, grouping by age bin
data.prev <- data %>% EMODAnalyzeR::calculate.prevalence(
  stratify_columns = c("Year", "AgeBin_index", "AgeBin", "Gender", "scenario_name", "sim.id"),
  numerator = "Infected",
  denominator = "Population")

# Calculate mean prevalence across all sim runs
data.mean <- data.prev %>%
  dplyr::group_by(Year, AgeBin_index, AgeBin, Gender, scenario_name) %>%
  dplyr::summarize(mean.Prevalence = mean(Prevalence),
            sd.Prevalence = sd(Prevalence),
            .groups = 'keep') %>%
  ungroup() %>%
  dplyr::mutate(upper = mean.Prevalence + 2*sd.Prevalence,
                lower = case_when(mean.Prevalence - 2 * sd.Prevalence > 0 ~ mean.Prevalence - 2 * sd.Prevalence,
                         mean.Prevalence - 2 * sd.Prevalence <= 0 ~ 0)
                )

# Transform data
data.mean <- data.mean %>% mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

# Reformat the prevalence data:
obs.prev.sheet.base <- obs.prev.sheet.base %>% 
  mutate(AgeBin_index = factor(obs.prev.sheet.base$AgeBin,labels = 1:length(age_labels)))

p <- data.mean %>%
  ggplot() +
  geom_point(data = obs.prev.sheet.base,
             mapping = aes(x = AgeBin_index, y = Prevalence), 
             size = 3, color = 'black', shape = 0,
             show.legend = FALSE) +
  geom_errorbar(data = obs.prev.sheet.base,
             mapping = aes(x = AgeBin_index, ymin = lb, ymax = ub),
             size = 1, color = 'black',
             show.legend = FALSE) +
  # plot means
  geom_point(
    mapping = aes(x = AgeBin_index, y = mean.Prevalence, color = Gender),
    size=1,
     show.legend = FALSE
  ) +
  geom_errorbar(
    mapping = aes(x=AgeBin_index, ymin=lower, ymax=upper, color=Gender),
    width=.15, size=1,
   show.legend = FALSE) +
  facet_grid(cols = vars(Gender), rows = vars(Year)) +
  xlab("Age") +
  ylab("Prevalence") +
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_discrete(
    breaks = 1:length(age_labels),
    labels = age_labels
    ) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_manual(values=c("blue", "red"))
  
p

ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/Analysis/hiv_age_prev.pdf",
       width = 12, height = 6, units = "in")
  
```

```{r}
ggplot() +
  geom_point(data = obs.prev.sheet.base,
             mapping = aes(x = AgeBin_index, y = Prevalence, color = Gender), 
             size = 3, shape = 0,
             show.legend = FALSE) +
  geom_errorbar(data = obs.prev.sheet.base,
             mapping = aes(x = AgeBin_index, ymin = lb, ymax = ub, color = Gender),
             size = 1
             show.legend = FALSE) +
  facet_grid(cols = vars(Gender), rows = vars(Year)) +
  xlab("Age") +
  ylab("Prevalence") +
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_discrete(
    breaks = 1:length(age_labels),
    labels = age_labels
    ) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_manual(values=c("blue", "red"))

ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/Analysis/hiv_age_prev_data.pdf",
       width = 12, height = 8, units = "in")
```


## Mean age of infected population over time:

Method here is counting number of infected people in each age group:
```{r}

# These are the means that kasturi calculated
mean.age.plhiv.dat <- data.table(Year = c(2006, 2011, 2016), 
           Gender = c("Male", "Male", "Male", "Female", "Female", "Female"),
           mean.age.plhiv = c(32.83, 37.26,39.88, 29.10, 30.41, 35.80))

Infected.by.age = sim.results %>% 
  filter(Age >= 15) %>% 
  group_by(Year, Gender, Age, scenario_name, sim.ix) %>% 
  summarize(Infected = sum(Infected), .groups = 'keep') %>% 
  group_by(Year, Gender, Age, scenario_name) %>% 
  summarize(Infected = mean(Infected), .groups = 'keep') %>% 
  ungroup()


Infected.by.age <- Infected.by.age %>% 
  merge(
    Infected.by.age %>% 
      group_by(Year, Gender, scenario_name) %>% 
      summarize(Infected.total = sum(Infected)),
    by = c("Year", "Gender", "scenario_name")
) %>% 
  mutate(prod = case_when(Infected.total > 0 ~ Age * Infected,
                          Infected.total == 0 ~ 0)
         ) %>% 
  group_by(Year, Gender, scenario_name) %>% 
  summarize(mean.age = sum(prod), Infected.total = mean(Infected.total)) %>% 
  ungroup() %>% 
  mutate(prod = case_when(Infected.total > 0 ~ mean.age/Infected.total,
                          Infected.total == 0 ~ 0)
       ) %>% 
  arrange(Gender, Year)
  
Infected.by.age %>% 
  filter(Year > 1990) %>% 
    mutate(Gender = factor(Gender, labels = c( "Male", "Female")))  %>%
  ggplot() + 
  geom_point(mapping = aes(x = Year, y = prod, color = Gender)) + 
  geom_point(data = mean.age.plhiv.dat, 
             mapping = aes(x = Year, y = mean.age.plhiv, color = Gender), shape = 0, size = 3) +
  theme_bw(base_size=16) +
    guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
    scale_x_continuous(breaks = seq(1990,2040,10)) +
    theme(legend.position="bottom") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    theme(strip.background = element_rect(colour="black", fill="white")) +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    ylab("Mean Age of PLHIV (15+)") + 
  scale_color_manual(values = c("darkred", "darkblue"))

ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/Analysis/hiv_mean_age_15plus.pdf",
       width = 5, height = 4, units = "in")

```

## Age distribution among PLHIV

Among all PLHIV, what is the distribution across ages? What fraction of PLHIV are in each age category?

```{r}
age_bins = c(15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65,99)
subset_years = c(2007, 2011, 2016, 2021)

# Subset data on years
data <- sim.results %>% filter(Year %in% subset_years)

# Age bins
age_labels = c()
for (i in 1:(length(age_bins) - 1)){
  age_labels <- append(age_labels, paste0("[",age_bins[i],":",age_bins[i + 1],")"))
}

# Label each age by its bin
data <- data %>% mutate(
  AgeBin = cut(Age, breaks = age_bins, right = FALSE)
  ) %>%
  filter(!is.na(AgeBin))
data$AgeBin_index = factor(data$AgeBin,labels = 1:length(age_labels))

# Count total PLHIV in each year:
plhiv.frac <- data %>% merge(
  data %>% group_by(Year, Gender, scenario_name, sim.ix) %>% 
  summarize(PLHIV = sum(Infected)),
  by = c("Year", "Gender", "scenario_name", "sim.ix")
) %>% 
  ungroup %>% 
  mutate(PLHIV.frac = case_when(PLHIV == 0 ~ 0, 
                                PLHIV > 0 ~ Infected/PLHIV)) %>% 
  group_by(Year, AgeBin_index, AgeBin, Gender, scenario_name) %>% 
  summarize(
    sd.PLHIV.frac = sd(PLHIV.frac),
    mean.PLHIV.frac = mean(PLHIV.frac), .groups = 'keep' ) %>% 
  ungroup %>% 
  mutate(upper = mean.PLHIV.frac + 2*sd.PLHIV.frac,
                lower = case_when(mean.PLHIV.frac - 2 * sd.PLHIV.frac > 0 ~ mean.PLHIV.frac - 2 * sd.PLHIV.frac,
                         mean.PLHIV.frac - 2 * sd.PLHIV.frac <= 0 ~ 0)
                )

# Transform data
plhiv.frac <- plhiv.frac %>% mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

p <- plhiv.frac %>%
  ggplot() +
  # plot means
  geom_point(
    mapping = aes(x = AgeBin_index, y = mean.PLHIV.frac, color = Gender),
    size=1,
     show.legend = FALSE
  ) +
  geom_errorbar(
    mapping = aes(x=AgeBin_index, ymin=lower, ymax=upper, color=Gender),
    width=.15, size=1,
   show.legend = FALSE) +
  facet_grid(cols = vars(Gender), rows = vars(Year)) +
  xlab("Age") +
  ylab("Prevalence") +
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_discrete(
    breaks = 1:length(age_labels),
    labels = age_labels
    ) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_manual(values=c("blue", "red"))
  
p

ggsave(
  filename = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/Analysis/hiv_plhiv_age_dist.pdf",
  width = 12, height = 6, units = "in"
  )

```


# Population

### Population by age

```{r}
ingest.file.base = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/Data/calibration_ingest_form-Swaziland--UPDATED--2023-12.xlsm"

obs.pop.sheet <- EMODAnalyzeR::read.ingest.sheet(ingest.file.base, "Obs-Population")
obs.pop.sheet <- obs.pop.sheet %>% filter(!is.na(AgeBin))

age_bins = c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65,70,75,80,85,90,95,99)
age_labels = c()
for (i in 1:(length(age_bins) - 1)){
  age_labels <- append(age_labels, paste0("[",age_bins[i],":",age_bins[i + 1],")"))
}

obs.pop.sheet <- obs.pop.sheet %>% 
  #mutate(AgeBin_index = factor(obs.pop.sheet$AgeBin, levels = age_labels, labels = 1:length(age_labels)))
  mutate(AgeBin = factor(obs.pop.sheet$AgeBin, levels = age_labels)) %>% 
  mutate(AgeBin = fct_relevel(AgeBin, age_labels)) %>% 
  mutate(AgeBin_index = factor(obs.pop.sheet$AgeBin, 
                               levels = age_labels,
                               labels = 1:20)
         )

obs.pop.sheet$AgeBin_index <- as.numeric(obs.pop.sheet$AgeBin_index)

#obs.pop.sheet %>% View
```


```{r, fig.height=10, fig.width=8}
# Subset data on years
subset_years = c(2000, 2010,2020)
data <- sim.results %>% filter(Year %in% subset_years)

# Label each age by its bin
age_bins = c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65,70,75,80,85,90,95,99)
age_labels = c()
for (i in 1:(length(age_bins) - 1)){
  age_labels <- append(age_labels, paste0("[",age_bins[i],":",age_bins[i + 1],")"))
}
data <- data %>% mutate(
  AgeBin = cut(Age, breaks = age_bins, right = FALSE)
  ) %>%
  filter(!is.na(AgeBin))
data$AgeBin_index = factor(data$AgeBin,labels = 1:length(age_labels))

# Count total people in each year:
pop.data <- data %>% 
  group_by(Year, Gender, AgeBin_index, AgeBin, scenario_name, sim.ix) %>% 
  summarize(Population = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, Gender, AgeBin_index,  AgeBin, scenario_name) %>% 
  summarize(sd.Population = sd(Population),
            mean.Population = mean(Population), .groups = 'keep') %>% 
  ungroup %>% 
  mutate(
    upper = mean.Population + 2*sd.Population,
    lower = case_when(
      mean.Population - 2 * sd.Population > 0 ~ mean.Population - 2 * sd.Population,
      mean.Population - 2 * sd.Population <= 0 ~ 0)
                ) %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

p <- pop.data %>% 
  ggplot() +
  # plot the data too
  geom_point(
    data = obs.pop.sheet %>% filter(Year %in% subset_years), 
    mapping = aes(x = AgeBin_index, y = Population/1000), 
    color = 'black', shape = 0, size = 3
  ) + 
  geom_errorbar(
    data = obs.pop.sheet %>% filter(Year %in% subset_years), 
    mapping = aes(x = AgeBin_index, ymin = lb/1000, ymax = ub/1000), 
    color = 'black', size = 1
  ) + 
  # plot means from the simulation
  geom_point(
    mapping = aes(x = AgeBin_index, y = mean.Population/1000, color = Gender),
    size=1,
   show.legend = FALSE
  ) +
  geom_errorbar(
    mapping = aes(x=AgeBin_index, ymin=lower/1000, ymax=upper/1000, color=Gender),
    width=.15, size=1,
   show.legend = FALSE) +
  facet_grid(cols = vars(Gender), rows = vars(Year)) +
  xlab("Age") +
  ylab("Population (Thousands)") +
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_discrete(
    breaks = 1:length(age_labels),
    labels = age_labels
    ) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_manual(values=c("blue", "red"))
  
p

ggsave(
  filename = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/Analysis/pop_by_age.pdf",
       width = 10, height = 8, units = "in")

```

What's going on, looks like there's some bump in population in the age group 35-40 in the year 2000, 40-45 in the year 2005, 45-50 in 2010
So this is the cohort born between 1960-1965. There are too many.
And then, there are too many young people in the simulation by 2020


```{r}
pop.data %>% filter(Year == 2010)
```


### Total population

These are the populations from UN WPP
```{r}
pop.unwpp <- rbind(
  data.table(
    Year = c(1950:2020),
    Population = 1000*c(133, 136, 139, 141, 144, 147, 150, 153, 156, 160, 163, 166, 170, 173, 177, 182, 186, 191, 197, 203, 208, 214, 219, 225, 232, 238, 246, 254, 262, 271, 281, 290, 300, 310, 321, 332, 343, 354, 366, 378, 389, 401, 411, 422, 432, 442, 452, 462, 471, 478, 483, 487, 488, 489, 489, 489, 490, 492, 495, 498, 502, 507, 512, 519, 525, 532, 540, 547, 555, 563, 570),
    Gender = "Male"),
  data.table(
    Year = c(1950:2020),
    Population = 1000*c(140, 144, 147, 150, 153, 156, 159, 163, 166, 170, 173, 177, 180, 184, 188, 192, 198, 203, 210, 216, 223, 230, 238, 245, 253, 261, 270, 278, 287, 297, 307, 318, 330, 342, 355, 368, 381, 394, 408, 421, 433, 445, 456, 466, 475, 485, 493, 502, 509, 516, 522, 527, 531, 534, 538, 541, 546, 550, 555, 559, 563, 565, 567, 568, 570, 572, 574, 578, 581, 585, 590),
    Gender = "Female"
  )
)
```

Comparing total population
```{r}
pop.data.total <- sim.results %>% 
  group_by(Year, Gender, sim.ix) %>% 
  summarize(Population = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, Gender) %>% 
  summarize(mean.Population = mean(Population), .groups = 'keep') %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

pop.data.total %>% 
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = mean.Population/1000, color = Gender)) + 
  geom_line(data = pop.unwpp,
    mapping = aes(x = Year, y = Population/1000), color = 'black', size = 1) +
  facet_grid(cols = vars(Gender)) + 
  xlab("Year") +
  ylab("Total Population (Thousands)") +
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_manual(values=c("blue", "red"))

ggsave(
  filename = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/Analysis/total_pop.pdf",
       width = 10, height = 8, units = "in")
```

### Deaths all causes
```{r}
mort.all <- sim.results %>% group_by(Year, Gender, sim.ix) %>% 
  summarize(Died = sum(Died * pop.scaling.factor),
            Population = sum(Population * pop.scaling.factor)) %>% 
  group_by(Year, Gender) %>% 
  summarize(Died = mean(Died),
            Population = mean(Population)) %>% 
  ungroup() %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female")) %>% 
  mutate(mort.rate = case_when(Population == 0 ~ 0, Population > 0 ~ Died/Population)) 

mort.all %>% 
  ggplot() +  
   #geom_line(mapping = aes(x = Year, y = Died, color = Gender)) + 
    geom_line(mapping = aes(x = Year, y = mort.rate, color = Gender)) + 
    facet_grid(cols = vars(Gender)) + 
    xlab("Year") +
    ylab("Death Rate") +
    theme_bw(base_size=16) +
    guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
    theme(legend.position="bottom") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    theme(strip.background = element_rect(colour="black", fill="white")) +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    scale_color_manual(values=c("blue", "red"))
```
### Deaths from HIV

```{r}
hiv.mort <- sim.results %>% group_by(Year, Gender, sim.ix) %>% 
  summarize(Died = sum(Died_from_HIV * pop.scaling.factor),
            Population = sum(Population * pop.scaling.factor)) %>% 
  group_by(Year, Gender) %>% 
  summarize(Died = mean(Died),
            Population = mean(Population)) %>% 
  ungroup() %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female")) %>% 
  mutate(mort.rate = case_when(Population == 0 ~ 0, Population > 0 ~ Died/Population))

hiv.mort %>% 
  ggplot() +  
   #geom_line(mapping = aes(x = Year, y = Died, color = Gender)) + 
    geom_line(mapping = aes(x = Year, y = mort.rate, color = Gender)) + 
    facet_grid(cols = vars(Gender)) + 
    xlab("Year") +
    ylab("Death Rate") +
    theme_bw(base_size=16) +
    guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
    theme(legend.position="bottom") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    theme(strip.background = element_rect(colour="black", fill="white")) +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    scale_color_manual(values=c("blue", "red"))
```

```{r}
mort.all$row <- "All"

hiv.mort$row <- "HIV"

mort.dat <- rbind(mort.all, hiv.mort)


p <- ggplot() +  
  geom_line(mort.dat, mapping = aes(x = Year, y = mort.rate, color = Gender), 
            size = 2) + 
  facet_grid(cols = vars(Gender), rows = vars(row)) + 
  xlab("Year") +
  ylab("Death Rate") +
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_manual(values=c("blue", "red"))

p

ggsave(
  filename = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/Analysis/mortality.pdf",
       width = 10, height = 8, units = "in")
```
### Deaths by age group

# Incidence

### Incidence ages 15-49

```{r}
# 2011 SHIMS
# <https://www-ncbi-nlm-nih-gov.ezproxy.med.nyu.edu/pmc/articles/PMC5291824/>
# 2016
# <https://phia.icap.columbia.edu/wp-content/uploads/2019/05/SHIMS2_Final-Report_05.03.2019_forWEB.pdf>
# 2021
# <https://phia.icap.columbia.edu/wp-content/uploads/2023/12/241123_SHIMS_ENG_RR3_Final-1.pdf>
# Ages 15-49
incidence.data <- data.table(Year = c(2011, 2011, 2016, 2016, 2021, 2021),
                                     Gender = c("Male", "Female"),
                                     inc = c(1.7,3.1,.99, 1.99, .2, 1.45),
                                     lb = c(1.3, 2.6, .032, 1.09, 0, 0.69 ),
                                     ub = c(2.1,3.7, 1.66, 2.88, .48, 2.2))
```


```{r}
# Subset data on years
data <- sim.results %>% filter(Age >= 15, Age < 50)

# Calculate incidence
data$Year_Integer <- floor((data$Year-0.5))
# Aggregate number of new infections each year, broken down by Year_Integer and Gender
trajectories_IR.1a <- aggregate(Newly.Infected ~ Year_Integer+Gender + sim.id+scenario_name, data=data,FUN=sum)
#Make the denominator as HIV-negative individuals
trajectories_IR.2 <- aggregate(Population - Infected ~ Year+Gender + sim.id+scenario_name, data=data, FUN=sum)
trajectories_IR.2$Year_Integer <- floor(trajectories_IR.2$Year-0.5)
#remove second instance of duplicate rows
trajectories_IR.2 <- trajectories_IR.2[!duplicated(trajectories_IR.2[c("Year_Integer","Gender", "sim.id","scenario_name")]),]
trajectories_IR.2 <- trajectories_IR.2[-match("Year",names(trajectories_IR.2))]
trajectories_IRoverall <- merge(trajectories_IR.1a, trajectories_IR.2, by=c("Year_Integer","Gender","sim.id","scenario_name"))
trajectories_IRoverall$incidence <- trajectories_IRoverall$Newly.Infected / (trajectories_IRoverall$Population)
data <- trajectories_IRoverall %>% dplyr::rename(Year = Year_Integer)

# Calculate mean incidence across all sim runs
data.mean <- data %>%
  dplyr::group_by(Year, Gender, scenario_name) %>%
  dplyr::summarize(mean.Incidence = mean(incidence),
                  sd.Incidence = sd(incidence),
            .groups = 'keep') %>%
  ungroup() %>%
  dplyr::mutate(upper = mean.Incidence + 2*sd.Incidence,
                lower = case_when(mean.Incidence - 2 * sd.Incidence > 0 ~ mean.Incidence - 2 * sd.Incidence,
                         mean.Incidence - 2 * sd.Incidence <= 0 ~ 0)
                )

# Transform data
data.mean <- data.mean %>% mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

p <- data.mean %>%
  ggplot() +
  # plot means
  geom_point(
    mapping = aes(x = Year, y = mean.Incidence*100, color = Gender),
    size=2,
     show.legend = FALSE
  ) +
  geom_errorbar(
    mapping = aes(x=Year, ymin=lower*100, ymax=upper*100, color=Gender),
    width=.15, size=1,
   show.legend = FALSE) +
  geom_point(data = incidence.data, 
             mapping = aes(x = Year, y = inc), color = 'black') + 
  geom_errorbar(data = incidence.data, 
    mapping = aes(x = Year, ymin = lb, ymax = ub), color = 'black') + 
  facet_grid(cols = vars(Gender)) +
  xlab("Age") +
  ylab("Incidence (%)") +
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_continuous(breaks = c(1975, 1980, 1985, 1990, 1995, 2000, 2005, 2010, 2015, 2020, 2025),
                     limits = c(1975, 2025)) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_manual(values=c("blue", "red"))
  
p

ggsave(
  filename = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/Analysis/incidence_all_ages.pdf",
       width = 8, height = 6, units = "in")
```

# Incidence by age
```{r}
age_bins = c(15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65,100)
subset_years = c(2007, 2011, 2016, 2021)

# Subset data on years
data <- sim.results %>% filter(Year %in% subset_years)

# Calculate incidence
data$Year_Integer <- floor((data$Year-0.5))
# Aggregate number of new infections each year, broken down by Year_Integer and Gender
trajectories_IR.1a <- aggregate(Newly.Infected ~ Year_Integer+Gender+Age + sim.id+scenario_name, data=data,FUN=sum)
#Make the denominator as HIV-negative individuals
trajectories_IR.2 <- aggregate(Population - Infected ~ Year+Gender+Age + sim.id+scenario_name, data=data, FUN=sum)
trajectories_IR.2$Year_Integer <- floor(trajectories_IR.2$Year-0.5)
#remove second instance of duplicate rows
trajectories_IR.2 <- trajectories_IR.2[!duplicated(trajectories_IR.2[c("Year_Integer","Gender","Age", "sim.id","scenario_name")]),]
trajectories_IR.2 <- trajectories_IR.2[-match("Year",names(trajectories_IR.2))]
trajectories_IRoverall <- merge(trajectories_IR.1a, trajectories_IR.2, by=c("Year_Integer","Gender","Age", "sim.id","scenario_name"))
trajectories_IRoverall$incidence <- trajectories_IRoverall$Newly.Infected / (trajectories_IRoverall$Population)
data <- trajectories_IRoverall %>% dplyr::rename(Year = Year_Integer)

# Age bins
age_labels = c()
for (i in 1:(length(age_bins) - 1)){
  age_labels <- append(age_labels, paste0("[",age_bins[i],":",age_bins[i + 1],")"))
}

# Label each age by its bin
data <- data %>% mutate(
  AgeBin = cut(Age, breaks = age_bins, right = FALSE)
  ) %>%
  filter(!is.na(AgeBin))
data$AgeBin_index = factor(data$AgeBin,labels = 1:length(age_labels))

# Calculate mean prevalence across all sim runs
data.mean <- data %>%
  dplyr::group_by(Year, AgeBin_index, AgeBin, Gender, scenario_name) %>%
  dplyr::summarize(mean.Incidence = mean(incidence),
                  sd.Incidence = sd(incidence),
            .groups = 'keep') %>%
  ungroup() %>%
  dplyr::mutate(upper = mean.Incidence + 2*sd.Incidence,
                lower = case_when(mean.Incidence - 2 * sd.Incidence > 0 ~ mean.Incidence - 2 * sd.Incidence,
                         mean.Incidence - 2 * sd.Incidence <= 0 ~ 0)
                )

# Transform data
data.mean <- data.mean %>% mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

p <- data.mean %>%
  ggplot() +
  # plot means
  geom_point(
    mapping = aes(x = AgeBin_index, y = mean.Incidence*100, color = Gender),
    size=2,
     show.legend = FALSE
  ) +
  geom_errorbar(
    mapping = aes(x=AgeBin_index, ymin=lower*100, ymax=upper*100, color=Gender),
    width=.15, size=1,
   show.legend = FALSE) +
  facet_grid(cols = vars(Gender), rows = vars(Year)) +
  xlab("Age") +
  ylab("Incidence (%)") +
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_discrete(
    breaks = 1:length(age_labels),
    labels = age_labels
    ) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_manual(values=c("blue", "red"))
  
p

# ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/Analysis/hiv_age_incidence.pdf",
#        width = 12, height = 6, units = "in")

```

### Incidence comparison with SHIMS report

```{r}
# SHIMS annual report on incidence, 2016
inc.data <- data.table(
  Year = rep(2016, 6),
  Gender = c("Male","Male","Male", "Female", "Female", "Female"),
  AgeBin = c("[15,25)", "[25:35)","[35:50)", "[15,25)", "[25:35)","[35:50)"),
  AgeBin_index = c(1,2,3,1,2,3),
  Incidence = c(.79, 1.5, .68, 1.87, 1.84, 2.4),
  lb = c(.07, 0, 0 , .76, .17, .45),
  ub = c( 1.5, 3.06, 1.85, 2.98, 3.48, 4.33)
)
```


```{r}
age_bins = c(15, 25, 35,50)
subset_years = c(2016)

# Subset data on years
data <- sim.results #%>% filter(Year %in% subset_years)

# Calculate incidence
data$Year_Integer <- floor((data$Year-0.5))
# Aggregate number of new infections each year, broken down by Year_Integer and Gender
trajectories_IR.1a <- aggregate(Newly.Infected ~ Year_Integer+Gender+Age + sim.id+scenario_name, data=data,FUN=sum)
#Make the denominator as HIV-negative individuals
trajectories_IR.2 <- aggregate(Population - Infected ~ Year+Gender+Age + sim.id+scenario_name, data=data, FUN=sum)
trajectories_IR.2$Year_Integer <- floor(trajectories_IR.2$Year-0.5)
#remove second instance of duplicate rows
trajectories_IR.2 <- trajectories_IR.2[!duplicated(trajectories_IR.2[c("Year_Integer","Gender","Age", "sim.id","scenario_name")]),]
trajectories_IR.2 <- trajectories_IR.2[-match("Year",names(trajectories_IR.2))]
trajectories_IRoverall <- merge(trajectories_IR.1a, trajectories_IR.2, by=c("Year_Integer","Gender","Age", "sim.id","scenario_name"))
trajectories_IRoverall$incidence <- trajectories_IRoverall$Newly.Infected / (trajectories_IRoverall$Population)
data <- trajectories_IRoverall %>% dplyr::rename(Year = Year_Integer)

# Age bins
age_labels = c()
for (i in 1:(length(age_bins) - 1)){
  age_labels <- append(age_labels, paste0("[",age_bins[i],":",age_bins[i + 1],")"))
}

# Label each age by its bin
data <- data %>% mutate(
  AgeBin = cut(Age, breaks = age_bins, right = FALSE)
  ) %>%
  filter(!is.na(AgeBin))
data$AgeBin_index = factor(data$AgeBin,labels = 1:length(age_labels))

# Calculate mean incidence across all sim runs
data.mean <- data %>%
  dplyr::group_by(Year, AgeBin_index, AgeBin, Gender, scenario_name) %>%
  dplyr::summarize(mean.Incidence = mean(incidence),
                  sd.Incidence = sd(incidence),
            .groups = 'keep') %>%
  ungroup() %>%
  dplyr::mutate(
    upper = mean.Incidence + 2*sd.Incidence,
    lower = case_when(
      mean.Incidence - 2 * sd.Incidence > 0 ~ mean.Incidence - 2 * sd.Incidence,
      mean.Incidence - 2 * sd.Incidence <= 0 ~ 0)
    )  %>% mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

p <- data.mean %>% filter(Year == 2016) %>% 
  ggplot() +
  # plot means
  geom_point(
    mapping = aes(x = AgeBin_index, y = mean.Incidence*100, color = Gender),
    size=2,
     show.legend = FALSE
  ) +
  geom_errorbar(
    mapping = aes(x=AgeBin_index, ymin=lower*100, ymax=upper*100, color=Gender),
    width=.15, size=1,
   show.legend = FALSE) +
  # shims data 
  geom_point(
    data = inc.data, 
    mapping = aes(x = AgeBin_index, y = Incidence), 
    size = 3, shape = 0, color = 'black'
  ) + 
  geom_errorbar(
    data = inc.data,
    mapping = aes(x = AgeBin_index, ymin = lb, ymax = ub),
    color = 'black'
  ) + 
  facet_grid(cols = vars(Gender), rows = vars(Year)) +
  xlab("Age") +
  ylab("Incidence (%)") +
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_discrete(
    breaks = 1:length(age_labels),
    labels = age_labels
    ) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_manual(values=c("blue", "red"))
  
p

ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/Analysis/hiv_age_incidence.pdf",
       width = 12, height = 6, units = "in")

```

# New Cases by Age

```{r}
age_bins = c(15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65,100)
subset_years = c(2007, 2011, 2016, 2021)

# Subset data on years
data <- sim.results %>% mutate(Year = ceiling(Year)) %>% filter(Year %in% subset_years)

# Age bins
age_labels = c()
for (i in 1:(length(age_bins) - 1)){
  age_labels <- append(age_labels, paste0("[",age_bins[i],":",age_bins[i + 1],")"))
}

# Label each age by its bin
data <- data %>% mutate(
  AgeBin = cut(Age, breaks = age_bins, right = FALSE)
  ) %>%
  filter(!is.na(AgeBin))
data$AgeBin_index = factor(data$AgeBin,labels = 1:length(age_labels))

# Count HIV deaths
cases.dat <- data %>% 
  group_by(Year, AgeBin_index, AgeBin, Gender, scenario_name, sim.ix) %>% 
  summarize(Newly.Infected = sum(Newly.Infected* pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, AgeBin_index, AgeBin, Gender, scenario_name) %>% 
  summarize(sd.Newly.Infected = sd(Newly.Infected),
            Newly.Infected = mean(Newly.Infected), 
            .groups = "keep")  %>% 
  ungroup() %>%
  dplyr::mutate(upper = Newly.Infected + 2*sd.Newly.Infected,
                lower = case_when(Newly.Infected - 2 * sd.Newly.Infected > 0 ~ Newly.Infected - 2 * sd.Newly.Infected,
                         Newly.Infected - 2 * sd.Newly.Infected <= 0 ~ 0)
                )

# Transform data
cases.dat <- cases.dat %>% mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

p <- cases.dat %>%
  ggplot() +
  # plot means
  geom_point(
    mapping = aes(x = AgeBin_index, y = Newly.Infected, color = Gender),
    size=2,
     show.legend = FALSE
  ) +
  geom_errorbar(
    mapping = aes(x=AgeBin_index, ymin=lower, ymax=upper, color=Gender),
    width=.15, size=1,
   show.legend = FALSE) +
  facet_grid(cols = vars(Gender), rows = vars(Year)) +
  xlab("Age") +
  ylab("New HIV Cases") +
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_discrete(
    breaks = 1:length(age_labels),
    labels = age_labels
    ) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_manual(values=c("blue", "red"))
  
p

ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/Analysis/hiv_age_newcases.pdf",
       width = 12, height = 6, units = "in")

```


## Mean age of new infected

```{r}
NewCases.by.Age = sim.results %>% 
  group_by(Year, Gender, Age, scenario_name, sim.ix) %>% 
  summarize(Newly.Infected = sum(Newly.Infected), .groups = 'keep') %>% 
  group_by(Year, Gender, Age, scenario_name) %>% 
  summarize(Newly.Infected = mean(Newly.Infected), .groups = 'keep') %>% 
  ungroup()

NewCases.by.Age <- NewCases.by.Age %>% 
  merge(
    NewCases.by.Age %>% 
      group_by(Year, Gender, scenario_name) %>% 
      summarize(Newly.Infected.total = sum(Newly.Infected)),
    by = c("Year", "Gender", "scenario_name")
) %>% 
  mutate(prod = case_when(Newly.Infected > 0 ~ Age * Newly.Infected,
                          Newly.Infected == 0 ~ 0)
         ) %>% 
  group_by(Year, Gender, scenario_name) %>% 
  summarize(mean.age = sum(prod), Newly.Infected.total = mean(Newly.Infected.total)) %>% 
  ungroup() %>% 
  mutate(prod = case_when(Newly.Infected.total > 0 ~ mean.age/Newly.Infected.total,
                          Newly.Infected.total == 0 ~ 0)
       ) %>% 
  arrange(Gender, Year)

p <- NewCases.by.Age %>% 
  filter(Year >= 2000) %>% 
  mutate(Gender = factor(Gender, labels = c("Male", "Female")))  %>%
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = prod, color = Gender), size = 2) + 
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_continuous(breaks = seq(2000,2040,5)) +
  scale_y_continuous(breaks = c(20,25,30,35)) + 
  ylim(20,32.5) + 
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  ylab("Mean Age of New Infections") + 
  scale_color_manual(values = c("red", "blue"))

p

ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/Analysis/mean_age_new_infections.pdf",
       width = 8, height = 6, units = "in")

```



# HIV deaths by age and sex


```{r}
age_bins = c(15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65,100)
subset_years = c(2007, 2011, 2016, 2021)

# Subset data on years
data <- sim.results %>% mutate(Year = ceiling(Year)) %>% filter(Year %in% subset_years)

# Age bins
age_labels = c()
for (i in 1:(length(age_bins) - 1)){
  age_labels <- append(age_labels, paste0("[",age_bins[i],":",age_bins[i + 1],")"))
}

# Label each age by its bin
data <- data %>% mutate(
  AgeBin = cut(Age, breaks = age_bins, right = FALSE)
  ) %>%
  filter(!is.na(AgeBin))
data$AgeBin_index = factor(data$AgeBin,labels = 1:length(age_labels))

# Count HIV deaths
deaths.dat <- data %>% 
  mutate(Year = ceiling(Year)) %>% 
  group_by(Year, AgeBin_index, AgeBin, Gender, scenario_name, sim.ix) %>% 
  summarize(Died_from_HIV = sum(Died_from_HIV* pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, AgeBin_index, AgeBin, Gender, scenario_name) %>% 
  summarize(sd.Died_from_HIV = sd(Died_from_HIV),
            Died_from_HIV = mean(Died_from_HIV), 
            .groups = "keep")  %>% 
  ungroup() %>%
  dplyr::mutate(upper = Died_from_HIV + 2*sd.Died_from_HIV,
                lower = case_when(Died_from_HIV - 2 * sd.Died_from_HIV > 0 ~ Died_from_HIV - 2 * sd.Died_from_HIV,
                         Died_from_HIV - 2 * sd.Died_from_HIV <= 0 ~ 0)
                )

# Transform data
deaths.dat <- deaths.dat %>% mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

p <- deaths.dat %>%
  ggplot() +
  # plot means
  geom_point(
    mapping = aes(x = AgeBin_index, y = Died_from_HIV, color = Gender),
    size=2,
     show.legend = FALSE
  ) +
  geom_errorbar(
    mapping = aes(x=AgeBin_index, ymin=lower, ymax=upper, color=Gender),
    width=.15, size=1,
   show.legend = FALSE) +
  facet_grid(cols = vars(Gender), rows = vars(Year)) +
  xlab("Age") +
  ylab("HIV Deaths") +
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_discrete(
    breaks = 1:length(age_labels),
    labels = age_labels
    ) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_manual(values=c("blue", "red"))
  
p

ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/Analysis/hiv_age_deaths.pdf",
       width = 12, height = 6, units = "in")
```


# ART

```{r, fig.width=8}
sim.onart <- sim.results %>% 
  dplyr::group_by(Year, Gender, sim.id, scenario_name) %>% 
  dplyr::summarize(On_ART = sum(On_ART * pop.scaling.factor),
                   Population = sum(Infected * pop.scaling.factor), 
                   .groups = "keep") %>% 
  ungroup()

# sim.onart %>% group_by(Year, Gender, scenario_name) %>% 
#   summarize(On_ART = mean(On_ART), Population = mean(Population)) %>% 
#   mutate(ARTCov = case_when(Population == 0 ~ 0 ,
#                    Population > 0 ~ On_ART/Population)) %>% View

p <- EMODAnalyzeR::emodplot.by_gender(sim.onart, 2000, 2025, 
                        "On_ART", title = "Population on ART") + 
    ylab("Number on ART")

p

```

## ART Coverage by age

```{r}
age_bins = c(15, 25, 35, 45, 100)
# Age bins
age_labels = c()
for (i in 1:(length(age_bins) - 1)){
  age_labels <- append(age_labels, paste0("[",age_bins[i],":",age_bins[i + 1],")"))
}

# Label each age by its bin
data <- data %>% mutate(
  AgeBin = cut(Age, breaks = age_bins, right = FALSE)
  ) %>%
  filter(!is.na(AgeBin))

obs.onart.sheet <- fread("/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/Data/SWZ_art_coverage.csv")

obs.onart.sheet <- obs.onart.sheet %>% mutate(across(AgeBin, str_replace, ':', ','))

obs.onart.sheet$AgeBin = factor(obs.onart.sheet$AgeBin)
obs.onart.sheet$AgeBin_index = factor(obs.onart.sheet$AgeBin,labels = 1:length(age_labels))

obs.onart.sheet %>% head
```


```{r}
age_bins = c(15, 25, 35, 45, 99)

# Subset data on years
data <- sim.results %>% filter(Year >= 2004)

# Age bins
age_labels = c()
for (i in 1:(length(age_bins) - 1)){
  age_labels <- append(age_labels, paste0("[",age_bins[i],":",age_bins[i + 1],")"))
}

# Label each age by its bin
data <- data %>% mutate(
  AgeBin = cut(Age, breaks = age_bins, right = FALSE)
  ) %>%
  filter(!is.na(AgeBin))
data$AgeBin_index = factor(data$AgeBin,labels = 1:length(age_labels))

# Calculate prevalence, grouping by age bin
data.prev <- data %>% EMODAnalyzeR::calculate.prevalence(
  stratify_columns = c("Year", "AgeBin_index", "AgeBin", "Gender", "scenario_name", "sim.id"),
  numerator = "On_ART",
  denominator = "Infected")

# Calculate mean ART coverage
data.mean <- data.prev %>%
  dplyr::group_by(Year, AgeBin_index, AgeBin, Gender, scenario_name) %>%
  dplyr::summarize(mean.Prevalence = mean(Prevalence),
            sd.Prevalence = sd(Prevalence),
            .groups = 'keep') %>%
  ungroup() %>%
  dplyr::mutate(upper = mean.Prevalence + 2*sd.Prevalence,
                lower = case_when(mean.Prevalence - 2 * sd.Prevalence > 0 ~ mean.Prevalence - 2 * sd.Prevalence,
                         mean.Prevalence - 2 * sd.Prevalence <= 0 ~ 0)
                )

# Transform data
data.mean <- data.mean %>% mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

p <- data.mean %>%
  ggplot() +
  # plot data
  geom_point(data = obs.onart.sheet,
             mapping = aes(x = Year, y = ARTPrevalence*100)) + 
  # plot means
  geom_point(
    mapping = aes(x = Year, y = mean.Prevalence*100, color = Gender),
    size=1,
     show.legend = FALSE
  ) +
  geom_errorbar(
    mapping = aes(x=Year, ymin=lower, ymax=upper, color=Gender),
    width=.15, size=1,
   show.legend = FALSE) +
  facet_grid(cols = vars(Gender), rows = vars(AgeBin)) +
  xlab("Year") +
  ylab("ART Coverage (%)") +
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_manual(values=c("blue", "red"))
  
p

ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/Analysis/hiv_age_artcov.pdf",
       width = 12, height = 6, units = "in")
```

