---
title: "swz_idm24_abstract"
output: html_document
date: "2024-05-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The purpose of this notebook is to compare the Swaziland model output against the calibration targets

```{r Load Libraries, echo = FALSE}
library(tidyverse)
library(data.table)
library(magrittr)
library(ggplot2)
library(devtools)
library(readxl)
library(spatstat)
#devtools::install_github("BershteynLab/EMODAnalyzeR")
```

```{r}
CENSUS_YEAR = 2017
SWZ_CENSUS_POP = 1148000 # UN WPP 2019, according to SWZ national census 2017 1093238
```
## Import data

```{r, echo=FALSE}

# Test version 4
#results_path = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/test4/Baseline-campaign_20231113-baseline/ReportHIVByAgeAndGender"

# Test version 3
#results_path = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/test3_swz2024/Baseline-campaign_20231113-baseline/ReportHIVByAgeAndGender/"

# Version 3, but with updated
results_path = 

sim.results <- EMODAnalyzeR::read.simulation.results(
  results_path = results_path,
  scenario_name = 'baseline',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.Risk"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

sim.results.pop.scaling <- sim.results %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.id) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = SWZ_CENSUS_POP/total.pop)

sim.results <- sim.results %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.id")
  )

```

# Prevalence

```{r, echo=FALSE}
ingest.file.base = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/Data/calibration_ingest_form-Swaziland_ART_vars--UPDATED--2023-07.xlsm"

obs.prev.sheet.base <- EMODAnalyzeR::read.ingest.sheet(ingest.file.base, "Obs-Prevalence")
obs.prev.sheet.base <- obs.prev.sheet.base %>% filter(!is.na(AgeBin))

# DHS data for adults 15-50
# 2006
# Female: 31.1 [29.3, 32.9]
# Male: 19.7 [17.9, 21.5]

# PHIA data for adults 15 +
# 2016
# Female: 32.5 [31,34]
# Male: 20.4 [18.9, 21.9]

# Note the differences in age brackets. Depending on whether we look at Adults 15-50 or Adults 15+ we will match one or the ohter dataset but not both.
calib.targets.prev.all <- data.table(Year = c(2006, 2006, 2016, 2016),
                                     Gender = c("Male", "Female", "Male", "Female"),
                                     prev = c(19.7, 31.1, 20.4, 32.5),
                                     lb = c(17.9, 29.3, 18.9, 31),
                                     ub = c(21.5, 32.9, 21.9, 34))

obs.prev.sheet.base %>% head
```


```{r}
prev.15.49 <- data.table(Year = c(2006, 2006, 2011,2011, 2016, 2016, 2021, 2021),
                         Gender = c("Female", "Male"),
                         prev = c(31.36998255, 19.54469739, 38.79583333, 24.3101129, 34.67579541, 19.87162343, 32.01485259, 16.34463925)/100,
                         #prev = c(0.38861021, 0.282294676, 0.462308369, 0.274811025, 0.421160235, 0.26133829, 0.384828736, 0.195259228),
                         lb = c(30.02809341, 18.26093783, 37.83139223,23.39183621, 33.35133936,18.60315482,31.85041561, 16.21699044)/100,
                         ub = c(32.73564238, 20.87807258, 39.76691062, 25.2464012, 36.01828845,21.18736119, 32.17962673, 16.4728948)/100)

data <- EMODAnalyzeR::calculate.prevalence(
  sim.results %>% filter(Age >=15, Age < 50),
         stratify_columns = c("Year", "Gender", "sim.id", "scenario_name"),
         numerator = "Infected",
         denominator = "Population")

prev.data.mean <- data %>%
    dplyr::group_by(Year, Gender, scenario_name) %>%
    dplyr::summarise(Prevalence = mean(Prevalence), .groups = 'keep') %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

ggplot() +
    geom_line(data= prev.data.mean %>% filter(Year > 1995),
              aes(x=Year, y=Prevalence, group=scenario_name, color=Gender), linewidth=2, 
               show.legend = FALSE)+
    geom_point(data = prev.15.49,
               mapping = aes(x = Year, y = prev),
                show.legend = FALSE,
               color = 'black', shape = 0,
               size = 2) +
    geom_errorbar(data = prev.15.49,
                  mapping = aes(x = Year, ymin = lb, ymax = ub),
                  show.legend = FALSE,
                  color = 'black', size = .5)+
    facet_wrap(~ Gender, ncol=2) +
    xlab("Year")+
    #xlim(c(date.start, date.end)) +
    ylab("Prevalence") +
    theme_bw(base_size=16) +
    guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
    scale_x_continuous(breaks = seq(1980,2050,10)) +
    scale_y_continuous(breaks = seq(0,.40,.10), 
                       limits = c(0,.45),
                       labels = scales::percent_format(accuracy = 1)) +
    theme(legend.position="bottom") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    theme(strip.background = element_rect(colour="black", fill="white")) +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    ylab("HIV Prevalence (%)") + 
    scale_color_manual(values=c("blue", "red")) 


# ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/Analysis/prev_adults.pdf",
#       width = 8, height = 4, units = "in")
```

# Analysis

## Reductions in prevalence
```{r}

data <- EMODAnalyzeR::calculate.prevalence(
  sim.results %>% filter(Age >=15, Age < 100),
         stratify_columns = c("Year", "sim.id", "scenario_name"),
         numerator = "Infected",
         denominator = "Population")

prev.data.mean <- data %>%
    dplyr::group_by(Year, scenario_name) %>%
    dplyr::summarise(Prevalence = mean(Prevalence), .groups = 'keep')

prev.data.mean %>% filter(Year %in% c(2004, 2024))
```

## Reductions in incidence


```{r}
# 2011 SHIMS
# <https://www-ncbi-nlm-nih-gov.ezproxy.med.nyu.edu/pmc/articles/PMC5291824/>
# 2016
# <https://phia.icap.columbia.edu/wp-content/uploads/2019/05/SHIMS2_Final-Report_05.03.2019_forWEB.pdf>
# 2021
# <https://phia.icap.columbia.edu/wp-content/uploads/2023/12/241123_SHIMS_ENG_RR3_Final-1.pdf>
# Ages 15-49
incidence.data <- data.table(Year = c(2011, 2011, 2016, 2016, 2021, 2021),
                                     Gender = c("Male", "Female"),
                                     inc = c(1.7,3.1,.99, 1.99, .2, 1.45),
                                     lb = c(1.3, 2.6, .032, 1.09, 0, 0.69 ),
                                     ub = c(2.1,3.7, 1.66, 2.88, .48, 2.2))
```

Incidence ages 15-49?
```{r}
data <- sim.results %>% filter(Age >= 15, Age < 50)

# Calculate incidence
data$Year_Integer <- floor((data$Year-0.5))
# Aggregate number of new infections each year, broken down by Year_Integer and Gender
trajectories_IR.1a <- aggregate(Newly.Infected ~ Year_Integer+Gender + sim.id+scenario_name, data=data,FUN=sum)
#Make the denominator as HIV-negative individuals
trajectories_IR.2 <- aggregate(Population - Infected ~ Year+Gender + sim.id+scenario_name, data=data, FUN=sum)
trajectories_IR.2$Year_Integer <- floor(trajectories_IR.2$Year-0.5)
#remove second instance of duplicate rows
trajectories_IR.2 <- trajectories_IR.2[!duplicated(trajectories_IR.2[c("Year_Integer","Gender", "sim.id","scenario_name")]),]
trajectories_IR.2 <- trajectories_IR.2[-match("Year",names(trajectories_IR.2))]
trajectories_IRoverall <- merge(trajectories_IR.1a, trajectories_IR.2, by=c("Year_Integer","Gender","sim.id","scenario_name"))
trajectories_IRoverall$incidence <- trajectories_IRoverall$Newly.Infected / (trajectories_IRoverall$Population)
data <- trajectories_IRoverall %>% dplyr::rename(Year = Year_Integer)

# Calculate mean incidence across all sim runs
data.mean <- data %>%
  dplyr::group_by(Year, Gender, scenario_name) %>%
  dplyr::summarize(mean.Incidence = mean(incidence),
                  sd.Incidence = sd(incidence),
            .groups = 'keep') %>%
  ungroup() %>%
  dplyr::mutate(upper = mean.Incidence + 2*sd.Incidence,
                lower = case_when(mean.Incidence - 2 * sd.Incidence > 0 ~ mean.Incidence - 2 * sd.Incidence,
                         mean.Incidence - 2 * sd.Incidence <= 0 ~ 0)
                )

# Transform data
data.mean <- data.mean %>% mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

p <- data.mean %>%
  ggplot() +
  # plot means
  geom_point(
    mapping = aes(x = Year, y = mean.Incidence*100, color = Gender),
    size=2,
     show.legend = FALSE
  ) +
  geom_errorbar(
    mapping = aes(x=Year, ymin=lower*100, ymax=upper*100, color=Gender),
    width=.15, size=1,
   show.legend = FALSE) +
  geom_point(data = incidence.data, 
             mapping = aes(x = Year, y = inc), color = 'black') + 
  geom_errorbar(data = incidence.data, 
    mapping = aes(x = Year, ymin = lb, ymax = ub), color = 'black') + 
  facet_grid(cols = vars(Gender)) +
  xlab("Age") +
  ylab("Incidence (%)") +
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_continuous(breaks = c(1975, 1980, 1985, 1990, 1995, 2000, 2005, 2010, 2015, 2020, 2025),
                     limits = c(1975, 2025)) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_manual(values=c("blue", "red"))
  
p

# ggsave(
#   filename = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/Analysis/incidence_all_1549.pdf",
#        width = 12, height = 6, units = "in")

```
```{r}
data.mean %>% filter(Year > 2000) %>% arrange(Gender, Year)

# Peak incidence is 2005 for women
# Peak incidence is 2004 for men
```

# Prevalence by age

Estimating the peak 

```{r, fig.width=10, fig.height=10}
age_bins = c(15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65,99)
subset_years = c(2007, 2011, 2016, 2021)

# Subset data on years
data <- sim.results %>% filter(Year %in% subset_years)

# Age bins
age_labels = c()
for (i in 1:(length(age_bins) - 1)){
  age_labels <- append(age_labels, paste0("[",age_bins[i],":",age_bins[i + 1],")"))
}

# Label each age by its bin
data <- data %>% mutate(
  AgeBin = cut(Age, breaks = age_bins, right = FALSE)
  ) %>%
  filter(!is.na(AgeBin))
data$AgeBin_index = factor(data$AgeBin,labels = 1:length(age_labels))

# Calculate prevalence, grouping by age bin
data.prev <- data %>% EMODAnalyzeR::calculate.prevalence(
  stratify_columns = c("Year", "AgeBin_index", "AgeBin", "Gender", "scenario_name", "sim.id"),
  numerator = "Infected",
  denominator = "Population")

# Calculate mean prevalence across all sim runs
data.mean <- data.prev %>%
  dplyr::group_by(Year, AgeBin_index, AgeBin, Gender, scenario_name) %>%
  dplyr::summarize(mean.Prevalence = mean(Prevalence),
            sd.Prevalence = sd(Prevalence),
            .groups = 'keep') %>%
  ungroup() %>%
  dplyr::mutate(upper = mean.Prevalence + 2*sd.Prevalence,
                lower = case_when(mean.Prevalence - 2 * sd.Prevalence > 0 ~ mean.Prevalence - 2 * sd.Prevalence,
                         mean.Prevalence - 2 * sd.Prevalence <= 0 ~ 0)
                )

# Transform data
data.mean <- data.mean %>% mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

# Reformat the prevalence data:
obs.prev.sheet.base <- obs.prev.sheet.base %>% 
  mutate(AgeBin_index = factor(obs.prev.sheet.base$AgeBin,labels = 1:length(age_labels)))

p <- data.mean %>%
  ggplot() +
  geom_point(data = obs.prev.sheet.base,
             mapping = aes(x = AgeBin_index, y = Prevalence), 
             size = 3, color = 'black', shape = 0,
             show.legend = FALSE) +
  geom_errorbar(data = obs.prev.sheet.base,
             mapping = aes(x = AgeBin_index, ymin = lb, ymax = ub),
             size = 1, color = 'black',
             show.legend = FALSE) +
  # plot means
  geom_point(
    mapping = aes(x = AgeBin_index, y = mean.Prevalence, color = Gender),
    size=2,
     show.legend = FALSE
  ) +
  geom_line(
    mapping = aes(x = AgeBin_index, y = mean.Prevalence, color = Gender),
    size=1,
    show.legend = FALSE,
    group = 1
  ) +
  # geom_errorbar(
  #   mapping = aes(x=AgeBin_index, ymin=lower, ymax=upper, color=Gender),
  #   width=.15, size=1,
  #  show.legend = FALSE) +
  facet_grid(cols = vars(Gender), rows = vars(Year)) +
  #xlab("Age") +
  #ylab("Prevalence") +
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_discrete(
    breaks = 1:length(age_labels),
    labels = rep("",length(age_labels))
    ) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
  #theme(legend.position="bottom") + 
  theme(legend.position="bottom",
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        strip.text.x = element_blank(),
        strip.text.y = element_blank()) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_manual(values=c("blue", "red"))
  
p

# ggsave(filename = "/gpfs/data/bershteynlab/EMOD/citrod01/SWZ_calib/Analysis/hiv_age_prev.pdf",
#        width = 12, height = 6, units = "in")
```

## Mean age of PLHIV

```{r}
Infected.by.age = sim.results %>% 
  filter(Age >= 15, Age < 50 ) %>% 
  group_by(Year, Gender, Age, scenario_name, sim.ix) %>% 
  summarize(Infected = sum(Infected), .groups = 'keep') %>% 
  group_by(Year, Gender, Age, scenario_name) %>% 
  summarize(Infected = mean(Infected), .groups = 'keep') %>% 
  ungroup()


Infected.by.age <- Infected.by.age %>% 
  merge(
    Infected.by.age %>% 
      group_by(Year, Gender, scenario_name) %>% 
      summarize(Infected.total = sum(Infected)),
    by = c("Year", "Gender", "scenario_name")
) %>% 
  mutate(prod = case_when(Infected.total > 0 ~ Age * Infected,
                          Infected.total == 0 ~ 0)
         ) %>% 
  group_by(Year, Gender, scenario_name) %>% 
  summarize(mean.age = sum(prod), Infected.total = mean(Infected.total)) %>% 
  ungroup() %>% 
  mutate(prod = case_when(Infected.total > 0 ~ mean.age/Infected.total,
                          Infected.total == 0 ~ 0)
       ) %>% 
  arrange(Gender, Year)

p <- Infected.by.age %>% 
  filter(Year >= 2000) %>% 
  mutate(Gender = factor(Gender, labels = c("Male", "Female")))  %>%
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = prod, color = Gender), size = 2, show.legend = TRUE) + 
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_continuous(breaks = seq(2000,2050,5)) +
  #scale_y_continuous(breaks = c(20,25,30,35)) + 
  #ylim(25,40) + 
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  ylab("Mean Age of PLHIV (15-49)") + 
  scale_color_manual(values = c("red", "blue"))

p

```

```{r}
Infected.by.age = sim.results %>% 
  filter(Age >= 15, Age < 100 ) %>% 
  group_by(Year, Gender, Age, scenario_name, sim.ix) %>% 
  summarize(Infected = sum(Infected), .groups = 'keep') %>% 
  group_by(Year, Gender, Age, scenario_name) %>% 
  summarize(Infected = mean(Infected), .groups = 'keep') %>% 
  ungroup()


Infected.by.age <- Infected.by.age %>% 
  merge(
    Infected.by.age %>% 
      group_by(Year, Gender, scenario_name) %>% 
      summarize(Infected.total = sum(Infected)),
    by = c("Year", "Gender", "scenario_name")
) %>% 
  mutate(prod = case_when(Infected.total > 0 ~ Age * Infected,
                          Infected.total == 0 ~ 0)
         ) %>% 
  group_by(Year, Gender, scenario_name) %>% 
  summarize(mean.age = sum(prod), Infected.total = mean(Infected.total)) %>% 
  ungroup() %>% 
  mutate(prod = case_when(Infected.total > 0 ~ mean.age/Infected.total,
                          Infected.total == 0 ~ 0)
       ) %>% 
  arrange(Gender, Year)

p <- Infected.by.age %>% 
  filter(Year >= 2000) %>% 
  mutate(Gender = factor(Gender, labels = c("Male", "Female")))  %>%
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = prod, color = Gender), size = 2, show.legend = TRUE) + 
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_continuous(breaks = seq(2000,2050,5)) +
  #scale_y_continuous(breaks = c(20,25,30,35)) + 
  #ylim(25,40) + 
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  ylab("Mean Age of PLHIV (15-49)") + 
  scale_color_manual(values = c("red", "blue"))

p
```


```{r}

Infected.by.age = sim.results %>% 
  filter(Age >= 15, Age < 100 ) %>% 
  group_by(Year, Age, scenario_name, sim.ix) %>% 
  summarize(Infected = sum(Infected), .groups = 'keep') %>% 
  group_by(Year, Age, scenario_name) %>% 
  summarize(Infected = mean(Infected), .groups = 'keep') %>% 
  ungroup()


Infected.by.age <- Infected.by.age %>% 
  merge(
    Infected.by.age %>% 
      group_by(Year, scenario_name) %>% 
      summarize(Infected.total = sum(Infected)),
    by = c("Year", "scenario_name")
) %>% 
  mutate(prod = case_when(Infected.total > 0 ~ Age * Infected,
                          Infected.total == 0 ~ 0)
         ) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(mean.age = sum(prod), Infected.total = mean(Infected.total)) %>% 
  ungroup() %>% 
  mutate(prod = case_when(Infected.total > 0 ~ mean.age/Infected.total,
                          Infected.total == 0 ~ 0)
       ) %>% 
  arrange(Year)

Infected.by.age %>% filter(Year %in% c(2004, 2024, 2050))
```


```{r}
Infected.by.age %>% filter(Year %in% c(2004, 2024))
```

# New Cases by Age

## How much has incidence changed in each age group?

```{r}
age_bins = c(15, 25, 30, 35, 40, 45, 50, 55, 60, 65,100)
subset_years = c(2004, 2024) # c(2007, 2011, 2016, 2021, )

# Subset data on years
data <- sim.results %>% mutate(Year = ceiling(Year)) %>% filter(Year %in% subset_years)

# Age bins
age_labels = c()
for (i in 1:(length(age_bins) - 1)){
  age_labels <- append(age_labels, paste0("[",age_bins[i],":",age_bins[i + 1],")"))
}

# Label each age by its bin
data <- data %>% mutate(
  AgeBin = cut(Age, breaks = age_bins, right = FALSE)
  ) %>%
  filter(!is.na(AgeBin))
data$AgeBin_index = factor(data$AgeBin,labels = 1:length(age_labels))

# Count HIV deaths
cases.dat <- data %>% 
  group_by(Year, AgeBin_index, AgeBin, Gender, scenario_name, sim.ix) %>% 
  summarize(Newly.Infected = sum(Newly.Infected* pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, AgeBin_index, AgeBin, Gender, scenario_name) %>% 
  summarize(sd.Newly.Infected = sd(Newly.Infected),
            Newly.Infected = mean(Newly.Infected), 
            .groups = "keep")  %>% 
  ungroup() %>%
  dplyr::mutate(upper = Newly.Infected + 2*sd.Newly.Infected,
                lower = case_when(Newly.Infected - 2 * sd.Newly.Infected > 0 ~ Newly.Infected - 2 * sd.Newly.Infected,
                         Newly.Infected - 2 * sd.Newly.Infected <= 0 ~ 0)
                )

# Transform data
cases.dat <- cases.dat %>% mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))

cases.dat %>% arrange(Gender, AgeBin_index, Year) %>% 
  pivot_wider(id_cols = c(AgeBin_index, AgeBin, Gender), values_from = Newly.Infected, names_from = Year ) %>% 
  mutate(diff = `2024` - `2004`,
         pct = (`2024` - `2004`)/`2004`) %>%
  arrange(Gender, AgeBin_index)
```


## What is the mean age of new infections
```{r}
NewCases.by.Age = sim.results %>% 
  group_by(Year, Gender, Age, scenario_name, sim.ix) %>% 
  summarize(Newly.Infected = sum(Newly.Infected), .groups = 'keep') %>% 
  group_by(Year, Gender, Age, scenario_name) %>% 
  summarize(Newly.Infected = mean(Newly.Infected), .groups = 'keep') %>% 
  ungroup()

NewCases.by.Age <- NewCases.by.Age %>% 
  merge(
    NewCases.by.Age %>% 
      group_by(Year, Gender, scenario_name) %>% 
      summarize(Newly.Infected.total = sum(Newly.Infected)),
    by = c("Year", "Gender", "scenario_name")
) %>% 
  mutate(prod = case_when(Newly.Infected > 0 ~ Age * Newly.Infected,
                          Newly.Infected == 0 ~ 0)
         ) %>% 
  group_by(Year, Gender, scenario_name) %>% 
  summarize(mean.age = sum(prod), Newly.Infected.total = mean(Newly.Infected.total)) %>% 
  ungroup() %>% 
  mutate(prod = case_when(Newly.Infected.total > 0 ~ mean.age/Newly.Infected.total,
                          Newly.Infected.total == 0 ~ 0)
       ) %>% 
  arrange(Gender, Year)

p <- NewCases.by.Age %>% 
  filter(Year >= 2000) %>% 
  mutate(Gender = factor(Gender, labels = c("Male", "Female")))  %>%
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = prod, color = Gender), size = 2,
            show.legend = FALSE) + 
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_x_continuous(breaks = seq(2000,2050,5)) +
  scale_y_continuous(breaks = c(20,25,30,35)) + 
  ylim(20,45) + 
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  ylab("Mean Age of New Infections") + 
  scale_color_manual(values = c("red", "blue"))

p
```

```{r}
NewCases.by.Age %>% filter(Year %in% c(2004, 2024))
```

